---
title: "日本語"
output:
  html_document:
    theme: sandstone
    css: "mystyle.css"
    toc: false
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{=html}
<style type="text/css">

body{
      font-size: 13px;
      font-family: "Anonymous Pro", "Roboto", "Helvetica Neue";
  }
</style>
```
<link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Hina+Mincho&family=Klee+One:wght@400;600&family=New+Tegomin&family=Sawarabi+Gothic&family=Shippori+Mincho+B1:wght@400;500&family=Yomogi&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Noto+Sans+JP:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=M+PLUS+Rounded+1c:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;1,700&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;0,700;1,700&display=swap" rel="stylesheet">

```{css, echo=FALSE}
.my-tbl {
  border: 1px solid rgba(0, 0, 0, 0.1);
}

.my-header {
  border-width: 1px;
}

.my-col {
  border-right: 1px solid rgba(0, 0, 0, 0.05);
}

.my-row:hover {
  background-color: #f5f8ff;
}

.toc-content {
    padding-left: 10px;
    padding-right: 10px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo=FALSE}
@media(prefers-color-scheme: dark) {
  body {
    background-color: black;
    filter: invert(1);
  }
}
```

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(reactable)
library(htmltools)
library(bslib)
library(dplyr)
library(purrr)
library(readr)
library(vembedr)
options(readr.show_col_types = FALSE)
```

```{r, echo=FALSE, message=FALSE, error=FALSE}
vnstx <- read_csv("vrbjp/Sheet 178-VNLST.csv")
vnstb <- read_csv("vrbjp/Sheet 83-VBPH.csv")
vnstc <- read_csv("vrbjp/Sheet 148-SSTNC.csv")
vnstd <- read_csv("vrbjp/Sheet 149-SSTNC.csv")
vnste <- read_csv("vrbjp/Sheet 150-SSTNC.csv")
vnstg <- read_csv("vrbjp/Sheet 2-VGRM.csv")
vnsgg <- read_csv("vrbjp/Sheet 3-VGRM.csv")
vnsss <- read_csv("vrbjp/Sheet 1-VBPLS.csv")
knj <- read_csv("vrbjp/Sheet 5-KNJ.csv")
knjr <- read_csv("vrbjp/Sheet 6-KNJ.csv")
vnsst <- read_csv("vrbjp/Sheet 7-VPHS.csv")
klvl1 <- read_csv("vrbjp/Sheet 8-WBKNJ1.csv")
klvl2 <- read_csv("vrbjp/Sheet 9-WBKNJ2.csv")
klvl3 <- read_csv("vrbjp/Sheet 10-WBKNJ3.csv")
klv1 <- read_csv("vrbjp/Sheet 11-KNJD1.csv")
klv2 <- read_csv("vrbjp/Sheet 12-KNJD2.csv")
vnlr <- read_csv("vrbjp/Sheet 14-VNLST.csv")
dlgm <- read_csv("vrbjp/Sheet 13-TBE.csv")
nlgm <- read_csv("vrbjp/Sheet 15-JGRM.csv")
jlgm <- read_csv("vrbjp/Sheet 16-JGRM.csv")
mnlg <- read_csv("vrbjp/Sheet 17-MNLNG.csv")
onmp <- read_csv("vrbjp/Sheet 18-ONMP.csv")
cnmw <- read_csv("vrbjp/Sheet 19-CMNW.csv")
cnmw1 <- read_csv("vrbjp/Sheet 22-CMNW.csv")
cnmw2 <- read_csv("vrbjp/Sheet 23-CMNW.csv")
cnmw3 <- read_csv("vrbjp/Sheet 24-CMNW.csv")
cnmw4 <- read_csv("vrbjp/Sheet 25-CMNW.csv")
cnmw5 <- read_csv("vrbjp/Sheet 26-CMNW.csv")
cnmw6 <- read_csv("vrbjp/Sheet 27-CMNW.csv")
cmpnd <- read_csv("vrbjp/Sheet 35-CMPWD.csv")
cook <- read_csv("vrbjp/Sheet 20-MKOKT.csv")
diary <- read_csv("vrbjp/Sheet 21-FTRD.csv")
knjdl<- read_csv("vrbjp/Sheet 40-KNJD.csv")
expw<- read_csv("vrbjp/Sheet 36-EXPR.csv")
adjadv<- read_csv("vrbjp/Sheet 37-ADVADJ.csv")
cmwrdsn<- read_csv("vrbjp/Sheet 43-CMNWP.csv")
exppw<- read_csv("vrbjp/Sheet 42-EXPRP.csv")
jnrst <- read_csv("vrbjp/Sheet 44-JNRST.csv")
sntv <- read_csv("vrbjp/Sheet 98-MSNTC.csv")
rvvrb <- read_csv("vrbjp/Sheet 179-VNLST.csv")
rvwrd <- read_csv("vrbjp/Sheet 180-WRDSR.csv")
rvsnt <- read_csv("vrbjp/Sheet 181-WRDST.csv")
knjrvw <- read_csv("vrbjp/Sheet 50-WBKNRN.csv")
knjwrdx <- read_csv("vrbjp/Sheet 51-KNJWRD.csv")
icwrds <- read_csv("vrbjp/Sheet 128-VBPRHS.csv")
lvlg2 <- read_csv("vrbjp/Sheet 52-LVLGR.csv")
kjpen <- read_csv("vrbjp/Sheet 34-KJPEN.csv")
cmnknj <- read_csv("vrbjp/Sheet 70-CMKNJ.csv")
cmnknjv <- read_csv("vrbjp/Sheet 80-CMKNJV.csv")
cmnknjp <- read_csv("vrbjp/Sheet 81-CMKNJW.csv")
cmwpf <- read_csv("vrbjp/Sheet 90-CMKNJVM.csv")
cmwpg <- read_csv("vrbjp/Sheet 92-VGRM.csv")
cmwpc <- read_csv("vrbjp/Sheet 46-SSTBLM.csv")
cmwpu <- read_csv("vrbjp/Sheet 93-CMKNJVM.csv")
cmwpd <- read_csv("vrbjp/Sheet 95-CMKNJVM.csv")
cmwpe <- read_csv("vrbjp/Sheet 96-CMKNJVM.csv")
cmwpd2 <- read_csv("vrbjp/Sheet 97-CMKNJVM.csv")
cmwcpd <- read_csv("vrbjp/Sheet 49-WRDSCMN.csv")
fkanji <- read_csv("vrbjp/FRKJN-FREQ.csv")
ckanji <- read_csv("vrbjp/CKJN-KNJ.csv")
fwkanji <- read_csv("vrbjp/FRWKJN-FREQ.csv")
smpsnt <- read_csv("vrbjp/SMSNT-SNT.csv")
expspk <- read_csv("vrbjp/Sheet 77-ESNEXP.csv")
knjlst1 <- read_csv("vrbjp/KNJ1-WBKNJ1.csv")
knjlst2 <- read_csv("vrbjp/KNJ2-WBKNJ2.csv")
knjlst3 <- read_csv("vrbjp/KNJ3-WBKNJ3.csv")
knjlst4 <- read_csv("vrbjp/KNJ4-WBKNJ4.csv")
knjlst5 <- read_csv("vrbjp/KNJ5-WBKNJ5.csv")
knjlstr <- read_csv("vrbjp/KNJR-RNDMWV.csv")
spphr <- read_csv("vrbjp/SPPHR-HLPRS.csv")
chnkw <- read_csv("vrbjp/CHNK-RLWRD.csv")
lverbs <- read_csv("vrbjp/VERBS-VRBRNK.csv")
scknj5 <- read_csv("vrbjp/SKNJN5-KNJD1.csv")
scknj4 <- read_csv("vrbjp/SKNJN4-KNJD2.csv")
scknj3 <- read_csv("vrbjp/SKNJN3-KNJD3.csv")
scknj2 <- read_csv("vrbjp/SKNJN2-KNJD4.csv")
scknj1 <- read_csv("vrbjp/SKNJN1-KNJD5.csv")
nadj1 <- read_csv("vrbjp/ADJL-NAADJ1.csv")
nadj2 <- read_csv("vrbjp/ADJI-IADJ1.csv")
adv1 <- read_csv("vrbjp/ADV-ADV1.csv")
v1hme <- read_csv("vrbjp/CATG-VCBT1.csv")
v1hme <- read_csv("vrbjp/CATG-VCBT1.csv")
wrd5ex <- read_csv("vrbjp/WRDN5-WRD5.csv")
wrd4ex <- read_csv("vrbjp/WRDN4-WRD4.csv")
wrd3ex <- read_csv("vrbjp/WRDN3-WRD3.csv")
wrd2ex <- read_csv("vrbjp/WRDN2-WRD2.csv")
wrd1ex <- read_csv("vrbjp/WRDN1-WRD1.csv")
qsn5 <- read_csv("vrbjp/QSNTN5-QSNT5.csv")
qsn4 <- read_csv("vrbjp/QSNTN4-QSNT4.csv")
qsn3 <- read_csv("vrbjp/QSNTN3-QSNT3.csv")
qsn2 <- read_csv("vrbjp/QSNTN2-QSNT2.csv")
qsn1 <- read_csv("vrbjp/QSNTN1-QSNT1.csv")
knjcmm <- read_csv("vrbjp/CMPCH-KNJCMM.csv")
jyknj <- read_csv("vrbjp/JYKNJ-JYKNJI.csv")
jyknjon <- read_csv("vrbjp/JYKNJS-JYKNJI.csv")
jyknjkn <- read_csv("vrbjp/JYKNJK-JYKNJI.csv")
wrcll <- read_csv("vrbjp/RCLL-RCLL.csv")
shpe <- read_csv("vrbjp/SHPE-SHPE.csv")
vusge <- read_csv("vrbjp/VUSGE-VUSGE.csv")
kjlpt <- read_csv("vrbjp/JLPTW-PTWRD.csv")
wjlpt <- read_csv("vrbjp/JLPTWR-PTWRDS.csv")
grphrs <- read_csv("vrbjp/GRPHR-GRMPH.csv")
vwrbst <- read_csv("vrbjp/WVRBSH-WVBRN.csv")
tnkwrd <- read_csv("vrbjp/WTNK-WRDS.csv")
cmnvrb <- read_csv("vrbjp/CMVRB-CMVRB.csv")
sylvrb <- read_csv("vrbjp/WVRBSYL-WVBSYL.csv")
vrcll <- read_csv("vrbjp/VRCLL-WVBRN.csv")
vrbxt <- read_csv("vrbjp/VRBXT-VWRBXT.csv")
dlyknj <- read_csv("vrbjp/DLYKNJ-JYKDL.csv")
bscknj <- read_csv("vrbjp/BSCKNJ-JYKDL.csv")
vrbrvws <- read_csv("vrbjp/VRWK-KRVW.csv")
ivrbs <- read_csv("vrbjp/IVRBS-IVRBS.csv")
gvrbs <- read_csv("vrbjp/GVRBS-GVRBS.csv")
vfrsyl <- read_csv("vrbjp/WVFRSYL-WVBRN.csv")
corew <- read_csv("vrbjp/CRWRD-CRSWRD.csv")
sndknj <- read_csv("vrbjp/KNSND-KNSND.csv")
vrbxte <- read_csv("vrbjp/VRBXTE-VWRBXT.csv")
mem <- read_csv("vrbjp/MEM-MEM.csv")
dct <- read_csv("vrbjp/DCT-MEM.csv")
kana <- read_csv("vrbjp/KANA-CHR.csv")
kcmb <- read_csv("vrbjp/CMBD-CHR.csv")
verbrw <- read_csv("vrbjp/VRBRVS-WRB.csv")
dictny <- read_csv("vrbjp/DCTNY-MEM.csv")
wrdmm <- read_csv("vrbjp/WRDMM-MEM.csv")
exwrd <- read_csv("vrbjp/EXRVW-EXWRD.csv")
mcmndc <- read_csv("vrbjp/MNWRDC-CMNWRDS.csv")
tchwrd <- read_csv("vrbjp/TCWRDS-NWRDS.csv")
expvcb <- read_csv("vrbjp/EXPTB-EXPTB.csv")
skmscn <- read_csv("vrbjp/SKMSCN-SKSC.csv")
cvnptn <- read_csv("vrbjp/PTRNLST-GRML.csv")
knjrndx <- read_csv("vrbjp/RNMDKNJX-TBL.csv")
dlywrds <- read_csv("vrbjp/DLYWD-TBL.csv")
mwrdslvl <- read_csv("vrbjp/JLPTWD-JLPT.csv")
spksnt <- read_csv("vrbjp/SPKSNT-TBLSNT.csv")
vrbrwq <- read_csv("vrbjp/VRBRVWS-VRB.csv")
```

# Exams {.tabset}

## Kanji {.tabset}

```{r, echo=FALSE, message=FALSE}

# kjlpt <- kjlpt[sample(1:nrow(kjlpt)),]

reactable(
  kjlpt,
  columns = list(
    Kanji = colDef(
      # Show species under character names
      cell = function(value, index) {
        Meaning <- kjlpt$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        # Reading <- kjlpt$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        # Asso <- kjlpt$Asso[index]
        # Asso <- if (!is.na(Asso)) Asso else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 500), value),
          # div(style = list(fontSize = 10), Reading),
          div(style = list(fontSize = 9), Meaning),
          # div(style = list(fontSize = 13, fontWeight = 600), value, Asso),
        )
      },
      align = "center"
    ),
    W1 = colDef(
      cell = function(value, index) {
        M1 <- kjlpt$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        R1 <- kjlpt$R1[index]
        R1 <- if (!is.na(R1)) R1 else ""
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 9, fontWeight = 400), R1),
          div(style = list(fontSize = 9, fontWeight = 400), M1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        M2 <- kjlpt$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        R2 <- kjlpt$R2[index]
        R2 <- if (!is.na(M2)) R2 else ""
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 9, fontWeight = 400), R2),
          div(style = list(fontSize = 9, fontWeight = 400), M2),
        )
      },
      align = "center"
    ),
    W3 = colDef(
      cell = function(value, index) {
        M3 <- kjlpt$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        R3 <- kjlpt$R3[index]
        R3 <- if (!is.na(R3)) R3 else ""
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 9, fontWeight = 400), R3),
          div(style = list(fontSize = 9, fontWeight = 400), M3),
        )
      },
      align = "center"
    ),
    W4 = colDef(
      cell = function(value, index) {
        M4 <- kjlpt$M4[index]
        M4 <- if (!is.na(M4)) M4 else ""
        R4 <- kjlpt$R4[index]
        R4 <- if (!is.na(R4)) R4 else ""
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 9, fontWeight = 400), R4),
          div(style = list(fontSize = 9, fontWeight = 400), M4),
        )
      },
      align = "center"
    ),
    # W5 = colDef(
    #   cell = function(value, index) {
    #     M5 <- ckanji$M5[index]
    #     M5 <- if (!is.na(M5)) M5 else ""
    #     R5 <- ckanji$R5[index]
    #     R5 <- if (!is.na(R5)) R5 else ""
    #     tagList(
    #       div(style = list(fontSize = 25, fontWeight = 600), value),
    #       div(style = list(fontSize = 9, fontWeight = 500), R5),
    #       div(style = list(fontSize = 9, fontWeight = 500), M5),
    #     )
    #   },
    #   align = "center"
    # ),
    R1 = colDef(show = FALSE),
    R2 = colDef(show = FALSE),
    R3 = colDef(show = FALSE),
    R4 = colDef(show = FALSE),
    # R5 = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    M4 = colDef(show = FALSE),
    # M5 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)
    # Reading = colDef(show = FALSE),
    # Asso = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 85),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## Words {.tabset}

<!-- ### NR -->

<!-- ```{r, echo=FALSE, message=FALSE} -->

<!-- # wjlpt <- wjlpt[sample(1:nrow(wjlpt)),] -->

<!-- reactable( -->
<!--   wjlpt, -->
<!--   columns = list( -->
<!--     W1 = colDef( -->
<!--       # Show species under character names -->
<!--       cell = function(value, index) { -->
<!--         M1 <- wjlpt$M1[index] -->
<!--         M1 <- if (!is.na(M1)) M1 else "" -->
<!--         R1 <- wjlpt$R1[index] -->
<!--         R1 <- if (!is.na(R1)) R1 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 19, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), R1), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), M1), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->
<!--     W2 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         M2 <- wjlpt$M2[index] -->
<!--         M2 <- if (!is.na(M2)) M2 else "" -->
<!--         R2 <- wjlpt$R2[index] -->
<!--         R2 <- if (!is.na(M2)) R2 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 19, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), R2), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), M2), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->
<!--     W3 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         M3 <- wjlpt$M3[index] -->
<!--         M3 <- if (!is.na(M3)) M3 else "" -->
<!--         R3 <- wjlpt$R3[index] -->
<!--         R3 <- if (!is.na(R3)) R3 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 19, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), R3), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), M3), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->
<!--     W4 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         M4 <- wjlpt$M4[index] -->
<!--         M4 <- if (!is.na(M4)) M4 else "" -->
<!--         R4 <- wjlpt$R4[index] -->
<!--         R4 <- if (!is.na(R4)) R4 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 19, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), R4), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), M4), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->
<!--     W5 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         M5 <- wjlpt$M5[index] -->
<!--         M5 <- if (!is.na(M5)) M5 else "" -->
<!--         R5 <- wjlpt$R5[index] -->
<!--         R5 <- if (!is.na(R5)) R5 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 19, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), R5), -->
<!--           div(style = list(fontSize = 9, fontWeight = 400), M5), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->
<!--     R1 = colDef(show = FALSE), -->
<!--     R2 = colDef(show = FALSE), -->
<!--     R3 = colDef(show = FALSE), -->
<!--     R4 = colDef(show = FALSE), -->
<!--     R5 = colDef(show = FALSE), -->
<!--     M1 = colDef(show = FALSE), -->
<!--     M2 = colDef(show = FALSE), -->
<!--     M3 = colDef(show = FALSE), -->
<!--     M4 = colDef(show = FALSE), -->
<!--     M5 = colDef(show = FALSE) -->
<!--   ), -->
<!--   defaultPageSize = 5, -->
<!--   theme = reactableTheme( -->
<!--     cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 85), -->
<!--     searchInputStyle = list( -->
<!--       paddingLeft = "8px", -->
<!--       paddingTop = "8px", -->
<!--       paddingBottom = "8px", -->
<!--       width = "100%", -->
<!--       fontSize = "11px" -->
<!--     ) -->
<!--   ), -->
<!--   showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", -->

<!--   style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px") -->
<!-- ) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

### N5

```{r, echo=FALSE, message=FALSE}

wrd5ex <- wrd5ex[sample(1:nrow(wrd5ex)),]

reactable(
  wrd5ex,
  columns = list(
    W1 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W2 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W3 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W4 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W5 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center")

  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 70),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### N4

```{r, echo=FALSE, message=FALSE}

wrd4ex <- wrd4ex[sample(1:nrow(wrd4ex)),]

reactable(
  wrd4ex,
  columns = list(
    W1 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W2 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W3 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W4 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W5 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center")

  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 70),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### N3

```{r, echo=FALSE, message=FALSE}

wrd3ex <- wrd3ex[sample(1:nrow(wrd3ex)),]

reactable(
  wrd3ex,
  columns = list(
    W1 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W2 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W3 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W4 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W5 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center")

  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 70),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### N2

```{r, echo=FALSE, message=FALSE}

wrd2ex <- wrd2ex[sample(1:nrow(wrd2ex)),]

reactable(
  wrd2ex,
  columns = list(
    W1 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W2 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W3 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W4 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W5 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center")

  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 70),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### N1

```{r, echo=FALSE, message=FALSE}

wrd1ex <- wrd1ex[sample(1:nrow(wrd1ex)),]

reactable(
  wrd1ex,
  columns = list(
    W1 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W2 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W3 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W4 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center"), 
    W5 = colDef(minWidth = 83, style = list(fontSize = 17, fontWeight = 500), align = "center")

  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 70),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

<!-- ## Phrases {.tabset} -->

<!-- ```{r, echo=FALSE, message=FALSE} -->

<!-- grphrs <- grphrs[sample(1:nrow(grphrs)),] -->

<!-- reactable( -->
<!--   grphrs, -->
<!--   columns = list( -->
<!--     S1 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         T1 <- grphrs$T1[index] -->
<!--         T1 <- if (!is.na(T1)) T1 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 15, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 8), T1), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->
<!--     S2 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         T2 <- grphrs$T2[index] -->
<!--         T2 <- if (!is.na(T2)) T2 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 15, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 8), T2), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ),     -->
<!--     S3 = colDef( -->
<!--       cell = function(value, index) { -->
<!--         T3 <- grphrs$T3[index] -->
<!--         T3 <- if (!is.na(T3)) T3 else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 15, fontWeight = 500), value), -->
<!--           div(style = list(fontSize = 8), T3), -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ),    -->

<!--     T1 = colDef(show = FALSE), -->
<!--     T2 = colDef(show = FALSE), -->
<!--     T3 = colDef(show = FALSE) -->

<!--   ),  -->


<!--   defaultPageSize = 5, -->
<!--   theme = reactableTheme( -->
<!--     # Vertically center cells -->
<!--     cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 70), -->
<!--     searchInputStyle = list( -->
<!--       paddingLeft = "8px", -->
<!--       paddingTop = "8px", -->
<!--       paddingBottom = "8px", -->
<!--       width = "100%" -->
<!--     ) -->
<!--   ), -->
<!--   showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", -->

<!--   style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px") -->
<!-- ) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

## Grammar {.tabset}

### N1 {.tabset}

#### 1

❆ **あえて** `dare to・daringly・deliberately・purposely`

<h6>

**⚭　aete + action**

</h6>

    ・あえて反対はしない
    ・あえて論評するほどのことではない
    ・彼は天才であると言ってもあえて過言ではない

<!-- <h> -->

    ・I dare not disagree.
    ・It's not worth daring to comment on.
    ・I dare say he is a genius.

❆ **あくまでも** `to the end・to the last・persistency`

<h6>

**⚭　akumademo + N・V**

</h6>

    ・彼は飽くまでも否定した
    ・飽くまでも戦い抜く
    ・彼は提案に飽くまでも反対した

<!-- <h> -->

    ・He denied it to the end.
    ・We'll fight it out to the end.
    ・He was tirelessly opposed to the proposal.

<!-- ------------------------------------------------------------------------ -->

#### 2

<!-- ------------------------------------------------------------------------ -->

#### 3

<!-- ------------------------------------------------------------------------ -->

### N2 {.tabset}

#### 1

❆ **あるいは** `or・possibly`

<h6>

**⚭　aruiwa + N・Phrase**

</h6>

    ・英語かあるいはフランス語かどちらかが必修です
    ・人々はあるいは海へあるいは山へと出かけた
    ・あるいはそうかもしれない

<!-- <h> -->

    ・Either English or French is required.
    ・Some people went to the sea and others to the mountains.
    ・Perhaps it is so.

❆ **ぶりに** `for the first time in (time period)`

<h6>

**⚭　N (time period) + burini**

</h6>

    ・彼に会うのは５年ぶりだった
    ・兄が10年ぶりで故郷へ帰って来た
    ・これは７年ぶりの豊作だ

<!-- <h> -->

    ・I hadn't seen him in five years.
    ・My brother came home for the first time in 10 years.
    ・This is the first good crop in seven years.

❆ **もとに** `based on・derived from`

<h6>

**⚭ N + wo + motoni・motonishite**

</h6>

    ・試験の結果をもとにしてクラス分けを行います
    ・Will be placed in classes based on the results of the exam.

<!-- ------------------------------------------------------------------------ -->

#### 2

<!-- ------------------------------------------------------------------------ -->

#### 3

<!-- ------------------------------------------------------------------------ -->

### N3 {.tabset}

#### 1

❆ **始める** `started to・begin to`

<h6>

**⚭ Vnoun-stem + hajimeru**

</h6>

    ・日本語を習い始めたのは半年前です  
    ・I started learning Japanese six months ago

❆ **終わる** `to end・done doing・finish doing`

<h6>

**⚭ Vnoun-stem + owaru**

</h6>

    ・その本読み終わったら貸してもらえませんか  
    ・When you finish reading that book, can I borrow it?

❆ **ように言われる** `I get/got told・I was told`

<h6>

**⚭ Vru・Vnai+ you ni iwareru**

</h6>

    ・医者にお酒を飲まないように言われました
    ・The doctor told me not to drink alcohol

❆ **ように注意させる** `I get/got cautioned・I was cautioned`

<h6>

**⚭ Vru・Vnai+ you ni chuui sareru**

</h6>

    ・先生に宿題を忘れないように注意された
    ・The teacher cautioned me not to forget my homework

❆ **ようにら飲まれる** `I get/got asked・I was asked`

<h6>

**⚭ Vru・Vnai+ you ni tanomareru**

</h6>

    ・佐藤さんに会議の前に資料をコピーしておくように頼まれた
    ・Mr. Sato asked me to make copies of the documents before the meeting

❆ **ようにいう** `I tell/told`

<h6>

**⚭ Vru/Vnai+ you ni iu**

</h6>

    ・医者にお酒を飲まないように言った
    ・I told the doctor not to drink alcohol

❆ **ように注意する** `I caution/cautioned`

<h6>

**⚭ Vru・Vnai+ you ni chuui suru**

</h6>

    ・先生に宿題を忘れないように注意した
    ・I cautioned the teacher not to forget my homework

❆ **ように頼む** `I ask/asked`

<h6>

**⚭ Vru・Vnai+ you ni tanomu**

</h6>

    ・佐藤さんに会議の前に資料をコピーしておくように頼んだ
    ・I asked Ms. Sato to make copies of the materials before the meeting

❆ **ように言ってください** `please tell him`

<h6>

**⚭ Vru・Vnai+ you ni itte kudasai**

</h6>

    ・彼にもっと勉強するように言ってください
    ・Please, tell him to study harder

❆ **ようにお願いしてください**`please ask him`

<h6>

**⚭ Vru・Vnai+ you ni onegaishite kudasai**

</h6>

    ・社長に残業を減らすようにお願いしてくださいよ
    ・Please, ask the president to reduce overtime.

❆ **ように注意してください** `please caution him`

<h6>

**⚭ Vru・Vnai+ you ni chuuishite kudasai**

</h6>

    ・彼にもっと時間を守るよう注意してください
    ・Please, remind him to be more punctual

❆ **という** `describes something (external relative clause)` **⚭ Plain-form + toiu + N**

</h6>

    ・最近は大学卒業しても就職が難しいという話を聞きました
    ・I've heard that it's difficult to find a job after graduating from college these days

❆ **だろうと思う** `I guess/think that it seems/probably`

<h6>

**⚭ Plain-form + darou + to omou**

</h6>

    ・外国で一人暮らしをするのは寂しいだろうと思う
    ・I think it seems to be lonely to live alone in a foreign country

❆ **なさそうだ** `It looks/seems that its not`

<h6>

**⚭ I-Adj・Na-Adj+ja・N+ja + nasasou da・datta**

</h6>

    ・この仕事はそんなに大変じゃなさそうだ
    ・This kind of a job doesn't seem so hard

❆ **そうもない** `It looks/seems that its not`

<h6>

**⚭ Vnoun-stem + soumonai・souninai・sounimonai**

</h6>

    ・こんな難しそうな本１週間では読めそうもない
    ・I don't think I can read such a difficult book in a week

<!-- ------------------------------------------------------------------------ -->

#### 2

❆ **と** `if・when (noticed something you had not been aware until that time)`

<h6>

**⚭ Vru + to**

</h6>

    ・待ち合わせの場所に着くと友達はもう来ていた  
    ・When I arrived at the meeting, my friend had already come

❆ **たら** `if・when (noticed something you had not been aware until that time)`

<h6>

**⚭ Vru + tara**

</h6>

    ・屋上に上がったら東京スカイツリー見えた  
    ・I went up to the rooftop and saw the Tokyo Sky Tree

❆ **ほど** `to that extent (describe unusual condition/degree)`

<h6>

**⚭ Vru・Vnai・I-Adj・Na-Adj・N + hodo**

</h6>

    ・富士山登って降りてきた時はもう一歩も歩けないほど疲れていた  
    ・When I climbed Mt. Fuji and came down, I was so tired I couldn't take another step

❆ **ていく** `go after doing・do go・go away・to keep (temporal and spatial changes/action)`

<h6>

**⚭ Vte + iku**

</h6>

    ・冬になると渡り鳥は南の方へ飛んでいく  
    ・In the winter, migratory birds fly south

❆ **てくる** `come back after doing・do come・come in・to continue (temporal, spatial & perceptional changes)`

<h6>

**⚭ Vte + kuru**

</h6>

    ・日本じんは昔から魚を食べてきました  
    ・Japanese carrots have been eating fish for a long time

❆ **続ける** `action going on continuously`

<h6>

**⚭ Vnoun-stem + tsuzukeru**

</h6>

    ・この薬は途中でやめないで1週間飲み続けてください  
    ・Please do not stop taking this medicine halfway, but continue taking it for one week

❆ **なら** `if・when (clause sets limit and to provide advice, suggestion or course of action)`

<h6>

**⚭ Vru・N + nara**

</h6>

    ・北海道へ旅行に行くなら2月が一番いいと思いますよ  
    ・If you are going on a trip to Hokkaido, February is the best time to go.

<!-- ------------------------------------------------------------------------ -->

#### 3

❆ **って** `called (give a name)`

<h6>

**⚭ N + tte + N**

    ・長野県の戸隠ってとこる  
    ・A place called Togakushi in Nagano Prefecture

❆ **せてもらう** `I have/had someone let me (obtain permission from another person)`

<h6>

**⚭ Vsasete + morau**

</h6>

    ・ここに荷物を置かせてもらってもいいですか  
    ・Do you mind if I put my stuff here?

❆ **せてくれる** `Someone let me (someone give me permission)`

<h6>

**⚭ Vsasete + kureru**

</h6>

    ・この会社は自分の意見を自由に言わせてくれる  
    ・This company allows me to express my opinions freely

❆ **ていく** `go after doing・do go・go away・to keep (temporal and spatial changes/action)`

<h6>

**⚭ Vte + iku**

</h6>

    ・冬になると渡り鳥は南の方へ飛んでいく  
    ・In the winter, migratory birds fly south

❆ **てくる** `come back after doing・do come・come in・to continue (temporal, spatial & perceptional changes)`

<h6>

**⚭ Vte+ kuru**

</h6>

    ・日本じんは昔から魚を食べてきました  
    ・Japanese carrots have been eating fish for a long time

❆ **続ける** `action going on continuously`

<h6>

**⚭ Vnoun-stem + tsuzukeru**

</h6>

    ・この薬は途中でやめないで1週間飲み続けてください  
    ・Please do not stop taking this medicine halfway, but continue taking it for one week

❆ **なら** `if・when (clause sets limit and to provide advice, suggestion or course of action)`

<h6>

**⚭ Vru・N + nara**

</h6>

    ・北海道へ旅行に行くなら2月が一番いいと思いますよ  
    ・If you are going on a trip to Hokkaido, February is the best time to go.

<!-- ------------------------------------------------------------------------ -->

#### 4

❆ **別に\~ない** `ifn(Expressing that nothing is special)`

<h6>

**⚭ betsu ni + Vnai・N+dewanai・I-Adj+kunai・Na-Adj+dewanai**

</h6>

    ・別にかまわないよ  
    ・I dont really care

❆ **ようなら** `if (if something/someone in this situation, then)`

<h6>

**⚭ Vplain・I-Adj・N+no・Na-Adj+na + you nara**

</h6>

    ・体の調子が悪いようなら病院に行ってください  
    ・if you feel bad, please go to the hospital

❆ **うちに** `before・while (do something before a state or a situation changes)`

<h6>

**⚭ Vplain・I-Adj・Na-Adj・N+no + uchini**

</h6>

    ・溶けないうちに早く食べてください 
    ・Eat quickly before it melts

❆ **うちに** `while (express a process or action is happening a change also happens)`

<h6>

**⚭ Vplain・I-Adj・Na-Adj・N+no + uchini**

</h6>

    ・音楽を聞いているうちに眠ってしまった 
    ・I fell asleep while listening to the music

❆ **てからでないと** `until・unless (until or unless something happens/done, it cannot happens/be done)`

<h6>

**⚭ Vte + tekaradenaito**

</h6>

    ・高いものなので、家族と相談してからでないと買うかどうか決められませんね
    ・It's an expensive item, so I'll have to discuss it with my family before deciding whether or not to buy it

❆ **てからでなければ**`until・unless (unless something happens/done, it cannot happen/be done)`

<h6>

**⚭ Vte + tekaradenakereba**

</h6>

    ・運転免許を取ってからでなければ車を運転しては行けません
    ・You must have a driver's license before you can drive a car

<!-- ------------------------------------------------------------------------ -->

#### 5

❆ **には..がいる・がある・が多い** `Cohessive-patterns・Emphasized-target-Existence・State`

<h6>

**⚭ \~niwa + \~ga iru・ga aru・ga ooi**

</h6>

    ・世界にはいろいろな文化を持った国がある 
    ・この計画には問題点が多い 

<!-- <h> -->

    ・There are many different cultures in the world. 
    ・There are many problems with this plan. 

❆ **には・のに(は)..が必要だ・が便利だ・なければならない・がかかる** `Cohessive-patterns・Purpose-Action・Remarks`

<h6>

**⚭ \~niwa・noni(wa) + \~ga hitsuyou・ga benri・nakerebanaranai・ga kakaru**

</h6>

    ・この仕事をするには車の運転できなければならない 
    ・外国へ行くのにはぱパスポートが必要だ

<!-- <h> -->

    ・I have to be able to drive a car to do this job. 
    ・I need a passport to go abroad.

❆ **のは..だ・からだ・ためだ** `Cohessive-patterns・Normalized-clause-Explanation`

<h6>

**⚭ \~nowa + \~da・karada・tameda**

</h6>

    ・私が祖母について思い出せるのは優しい笑顔でけだ
    ・昨夜家に帰れなかったのは急ぎの仕事が終わらなかったからです

<!-- <h> -->

    ・All I can remember about my grandmother is her kind smile.
    ・I didn't come home last night because I had some urgent work to finish.

❆ **どうして・なぜ〜かというと..からだ** `Cohessive-patterns・Cause-Reason`

<h6>

**⚭ doushite・naze \~katouito + \~karada**

</h6>

    ・どうしてこの植物にあまり水をやらないかというとその方が綺麗な花が咲くからです
    ・なぜこの仕事を選んだかというと子供のときから動物が好きだったからです

<!-- <h> -->

    ・The reason why I don't water this plant very much is because it blooms more beautifully.
    ・The reason why I chose this job is because I have loved animals since I was a child.

❆ **まもなく・もうすぐ・やがて・来年** `Cohessive Patterns・Adverb-time-Verb-state`

<h6>

**⚭ mamonaku・mousugu・yagate・rainen + \~Vru**

</h6>

    ・来年この子は５歳になる 
    ・Next year this boy will be five years old.

❆ **今・現在 + ..Vteiru** `Cohessive-patterns・Adverb-time-Verb-state`

<h6>

**⚭ ima・genzai + \~Vteiru**

</h6>

    ・現在雪が降っている 
    ・It is currently snowing. 

❆ **去年・先週 + ..Vta** `Cohessive-patterns・Adverb-time-Verb-state`

<h6>

**⚭ kyonen・senshuu + \~Vta**

</h6>

    ・去年私は日本に来た 
    ・Last year I came to Japan.

<!-- ------------------------------------------------------------------------ -->

#### 6

❆ **ないと** `have to (should or have to do)`

<h6>

**⚭ Vneg-stem + nakya・nakucha・naito**

</h6>

    ・あ、もう８時だ。そろそろ出かけないと
    ・Oh, it's 8 o'clock already. I have to go out soon.

❆ **っけ** `what was it? (confirm an info that was forgotten)`

<h6>

**⚭ Vru+nda・ndatta・Vta・I-Adj+katta・Na-Adj+da・datta・N+da・datta + kke**

</h6>

    ・これどうやって食べるんだったっけ
    ・How should I eat this again?

❆ **疑問視 + か** `cite or refer to a question`

<h6>

**⚭ Question-word \~ Vru + ka + (kiku・shitteiru・wakaru・oshieru・oboeteiru・etc)**

</h6>

    ・何を買うかわからない
    ・I don't know what I'll buy

❆ **かどうか** `whether or not (cite or refer to a question)`

<h6>

**⚭ Vru + ka + (kiku・shitteiru・wakaru・oshieru・oboeteiru・etc)**

</h6>

    ・出かける前に鍵をかけるかどうか覚えていません
    ・I can't remember if I lock the door before I leave.

❆ **ている** `continuous action (progressive)`

<h6>

**⚭ Vte + iru**

</h6>

    ・あそこで新聞を読んでいる人知っている？
    ・Do you know who's reading the newspaper over there?

❆ **ている** `continuous state (resultative)`

<h6>

**⚭ Vte + iru**

</h6>

    ・いい天気です。空が晴れています
    ・It's a beautiful day. The sky is clear.

❆ **ている** `habitual・routine state (repeatitive)`

<h6>

**⚭ Vte + iru**

</h6>

    ・あの店では新しい野菜を売っています
    ・That vegetable store sells fresh vegetables.

❆ **てしまう** `whether or not (cite or refer to a question)`

<h6>

**⚭ Vte + shimau・chau・jau**

</h6>

    ・小遣いはもう使ってしまったの?
    ・Have you spent your allowance already?

❆ **ておく** `to do something in advance`

<h6>

**⚭ Vte + oku・Vtoku**

    ・このビールを冷蔵庫に入れといて
    ・Put this beer in the fridge (in advance).

❆ **ようにいう** `says・tells (tells, cite or refer to an order, request, or piece of advice)`

<h6>

**⚭ Vru・Vnai + youni iu)**

</h6>

    ・先生はみんなにもっと勉強するよう言った
    ・The teacher told everyone to study harder.

❆ **ように言われる** `told by someone (tells, cite or refer to an order, request by someone)`

<h6>

**⚭ Vru・Vnai + youni iwareru)**

</h6>

    ・医者にお酒を飲まないように言われた
    ・The doctor told me not to drink alcohol.

<!-- ------------------------------------------------------------------------ -->

### N4 {.tabset}

#### 1

❆ **あまり\~ない** `not very・not much`

<h6>

**⚭ amari + Vnai・N+janai・I-Adj+kunai・Na-Adj+janai**

</h6>

    ・鶏肉はあまり好きじゃないです  
    ・香港はあまり寒くない
    ・私はあまり眠くない

<!-- <h> -->

    ・I don't like chicken very much.  
    ・It's not so cold in Hong Kong.
    ・I am not very sleepy.

❆ **後で** `after・later`

<h6>

**⚭ Vta・N+no + atode**

</h6>

    ・昼ごはんの後で友達とお茶を飲みました  
    ・After lunch, I had a cup of tea with a friend.

❆ **ば** `if..then`

<h6>

**⚭ Vcmd-stem + ba → Vba**

</h6>

    ・このボタンを押せばドアが開きます  
    ・If you press this button, the door wil open.

❆ **場合は** `if・in the case・in the event of`

<h6>

**⚭ Vplain・N+no・Na-Adj+na + baai wa**

</h6>

    ・もし無理な場合は注文をキャンセルします 
    ・If this is not possible, We will be cancel the order.

❆ **場合に** `if・in the case・in the event of`

<h6>

**⚭ Vplain・N+no・Na-Adj+na + baai ni**

</h6>

    ・ロブスターは特別な場合にしか食べない
    ・I only eat lobster on special occasions.

❆ **だけで** `just by・just by doing`

<h6>

**⚭ Vplain・N + dake de**

</h6>

    ・一目見ただけで俺に必要なことは全てわかった
    ・At first glance I knew everything I needed.

<!-- ------------------------------------------------------------------------ -->

#### 2

❆ **出す** `suddenly`

<h6>

**⚭ Vnoun-stem + dasu**

</h6>

    ・雨が突然降り出した  
    ・Rain came down suddenly.

❆ **でも** `even・or anything`

<h6>

**⚭ N + demo**

</h6>

    ・私はコーヒーでも飲みたい  
    ・I want to drink coffee.

<!-- ------------------------------------------------------------------------ -->

### N5 {.tabset}

#### 1

❆ **は** `indicates the topic`

<h6>

**⚭ N + wa**

</h6>

    ・私はカナダから来ました 
    ・I come from Canada.

❆ **は** `indicates comparison of topics`

<h6>

**⚭ N + wa .. ga .. N + wa**

</h6>

    ・私は肉は食べますが魚は食べません 
    ・I eat meat, but not fish.

❆ **は** `indicates emphasis on the action or state`

<h6>

**⚭ N + wa .. N + ga**

</h6>

    ・東京は人が多いです 
    ・Tokyo is very crowded.  

❆ **が** `indicates and emphasize the subject`

<h6>

**⚭ N + ga**

</h6>

    ・車が早いです 
    ・The car is fast.

❆ **が** `attached to a question word`

<h6>

**⚭ Question-word + ga**

</h6>

    ・どれが田中さんのコップですか 
    ・Which one is Mr. Tanaka's cup?  

❆ **を** `leaving a place`

<h6>

**⚭ N + wo**

</h6>

    ・東京駅で電車を降ります 
    ・Get off the train at Tokyo Station.   

❆ **を** `express place of passage`

<h6>

**⚭ N + wo**

</h6>

    ・毎朝公園を散歩します 
    ・I take a walk in the park every morning.

❆ **と** `express beign together with someone`

<h6>

**⚭ N + to**

</h6>

    ・母と買い物をしました 
    ・I did some shopping with my mother.

<!-- ------------------------------------------------------------------------ -->

#### 2

❆ **に** `indicates destination`

<h6>

**⚭ N + ni**

</h6>

    ・友達誕生日パーティーに行きます 
    ・I'm going to a friend's birthday party.

❆ **に** `indicates a point in time`

<h6>

**⚭ N + ni**

</h6>

    ・月曜日にきて下さい 
    ・Please come back on Monday.

❆ **に** `indicates a period of time`

<h6>

**⚭ N + ni**

</h6>

    ・彼女は１週間に１度ピアノのレッスンを受ける 
    ・She takes piano lessons once a week.

❆ **に** `indicates the recepient of the action`

<h6>

**⚭ N + ni**

</h6>

    ・友達に会います 
    ・I'm meeting a friend.

❆ **に** `indicates place of existence`

<h6>

**⚭ N + ni**

</h6>

    ・駅の前にデパートがあります 
    ・There is a department store in front of the station.

❆ **で** `indicates place of action`

<h6>

**⚭ N + de**

</h6>

    ・図書館で勉強します 
    ・I'll study at the library. 

❆ **で** `indicates means, way or method`

<h6>

**⚭ N + de**

</h6>

    ・電車で行きます 
    ・I'll go by train. 

❆ **で** `use as ingredient or material`

<h6>

**⚭ N + de**

</h6>

    ・肉と野菜で料理を作りました 
    ・I cooked with meat and vegetables.

❆ **で** `termination of time`

<h6>

**⚭ N + de**

</h6>

    ・もう二週間で夏休みになります 
    ・It will be summer vacation in two weeks.

❆ **で** `indicates range`

<h6>

**⚭ N + de**

</h6>

    ・世界で一番長い川はナイル川です 
    ・The longest river in the world is the Nile.

❆ **で** `indicates reason`

<h6>

**⚭ N + de**

</h6>

    ・病気で学校を休みました
    ・I missed school because I was sick.

❆ **も** `express similar situation or things`

<h6>

**⚭ N + mo**

</h6>

    ・私もパーティーに行きます 
    ・I'm going to the party too.

<!-- ------------------------------------------------------------------------ -->

#### 3

❆ **か** `or`

<h6>

**⚭ N + ka + N (ka)**

</h6>

    ・明日か明後日田中さんに電話します 
    ・I'll call Mr. Tanaka tomorrow or the next day.

❆ **や** `and`

<h6>

**⚭　N + ya + N**

</h6>

    ・駅の前にはコンビニや銀行があります 
    ・There are convenience stores and banks in front of the station.

❆ **だ・です** `copula`

<h6>

**⚭ Na-Adj・N + da・desu**

</h6>

    ・それは非常に面白いコメントですね 
    ・That's a very interesting comment. 

❆ **など** `etc`

<h6>

**⚭ N + ya + N + nado**

</h6>

    ・駅の前にはコンビニや銀行などがあります 
    ・There are convenience stores, banks and etc in front of the station.

❆ **から\~まで** `from~until`

<h6>

**⚭ N + kara + N + made**

</h6>

    ・テストは15日から18日までです 
    ・The test will be from the 15th to the 18th.

❆ **ごろ** `around (point in time)`

<h6>

**⚭ N + goro**

</h6>

    ・明日の昼ごろ来てください 
    ・Please come back tomorrow around noon.

❆ **くらい** `about・around (approx. amount or degree)`

<h6>

**⚭ N + kurai・gurai**

</h6>

    ・四冊くらい
    ・百人くらい
    ・駅までタクシーで1000円ぐらいかかります 
    ・家から学校までどのぐらいかかりますか
    ・きむさんはどれぐらい日本語勉強していますか
    ・その車はいくらぐらいでしたか

<!-- <h> -->

    ・About four books.
    ・About a hundred people.
    ・It costs about 1,000 yen to take a cab to the station.
    ・Approximately, how long does it take from your home to school?
    ・About how long does Mr. Kim is studying Japanese?
    ・About how much was that car?

❆ **だけ** `only・just`

<h6>

**⚭　Vplain・I-Adj・Na-Adj+na・N + dake**

</h6>

    ・10分だけ休みましょう 
    ・ほかに一つだけ可能性がある
    ・朝はコーヒーをいっぱい飲むだけです 
    ・この本は高いだけでおもしりくない
    ・あの先生には一度だけ会いました
    ・テニスは好きなだけで上手じゃない 

<!-- <h> -->

    ・Let's just rest for ten minutes.
    ・There's only one other possibility.
    ・In the morning, I just drink a cup of coffee, that’s all
    ・This book is just expensive and is not interesting
    ・I met that professor only once
    ・I just like tennis and I’m not good at it

❆ **では** `location of action & emphasis`

<h6>

**⚭ N + de wa**

</h6>

    ・会社の食堂で食べます
    ・I'll eat at the company cafeteria.

❆ **へは** `direction & emphasis`

<h6>

**⚭ N + e wa**

</h6>

    ・東京駅へは何で行きますか
    ・Why do you go to Tokyo Station?

❆ **には** `place of existence & emphasis`

<h6>

**⚭ N + ni wa**

</h6>

    ・この町には図書館がありません
    ・There is no library in this town.

<!-- ------------------------------------------------------------------------ -->

#### 4

❆ **だれ** `who`

<h6>

**⚭ dare・donata**

</h6>

    ・これはだれのペンですか 
    ・Whose pen is this?

❆ **なに** `what`

<h6>

**⚭ nani・nan**

</h6>

    ・これはなに本ですか 
    ・What book is this?

❆ **どこ** `where`

<h6>

**⚭ doko**

</h6>

    ・駅の前にはコンビニや銀行などがあります 
    ・There are convenience stores, banks and etc in front of the station.

❆ **どちら** `which`

<h6>

**⚭ dochira**

</h6>

    ・お国はどちらですか？ 
    ・Which country are you from? 

❆ **どう** `how・what`

<h6>

**⚭ dou**

</h6>

    ・あなたの旅はどうでしたか？
    ・How was your trip?

❆ **どうやって** `how・in what way`

<h6>

**⚭ douyatte**

</h6>

    ・どうやってそれを知ったのですか？ 
    ・How do you know that?

❆ **何で** `how・why`

<h6>

**⚭ nande**

</h6>

    ・なんでもっと早く言ってくれなかったの？
    ・Why didn't you tell me earlier?

❆ **どうして** `how・why`

<h6>

**⚭ doushite**

</h6>

    ・その赤ちゃんはどうして泣くの？
    ・Why is that baby crying?

❆ **なぜ** `why`

<h6>

**⚭ naze**

</h6>

    ・なぜ今日は駅にタクシーが全く無いのだろう
    ・Why are there no taxis at the station today?

❆ **どんな** `what kind of`

<h6>

**⚭ donna + N**

</h6>

    ・どんな音楽が好きですか 
    ・What kind of music do you like?

❆ **どの** `which`

<h6>

**⚭ dono + N**

</h6>

    ・私にはどのサイズが合うでしょうか 
    ・What size do you think I take?

❆ **いくつ** `how many・how old`

<h6>

**⚭ ikutsu**

</h6>

    ・帽子はいくつ持ってるんですか
    ・How many caps do you own?

❆ **どちら** `which・which one・which way・where`

<h6>

**⚭ dochira**

</h6>

    ・ジャイアンツとドラゴンズのどちらが好きですか
    ・Which do you like better, the Giants or the Dragons?

❆ **いつ** `when`

<h6>

**⚭ itsu**

</h6>

    ・いつ東京に行くの？
    ・When are you going to Tokyo?

<!-- ------------------------------------------------------------------------ -->

#### 5

❆ **なにか** `something`

<h6>

**⚭ nanika**

</h6>

    ・お腹がすきましたね。何か食べましょう 
    ・I'm starving. Let's get something to eat. 

❆ **どこか** `somewhere`

<h6>

**⚭ dokoka**

</h6>

    ・明日どこかに行きますか 
    ・Are you going somewhere tomorrow?

❆ **だれか** `someone`

<h6>

**⚭ dareka**

</h6>

    ・教室に誰かいますか 
    ・Is there someone in the classroom?

❆ **いつか** `sometime`

<h6>

**⚭ itsuka**

</h6>

    ・いつかフランスに行きたいです？ 
    ・I want to go to France someday.

❆ **だれも\~ません** `no one`

<h6>

**⚭ daremo\~masen・nai desu**

</h6>

    ・誰もないです
    ・No one.

❆ **どこにも\~ません** `nowhere・not anywhere`

<h6>

**⚭ dokonimo\~masen・nai desu**

</h6>

    ・どこにも行かなかったです 
    ・I didn't go anywhere.

❆ **なにも\~ません** `nothing・won't anything`

<h6>

**⚭ nanimo\~masen・nai desu**

</h6>

    ・何も食べなかったです
    ・I did not eat anything.

❆ **どれでも** `whichever・any of them`

<h6>

**⚭ doredemo**

</h6>

    ・どれでも100円です？
    ・Any of them is 100 yen.

❆ **なんでも** `anything`

<h6>

**⚭ nandemo**

</h6>

    ・私は何でも食べます
    ・I'll eat anything.

❆ **だれでも** `anyone・anybody`

<h6>

**⚭ daredemo**

</h6>

    ・この問題は誰でもできます 
    ・Anyone can do this problem.

❆ **いつでも** `anytime`

<h6>

**⚭ itsudemo**

</h6>

    ・いつでも来てください 
    ・Come back anytime.

❆ **どこでも** `anywhere`

<h6>

**⚭ dokodemo**

</h6>

    ・どこでも行きます
    ・I'll go anywhere.

❆ **どうですか** `how・how about`

<h6>

**⚭ dou desu ka**

</h6>

    ・コーヒーはどうですか
    ・How about some coffee?

❆ **いかがですか** `how・how about`

<h6>

**⚭ ikaga desu ka**

</h6>

    ・新しい会社はいかがですか
    ・How's the new company?

<!-- ------------------------------------------------------------------------ -->

#### 6

❆ **で** `te-form (connective form)`

<h6>

**⚭ N・Na-Adj + de**

</h6>

    ・先生は綺麗で優しいです 
    ・The teacher is beautiful and kind.

❆ **なくて** `te-form (connective form - negative)`

<h6>

**⚭ N・Na-Adj + ja・dewa + nakute**

</h6>

    ・あの人は先生じゃなくて学生です 
    ・He is not a teacher, He is a student.

❆ **くて** `te-form (connective form)`

<h6>

**⚭ I-Adj + kute**

    ・このバッグは色もよくて形もいいです 
    ・This bag has a nice color and a nice shape.

❆ **なくて** `te-form (connective form - negative)`

<h6>

**⚭ I-Adj+ku + nakute**

</h6>

    ・昨日のレストランはお美味しくなくて高かったです 
    ・Yesterday's restaurant was not good and expensive.

❆ **て** `te-form (connective form)`

<h6>

**⚭ Vte**

</h6>

    ・朝起きて朝ごはんを食べて散歩に行きます 
    ・I wake up, eat breakfast, and go for a walk.

❆ **てから** `After doing`

<h6>

**⚭ Vte + kara**

</h6>

    ・手を洗ってからご飯を食べましょう
    ・After washing hands, Let's eat.

❆ **それから**`and then・after that`

<h6>

**⚭ sorekara**

</h6>

    ・ピザをお願いします。それからコーヒーもお願いします
    ・I'll have a pizza, please. And then some coffee, please.

❆ **そして** `and・and the`

<h6>

**⚭ soshite**

</h6>

    ・兄が頭がいいです。そして優しいです 
    ・My brother is very smart. And he's kind. 

❆ **から** `because・since`

<h6>

**⚭　Vplain・I-Adj・Na-Adj+da・N+da + kara**

</h6>

    ・宿題がいっぱいあるから、遊べない
    ・一生懸命勉強したから大学入学試験位合格した
    ・寒いから、窓を閉めてください
    ・あの人はいつもとてもしずかだから、一度も話したことがない
    ・大事なしけんだから、がんばる

<!-- <h> -->

    ・I can't play because I have a lot of homework
    ・I passed the university entrance examination because I studied hard
    ・Please close the window because its cold
    ・That person is always really quiet, so I haven’t ever talked to them
    ・This is a very important test, so I will do my best!

❆ **けれども** `but・although・though`

<h6>

**⚭　Vplain・I-Adj・Na-Adj+da・N+da + keredemo・kedo**

</h6>

    ・入ってもいいけどしずかにしてくださいね
    ・あそびたいけど宿題はまだ終わってない
    ・これは給料は良くないけどやりがいのある仕事だ

<!-- <h> -->

    ・You can enter but please be quite
    ・I want to play but my homework isn't over yet
    ・This is a poorly paid but rewarding job

<!-- ------------------------------------------------------------------------ -->

#### 7

❆ **ほしい** `wants something`

<h6>

**⚭ N + ga + hoshii**

</h6>

    ・私は猫が欲しい 
    ・I want a cat.

❆ **たい** `wants to do (tai-form)`

<h6>

**⚭ Vtai (desu)**

</h6>

    ・ステーキが食べたいです 
    ・I want to eat steak.

❆ **ている** `progrssive-action (teiru-form)`

<h6>

**⚭ Vte + iru**

</h6>

    ・今妹はピアノを弾いています 
    ・Now my sister plays the piano.

❆ **ている** `continuous-state (teiru-form)`

<h6>

**⚭ Vte + iru**

</h6>

    ・姉はアメリカに住んでいます 
    ・My sister lives in the United States.

❆ **ている** `habitual-state (teiru-form)`

<h6>

**⚭ Vte + iru**

</h6>

    ・毎日あのお店は新鮮魚介類を売っている 
    ・Every day that store sells fresh seafood.

❆ **てください** `please do..`

<h6>

**⚭ Vte + kudasai**

</h6>

    ・ちょっと待ってください 
    ・Please wait a minute.

❆ **ないでください** `please do not`

<h6>

**⚭ Vnaide + kudasai**

</h6>

    ・タバコは吸わないでください 
    ・Please don't smoke.

❆ **ね** `ending particle (expresses agreement)`

<h6>

**⚭ S + ne**

</h6>

    ・今日もまた雨ですね 
    ・It's raining again today.

❆ **よ** `ending particle (informning)`

<h6>

**⚭ S + yo**

</h6>

    ・雨が降っていますよ 
    ・It's raining.

<!-- ------------------------------------------------------------------------ -->

#### 8

❆ **に\~もらいます** `receive from`

<h6>

**⚭ N + ni.. + moraimasu**

</h6>

    ・クリスマスに母にセーターをもらいました 
    ・I received a sweater from my mother for Christmas.

❆ **から\~もらいます** `receive from`

<h6>

**⚭ N + kara.. + moraimasu**

</h6>

    ・父から時計をもらいました 
    ・I received a watch from my father.

❆ **が\~くれます** `give me`

<h6>

**⚭ N + ga.. + kuremasu**

</h6>

    ・友達がチョコレートをくれました 
    ・My friend gave me some chocolates.

❆ **に\~あげます** `give to`

<h6>

**⚭ N + ni.. + agemasu**

</h6>

    ・妹にこのスカートをあげます 
    ・I'll give this skirt to my sister.

❆ **ましょう** `let's (volitional-polite-form)`

<h6>

**⚭ Vmashou**

</h6>

    ・近いから歩きましょう 
    ・It's close enough. Let's walk.

❆ **ましょうか** `shall (volitional-polite-question-form)`

<h6>

**⚭ Vmashou + ka**

</h6>

    ・明日どこで会いましょうか 
    ・Where shall we meet tomorrow?

❆ **ませんか** `why don't we/you do (masu-polite-negative-question-form)`

<h6>

**⚭ Vmasen + ka**

    ・いい天気ですね。公園に行きませんか
    ・It's a beautiful day. Why don't we go to the park?

❆ **だろう** `probably`

<h6>

**⚭　Vplain・I-Adj・Na-Adj・N + darou**

</h6>

    ・アンダーソンさんは日本へ行くだろう
    ・アンダーソンさんはたぶん日本へ行くだろう
    ・アンダーソンさんはきっと日本へ行くだろう
    ・あのアパートは高いだろう
    ・あの人は中国人だろう
    ・ロジャーはスキーが上手だろう

<!-- <h> -->

    ・Ms. Anderson will probably go to Japan
    ・Ms. Anderson will most probably go to Japan
    ・Ms. Anderson will most likely go to Japan
    ・That apartment is probably expensive
    ・That man is probably Chinese
    ・Roger is probably good at skiing

<!-- ------------------------------------------------------------------------ -->

#### 9

❆ **い形容詞+名詞** `noun modification`

<h6>

**⚭ I-Adj + Noun**

</h6>

    ・綺麗で優しい先生 
    ・Beautiful and kind teacher.

❆ **な形容詞+名詞** `noun modification`

<h6>

**⚭ Na-Adj+na + Noun**

</h6>

    ・優しくて綺麗な先生 
    ・A kind and beautiful teacher.

❆ **名詞+名詞** `noun modification`

<h6>

**⚭ Noun + no + Noun**

</h6>

    ・駅の近くの本屋 
    ・A bookstore near the station

❆ **文節+名詞** `noun modification`

<h6>

**⚭ Adjectival Relative Clause + Noun**

</h6>

    ・髪が長い人 
    ・髪の長い人 

<!-- <H> -->

    ・A person with long hair
    ・A person with long hair

❆ **動詞+名詞** `noun modification`

<h6>

**⚭ Verbal Relative Clause + Noun**

</h6>

    ・田中さんが働いている会社 
    ・昨日買った車  
    ・田中さんが作るごはん    

<!-- <H> -->

    ・The company where Mr. Tanaka works.
    ・The car I bought yesterday.
    ・Food prepared by Mr. Tanaka

<!-- ------------------------------------------------------------------------ -->

## Similars {.tabset}

### Words {.tabset}

#### complex

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 複雑・ふくざつ**</p>

###### **・complex, complicated, intricate, mixed feelings**

    ・それを聞いて複雑な気持ちになった
    ・Hearing it aroused mixed feelings in me

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 煩雑・はんざつ**</p>

###### **・complex, intricate, complicated, confused, troublesome**

    ・煩雑な都会生活を逃れたい
    ・I want to escape the complications of city life

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ ややこしい**</p>

###### **・puzzling, complicated, tangled, complex**

    ・そのややこしい説明では私は訳がわからなくなってしまった
    ・That complicated explanation lost me in translation

<!-- ------------------------------------------------------------------------ -->

#### clear

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 明確・めいかく**</p>

###### **・clear, precise, definite, distinct**

    ・出かける前に明確な計画を立てておいてほしい
    ・I want you to have a clear plan before you go out

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 明らか・あきらか**</p>

###### **・clear, obvious, evident, plain, definite**

    ・何か明らかな違いはあるんですか
    ・Is there any obvious difference?

<!-- ------------------------------------------------------------------------ -->

#### deceive

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 欺く・あざむく**</p>

###### **・to deceive, delude, trick, fool**

    ・敵を欺くにはまず味方を欺かなければならない
    ・To deceive one's enemy, one must first deceive one's friends

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 騙す・だます**</p>

###### **・to trick, cheat, deceive, coax**

    ・彼女は彼の態度に騙された
    ・She was fooled by his attitude

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ 誤魔化す・ごまかす**</p>

###### **・to deceive, falsify, misrepresent, cheat, swindle**

    ・彼は経歴をごまかした
    ・He misrepresented the facts of his career

<!-- ------------------------------------------------------------------------ -->

#### development

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 発展・はってん**</p>

###### **・development, growth, expansion**

    ・その計画は私たちの市を発展させるだろう
    ・That plan would develop our city

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 発達・はったつ**</p>

###### **・development, growth**

    ・スポーツは筋肉の発達に役立つ
    ・She was fooled by his attitude

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ 展開・てんかい**</p>

###### **・development, progression, unfolding, expansion, evolution**

    ・彼は独特の新理論を展開した
    ・He developed a unique new theory

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**④ 開発・かいはつ**</p>

###### **・development, exploitation**

    ・今アンドロイド用アプリを開発しているところだ
    ・We're developing an Android application at the moment

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑤ 現像・げんぞう**</p>

###### **・development of film, photographic processing**

    ・この写真を出来るだけ早く現像して下さい
    ・Please develop this photo as soon as possible

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑥ 進展・しんてん**</p>

###### **・growth, development, growing up**

    ・少年時代の彼の知的成長は実に目覚ましかった
    ・His intellectual growth as a boy was truly remarkable

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑦ 成長・せいちょう**</p>

###### **・progress, development**

    ・交渉はほとんど進展しなかった
    ・Negotiations made little progress

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑧ 発育・はついく**</p>

###### **・physical growth, development**

    ・十分な栄養摂取は幼児の発育にとって極めて重要です
    ・Adequate nutrition is critical to the development of young children

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑨ 進歩・しんぽ**</p>

###### **・progress, advance, improvement, development**

    ・彼女は最近英語が素晴らしく進歩した
    ・She has made wonderful progress in English recently

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑩ 開拓・かいたく**</p>

###### **・reclamation, cultivation, development**

    ・輸入品市場を開拓する多くの努力がなされてきた
    ・Many efforts have been made to develop the market for imported products

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑪ 生育・せいいく**</p>

###### **・birth and growth, development, breeding**

    ・雨の量が作物の生育に影響するのですか
    ・Does the amount of rain affect crop growth?

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑫ 養成・ようせい**</p>

###### **・training, education, development, cultivation**

    ・コンピューター技術者を養成する
    ・Train computer engineers

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑬ 造成・ぞうせい**</p>

###### **・development of land, preparation, reclamation**

    ・その沿岸地方に臨海工業地帯が造成された
    ・A coastal industrial zone was created in that coastal region

<!-- ------------------------------------------------------------------------ -->

#### emergency

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 非常・ひじょう**</p>

###### **・emergency, unusual, extraordinary**

    ・彼は非常に際して沈着に振る舞った
    ・He acted calmly in the emergency

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 応急・おうきゅう**</p>

###### **・emergency, first-aid**

    ・これらの建物は応急の修理が必要です
    ・These buildings need emergency repairs

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ 緊急・きんきゅう**</p>

###### **・urgent, pressing, emergency**

    ・緊急の時はこのボタンを押しなさい
    ・Press this button in case of emergency

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**④ 危機・きき**</p>

###### **・crisis, danger, risk**

    ・危機の時は落ち着かなければならない
    ・We must calm down in times of crisis

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑤ 避難・ひなん**</p>

###### **・taking refuge, finding shelter, evacuation**

    ・津波のため村民は高台に避難した
    ・Villagers evacuated to higher ground because of the tsunami

<!-- ------------------------------------------------------------------------ -->

#### expectation

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 期待・きたい**</p>

###### **・expectation, anticipation**

    ・あの人にはあまり期待しないほうがいいよ
    ・Don't expect too much from that guy

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 予想・よそう**</p>

###### **・expectation, anticipation, prediction**

    ・あなたはどんな結果を予想していますか
    ・What results do you anticipate?

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ 思惑・おもわく**</p>

###### **・expectation, anticipation, prediction, forecast**

    ・株価が思惑通りになった
    ・The stock prices behaved as I expected

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**④ 先見・せんけん**</p>

###### **・foresight, anticipation**

    ・先見の明のある人は最後に成功する
    ・A man of vision will succeed in the end

<!-- ------------------------------------------------------------------------ -->

#### disperse

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 拡散・かくさん**</p>

###### **・scattering, diffusion, spread**

    ・多くのコンピュータワームはネットワーク共有を通じて拡散する
    ・Many computer worms spread through network sharing

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 解散・かいさん**</p>

###### **・breaking up, dispersing, dissolution**

    ・警察がデモ隊を解散させた
    ・The police dispersed the demonstrators

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ 発散・はっさん**</p>

###### **・emission, emanation, radiation, diffusion**

    ・この動物は強いにおいを発散する
    ・This animal emits a strong odor.

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**④ 分散・ぶんさん**</p>

###### **・dispersion, breakup, scattering, decentralization**

    ・工場を地方へ分散させるのが望ましい
    ・It is desirable to decentralize factories to rural areas

<!-- ------------------------------------------------------------------------ -->

#### price

    費用 ・cost, expense   
    値段 ・price, cost   
    代金 ・price, cost, charge, payment, bill, fee  
    価格 ・price, value, cost   
    価値 ・value, worth, merit   
    定価 ・list price, regular price, established price  
    経費 ・expenses, expenditure, outgoings  
    物価 ・prices of commodities, prices in general, cost-of-living   
    会計 ・accounting, finance, account, reckoning, bill at a restaurant   
    勘定 ・calculation, computation, counting, bill, check, account, payment of a bill   
    評価 ・valuation, appraisal, evaluation, assessment, estimation, rating  
    高価 ・highly priced, expensive, valuable, costly  
    高騰 ・sudden price jump, steep price rise  
    相場 ・market price  
    時価 ・current value, price, market value  
    請求書 ・bill, job invoice  

<!-- ------------------------------------------------------------------------ -->

#### expenses

    消費 ・consumption, expenditure   
    浪費 ・waste, extravagance   
    経費 ・expenses, expenditure, outgoings, outlays, costs   
    出費 ・expenses, disbursements   
    消費税 ・consumption tax   
    学費 ・tuition, school expenses   
    燃費 ・fuel consumption, gas mileage   
    会費 ・membership fee   
    旅費 ・travel expenses   
    食費 ・food expense  
    交通費 ・traveling expenses, travelling expenses, carfare   
    自費 ・one's own expense, out-of-pocket expense   
    生活費 ・living expenses,   
    実費 ・actual expenses, out-of-pocket expenses   
    消費量 ・amount of consumption   
    生産費 ・production costs   
    医療費 ・medical expenses, doctor's bill   
    家計費 ・household expenses   
    広告費 ・advertising expenses   
    結婚費用 ・wedding expenses   

<!-- ------------------------------------------------------------------------ -->

#### fee

    料金 ・fee, charge, fare  
    無料 ・free of charge, gratuitous  
    有料 ・fee-charging, paid, not free  
    給料 ・salary, wages, pay  
    送料 ・postage, carriage, shipping charge 
    運賃 ・passenger fare, freight rates, shipping expenses   
    料金 ・fee, charge, fare     
    半額 ・half the amount of money, half price, half fare   

<!-- <h> -->

    乗車券 ・ticket, passenger ticket   
    入館料 ・admission fee   
    入場料 ・entrance fee, admission fee, admission, entrance charge   
    授業料 ・tuition fee, course fee  
    使用料 ・use fee, rent  
    手数料 ・handling fee, charge for a cancellation, commission, brokerage   

<!-- ------------------------------------------------------------------------ -->

#### rule

    規則 ・rule, regulation  
    支配 ・rule, domination, control, management, guidance, influence, sway  
    統治 ・rule, reign, governing  
    主義 ・doctrine, rule, principle  
    法則 ・law, rule 
    規定 ・stipulation, prescription, provision, regulation, rule   
    原則 ・principle, general rule     
    規制 ・regulation, control, restriction   
    統制 ・regulation, control, command and control     

<!-- ------------------------------------------------------------------------ -->

#### establish

    設定 ・establishment, creation, posing, setting  
    設立 ・establishment, founding, incorporation  
    創立 ・establishment, founding, organization  
    確立 ・establishment, settlement  
    樹立 ・establishment, founding, setting a record  
    設置 ・establishment, institution, installation   
    建設 ・establishment, construction     
    成立 ・establishment, formation, materialization   
    施設 ・establishment, institution, facility  
    創設 ・establishment, founding, organization  
    制定 ・establishment, enactment, creation  
    開設 ・establishment, opening, setting up, inauguration   

<!-- <h> -->

    新設 ・establishing, founding, setting up, organizing  
    為す ・establish, build up, form, accomplish, achieve  

<!-- <h> -->

    構える ・set up, build, establish, run, prepare in advance

<!-- ------------------------------------------------------------------------ -->

#### report

    報告 ・report, information  
    申告 ・report, return, statement, declaration  
    報道 ・report, reporting, news, information  
    記事 ・article, news story, report, account  
    通報 ・report, notification, tip, bulletin  
    特集 ・feature, special edition, report   
    情報 ・information, news, intelligence, advices     

<!-- ------------------------------------------------------------------------ -->

#### cooking

    料理 ・cooking, cookery, cuisine, meal, food, dish  
    調理 ・cooking, food preparation  
    炊事 ・cooking, kitchen work  
    自炊 ・cooking for oneself, cooking one's own food  
    割烹 ・cooking especially Japanese style, cuisine  

<!-- <h> -->

    煮炊き ・cooking   
    炊さん ・cooking of rice or grains   
    手料理 ・home cooking    

<!-- <h> -->

    日本料理 ・Japanese cooking    
    中華料理 ・Chinese cooking    

<!-- ------------------------------------------------------------------------ -->

#### search

    探索 ・search, lookup, hunt, research, exploration, investigation  
    捜索 ・search for someone, manhunt  
    捜査 ・search, investigation, inquiry  
    探求 ・search, quest, pursuit  
    追求 ・pursuit, search, chase, seeking after
    探究 ・research, investigation, enquiry, inquiry, study

<!-- <h> -->

    探す ・search for, hunt for, seek
    捜す ・search for, hunt for, seek
    探る ・feel around for, fumble for, search for, look for, investigate, probe, explore

<!-- <h> -->

    探検 ・exploration, expedition

<!-- ------------------------------------------------------------------------ -->

#### suitable

    適切 ・appropriate, suitable, fitting, apt, proper, right, relevant  
    適宜 ・appropriate, suitable, fitting, proper  
    適当 ・suitable, proper, appropriate, adequate, fit, fair   
    相当 ・equivalent to, appropriate, suitable, proportionate  
    妥当 ・valid, proper, right, appropriate, reasonable
    相応 ・suitable, appropriate, befitting, becoming, adequate
    穏当 ・proper, reasonable, right, appropriate
    当該 ・appropriate, concerned, relevant, applicable, competent

<!-- <h> -->

    相応しい ・appropriate, adequate, suitable, fitting, worthy

<!-- ------------------------------------------------------------------------ -->

#### finally

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① やっと**</p>

###### **・at last, at length**

###### ・expresses expectation or intention to happen, be able to happen

    ・長く続いた試合がやっと終わった
    ・The long game was finally over

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② ようやく**</p>

###### **・finally, at last**

###### ・expresses expectation or intention to happen, be able to happen

    ・今日になってようやく事の詳細を知りました
    ・Today I finally learned the details of what happened

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**③ いよいよ**</p>

###### **・finally, at last**

###### ・expresses expectation to happen, be able to happen, more bound to happen

    ・いよいよ今週を限りにしばらくのお休みです
    ・Finally, we are taking a short break after this week

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**④ ついに**</p>

###### **・finally, at last, in the end**

###### ・not planned or wanted to happen, happens naturally

    ・彼の夢がついに実現した
    ・His dream finally came true 

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑤ とうとう**</p>

###### **・finally, at last, ultimately, in the end**

###### ・not planned or wanted to happen, happens naturally

    ・実験を繰り返してとうとう予期した結果を得た
    ・Repeated experiments finally yielded the expected results

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**⑥ けっきょく**</p>

###### **・after all, in the end, ultimately, eventually**

###### ・happens in conclusion

    ・結局会社の役に立ったじゃないか
    ・After all, we did contribute something to our company

<!-- ------------------------------------------------------------------------ -->

### Grammar {.tabset}

#### 向き・向け

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**① 向き**</p>

###### **・suitable for, specially for**

    ・若い女性向きの小説を書いています
    ・このレストランは量が多いから男子学生向きですね

<!-- <h> -->

    ・I write novels for young women
    ・This restaurant is suitable for male students because of the large portions.

<p style="font-size:16px; line-height: 0.5; font-family: Noto Sans JP;  color: #202020; font-weight: bold">**② 向け**</p>

###### **・intended for, aimed at**

    ・最近は男性向けの料理教室が人気だ
    ・ここは女子学生向けの寮ですから男性は入れません

<!-- <h> -->

    ・Cooking classes for men are very popular these days
    ・This is a dormitory for female students, so men are not allowed

<!-- ------------------------------------------------------------------------ -->

## Category {.tabset}

### Connectives {.tabset}

```{r, echo=FALSE, message=FALSE}

exwrds <- exwrd %>% select(Connectives)
exwrds <- exwrds[sample(1:nrow(exwrds)),]

reactable(
  na.omit(exwrds),
  columns = list(
    Connectives = colDef(align = "center", style = list(fontSize = 32, fontWeight = 600))
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 220),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Adverbials {.tabset}

```{r, echo=FALSE, message=FALSE}

exwrds <- exwrd %>% select(Adverbials)
exwrds <- exwrds[sample(1:nrow(exwrds)),]

reactable(
  na.omit(exwrds),
  columns = list(
    Adverbials = colDef(align = "center", style = list(fontSize = 32, fontWeight = 600))
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 220),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Na-Adjectives {.tabset}

```{r, echo=FALSE, message=FALSE}

exwrds <- exwrd %>% select(Na.Adjectives)
exwrds <- exwrds[sample(1:nrow(exwrds)),]

reactable(
  na.omit(exwrds),
  columns = list(
    Na.Adjectives = colDef(align = "center", style = list(fontSize = 32, fontWeight = 600))
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 220),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### I-Adjectives {.tabset}

```{r, echo=FALSE, message=FALSE}

exwrds <- exwrd %>% select(I.Adjectives)
exwrds <- exwrds[sample(1:nrow(exwrds)),]

reactable(
  na.omit(exwrds),
  columns = list(
    I.Adjectives = colDef(align = "center", style = list(fontSize = 32, fontWeight = 600))
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 220),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Onomatope {.tabset}

```{r, echo=FALSE, message=FALSE}

exwrds <- exwrd %>% select(Onomatope)
exwrds <- exwrds[sample(1:nrow(exwrds)),]

reactable(
  na.omit(exwrds),
  columns = list(
    Onomatope = colDef(align = "center", style = list(fontSize = 32, fontWeight = 600))
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 220),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Interrogatives {.tabset}

```{r, echo=FALSE, message=FALSE}

exwrds <- exwrd %>% select(Interrogatives)
exwrds <- exwrds[sample(1:nrow(exwrds)),]

reactable(
  na.omit(exwrds),
  columns = list(
    Interrogatives = colDef(align = "center", style = list(fontSize = 32, fontWeight = 600))
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 220),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## Readings {.tabset}

### N5 {.tabset}

#### 01 {.tabset}

<pre>
<code style="font-size:18px; line-height: 1.4; font-family: Noto Sans JP; font-weight: 300; color: #202020">⓵＿＿＿週まつはとしょかんに行ったりえいがかんでえいがを見たりします。⓶＿＿＿はれているしゅうまつはこうえんであそんだり山にのぼったりします。今週まつははれますからともだちといっしょに　⓷ ＿＿＿。たぶん、グルフのれんしゅうもします。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
  問題（　）に入るものを１・２・３・４から選びなさい。  
  ⓵  
  1. 雨がふっている   2. 雨をふった   3. 雨をふる   4. 雨がふります  
  ⓶  
  1. それに   2.しかし    3. それでは   4. それから  
  ⓷  
  1. 本を読みたいです   2. こうえんに行きたいです   3. としょかんに行きたい   4. いえでえいがを見たいです 
</p>

<!-- ------------------------------------------------------------------------ -->

#### 02 {.tabset}

<pre>
<code style="font-size:18px; line-height: 1.4; font-family: Noto Sans JP; font-weight: 300; color: #202020">レストラン　ブラグを　書いています⓵＿＿　しゅうまつ　いつも　いろいろな　レストランで　食べます。新しいレストランで　りょうりを食べながら　ノートを　取ります。それから、いえにかえって　ブラグを　書きます。ぎおんの　新しい　フランスりょうりのレストラン　行きます。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３・４から選びなさい。  
⓵  
1. まで 2. それから 3. から 4. だから  
⓶  
1. だから 2. それに 3. つぎは 4. しかし  
</p>

<!-- ------------------------------------------------------------------------ -->

#### 03 {.tabset}

<pre>
<code style="font-size:18px; line-height: 1.4; font-family:  Noto Sans JP; font-weight: 300; color: #202020">来週の日よう日は、スキーの りょこうに 行きます。あさの 8 時に 出て よるの 8 時に かえります。お金が 8,000 円 かかります。
行きたい 人は、今週の金よう日までに このかみに 名前を 書いてください。
お金は りょこうの 1日前に 西村先生に わたして ください。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３・４から選びなさい。  
⓵ お金は いつ はらいますか。  
1. 今週の金よう日 2. 今週の土よう日 3. 来週の土よう日 4. 来週の日よう日  
</p>

<!-- ------------------------------------------------------------------------ -->

#### 04 {.tabset}

<pre>
<code style="font-size:18px; line-height: 1.4; font-family:  Noto Sans JP; font-weight: 300; color: #202020">兄は 来月 45 さいに なります。わかいとき からだが　よわくて あまり はたらきませんでした。しかし、今は 毎日 あさに はしります。それから、8 時から よるの 8時まではたらきます。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３・４から選びなさい。  
⓵ ただしい ものは どれですか。  
1. 兄は 今も わかいときも げんきでは ありません。   
2. 兄は 今は げんきですが、わかいとき げんきでは ありませんでした。  
3. 兄は 今も わかいときも げんきです。  
4. 兄は 今は げんきでは ありませんが、わかいとき げんきでした。  
</p>

<!-- ------------------------------------------------------------------------ -->

#### 05 {.tabset}

<pre>
<code style="font-size:18px; line-height: 1.4; font-family:  Noto Sans JP; font-weight: 300; color: #202020">わたしは　あきこさん　10年ぐらい　しっています。がっこうで、　はじめて　あってから　どこでも　いっしょに　行きました。わたしは　あるいて　５分ぐらいの　ところに　すんでいたので、　わたしは　いつも　あきこさんのいえに行きました。毎週まつ　そこで　かわいい　ふくをきて　うたをうたいました。わたしたちは　ゆうめいになりたかったです。
あきこさんは　わたしより　きれいで、せが　たかくて　ほそいです。今、あきこさんはアメリカにりゅうがくしています。あきこさんは　「ゆうめいな人に　なりたい。」と言っています。
わたしは　今は、ゆうめいな人になりたくないです。おかしと　ケーキをべんきょうしています。そして、コーヒーのお店ではたらいています。いつかじぶんの店をもちたいです。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３・４から選びなさい。  
⓵ 10年前　「わたし」と　あきこさんは　何を　していますか。  
1. 「わたし」の　いえで　うたを　うたっていました。   
2. あきこさんの　いえで　あそんでいます。  
3. がっこうで　うたうれんしゅうを　しています。  
4. ふくの　お店へ　買いものに　行っていました。    
⓶ あきこさんは　今、何をしてますか。  
1. コーヒーの　お店で　ケーキを　つくっています。   
2. 外国に　すんでいます。  
3. 日本に　かえってきました。  
4. ゆうめいな　人に　なりました。   
</p>

<!-- ------------------------------------------------------------------------ -->

### N4 {.tabset}

#### 01 {.tabset}

<pre>
<code style="font-size:20px; line-height: 1.4; font-family:  Noto Sans JP; font-weight: 300; color: #202020">北東京市中央図書館は、８月１０日から８月２４日⓵＿＿、本の整理のため休館します。休館する1週間前の８月３日から本の貸し出しは、いつもの２倍、２０冊までに⓶＿＿。また、休館中に、借りている本を返したい場合は、返却ボックスが図書館南側入り口にあります。⓷＿＿A駅のエレベーター前にもありますので、そちらも⓸＿＿。
毎週水曜日の「子供と絵本を読む会」は、休館中も隣の中央コミュニティー・センター２階で午後１時から２まで行いますのでどうぞご参加ください。
図書館は８月２５日からいつもと同じ時間に⓹＿＿。よろしくお願いします。
７月１０日
北東京市中央図書館</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３・４から選びなさい。  
⓵  
1. に 2. まで 3. では 4. のも  
⓶  
1. なります 2. あります 3. できます 4. かします  
⓷  
1. それに 2. それで 3. それでも 4. そうして  
⓸  
1. ご利用しなさい 2. ご利用します 3. ご利用です 4. ご利用ください  
⓹  
1. 開館でした 2. 開館です 3. 開館します 4. 開館しました  
</p>

<!-- ------------------------------------------------------------------------ -->

#### 02 {.tabset}

<pre>
<code style="font-size:20px; line-height: 1.4; font-family:  Noto Sans JP; font-weight: 300; color: #202020">朝アルバイトに行くとき、いつも　おじいさんに会います。⓵＿＿わかりません。おじいさん　はじめて⓶＿＿とき、何も言いませんでした。つぎの朝、　おじいさんが「おはよう」と言いました。私はびっくりして、「おはようございます」小さい声で言いました。
それから　だんだん大きい声で「おはようございます」と⓷＿＿。⓸＿＿、おじいさんも「おはよう」と　大きい声で言ってくれます。
おじいさん　会ってから２ヶ月になります。おじいさんは、あいさつの　ことば　いっしょに「寒いね」「元気だね」「がんばってね」と　言います。
私はおじいさんに⓹＿＿好きです。そして、元気になります。今日も頑張ってアルバイトしようと思います。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３・４から選びなさい。  
⓵  
1. 名前と家と 2. 名前や家や 3. 名前も家も 4. 名前に家に  
⓶  
1. 会います 2. 会いました 3. 会って 4. 会った  
⓷  
1. 言うようにあります 2. 言ったことがあります 3. 言うことになりました 4. 言うようになりました  
⓸  
1. しかし 2. すると 3. だけど 4. それに  
⓹  
1. 会うのが 2. 会うのを 3. 会うは 4. 会うが  
</p>

<!-- ------------------------------------------------------------------------ -->

### N3 {.tabset}

<!-- ------------------------------------------------------------------------ -->

### N2 {.tabset}

#### 01 {.tabset}

<pre>
<code style="font-size:18px; line-height: 1.4; font-family:  Noto Sans JP; font-weight: 300; color: #202020">この地方のスキー場はコース大部分は整備されており、滑りにくいうことはあまりありません。⓵＿＿、風が強く、⓶＿＿降った雪も積もるか積もらないかのうちに飛ばされてしまうことが多いのです。</code>
</pre>

<p style="font-size:15px; font-family: Noto Sans JP; font-weight: 300; color: #0F0F0F">
問題（　）に入るものを１・２・３から選びなさい。  
⓵   
1. そのため 2. すると 3. ただし  
⓶   
1. せっかく 2. わざわざ 3. きっと  
</p>

<!-- ------------------------------------------------------------------------ -->

#### 02 {.tabset}

<!-- ------------------------------------------------------------------------ -->

### N1 {.tabset}

<!-- ------------------------------------------------------------------------ -->

## Questions {.tabset}

### N5

```{r, echo=FALSE, message=FALSE}

# set.seed(3841)
qsn5 <- qsn5[sample(1:nrow(qsn5)),]

reactable(
  qsn5,
  columns = list(
       Question = colDef(
         #style = list(fontSize = "50px", fontWeight = 700), align = "center"
         
        style = JS("function(rowInfo, colInfo, state) {
        var firstSorted = state.sorted[0]
        if (!firstSorted || firstSorted.id === 'Question') {
          var prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.row['Question'] === prevRow['Question']) {
            return { visibility: 'Question' }
          }
        }
      }"),
      cell = function(value, index) {
        A <- qsn5$A[index]
        A  <- if (!is.na(A )) A  else "Unknown"
        B <- qsn5$B[index]
        B  <- if (!is.na(B )) B  else "Unknown"
        C <- qsn5$C[index]
        C  <- if (!is.na(C )) C  else "Unknown"
        D <- qsn5$D[index]
        D  <- if (!is.na(D )) D  else "Unknown"
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 14, fontWeight = 400), A, " ", B, " ", C, " ", D),
        )
      },
      align = "center", minWidth = 400
      ),
      A = colDef(show = FALSE),
      B = colDef(show = FALSE),
      C = colDef(show = FALSE),
      D = colDef(show = FALSE)
  ),
    outlined = TRUE, defaultPageSize = 3, compact = FALSE, highlight = TRUE, fullWidth = TRUE,
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px"),
    theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 110),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      # "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      # "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      # borderColor = "#555", 
      height = 30, fontSize = "11px"
    )
  )
)
```

<!-- ------------------------------------------------------------------------ -->

### N4

```{r, echo=FALSE, message=FALSE}

# set.seed(3841)
qsn4 <- qsn4[sample(1:nrow(qsn4)),]

reactable(
  qsn4,
  columns = list(
       Question = colDef(
         #style = list(fontSize = "50px", fontWeight = 700), align = "center"
         
        style = JS("function(rowInfo, colInfo, state) {
        var firstSorted = state.sorted[0]
        if (!firstSorted || firstSorted.id === 'Question') {
          var prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.row['Question'] === prevRow['Question']) {
            return { visibility: 'Question' }
          }
        }
      }"),
      cell = function(value, index) {
        A <- qsn4$A[index]
        A  <- if (!is.na(A )) A  else "Unknown"
        B <- qsn4$B[index]
        B  <- if (!is.na(B )) B  else "Unknown"
        C <- qsn4$C[index]
        C  <- if (!is.na(C )) C  else "Unknown"
        D <- qsn4$D[index]
        D  <- if (!is.na(D )) D  else "Unknown"
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 14, fontWeight = 400), A, " ", B, " ", C, " ", D),
        )
      },
      align = "center", minWidth = 400
      ),
      A = colDef(show = FALSE),
      B = colDef(show = FALSE),
      C = colDef(show = FALSE),
      D = colDef(show = FALSE)
  ),
    outlined = TRUE, defaultPageSize = 3, compact = FALSE, highlight = TRUE, fullWidth = TRUE,
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px"),
    theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 110),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      # "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      # "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      # borderColor = "#555", 
      height = 30, fontSize = "11px"
    )
  )
)
```

<!-- ------------------------------------------------------------------------ -->

### N3

```{r, echo=FALSE, message=FALSE}

# set.seed(3841)
qsn3 <- qsn3[sample(1:nrow(qsn3)),]

reactable(
  qsn3,
  columns = list(
       Question = colDef(
         #style = list(fontSize = "50px", fontWeight = 700), align = "center"
         
        style = JS("function(rowInfo, colInfo, state) {
        var firstSorted = state.sorted[0]
        if (!firstSorted || firstSorted.id === 'Question') {
          var prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.row['Question'] === prevRow['Question']) {
            return { visibility: 'Question' }
          }
        }
      }"),
      cell = function(value, index) {
        A <- qsn3$A[index]
        A  <- if (!is.na(A )) A  else "Unknown"
        B <- qsn3$B[index]
        B  <- if (!is.na(B )) B  else "Unknown"
        C <- qsn3$C[index]
        C  <- if (!is.na(C )) C  else "Unknown"
        D <- qsn3$D[index]
        D  <- if (!is.na(D )) D  else "Unknown"
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 14, fontWeight = 400), A, " ", B, " ", C, " ", D),
        )
      },
      align = "center", minWidth = 400
      ),
      A = colDef(show = FALSE),
      B = colDef(show = FALSE),
      C = colDef(show = FALSE),
      D = colDef(show = FALSE)
  ),
    outlined = TRUE, defaultPageSize = 3, compact = FALSE, highlight = TRUE, fullWidth = TRUE,
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px"),
    theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 110),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      # "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      # "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      # borderColor = "#555", 
      height = 30, fontSize = "11px"
    )
  )
)
```

<!-- ------------------------------------------------------------------------ -->

### N2

```{r, echo=FALSE, message=FALSE}

# set.seed(3841)
qsn2 <- qsn2[sample(1:nrow(qsn2)),]

reactable(
  qsn2,
  columns = list(
       Question = colDef(
         #style = list(fontSize = "50px", fontWeight = 700), align = "center"
         
        style = JS("function(rowInfo, colInfo, state) {
        var firstSorted = state.sorted[0]
        if (!firstSorted || firstSorted.id === 'Question') {
          var prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.row['Question'] === prevRow['Question']) {
            return { visibility: 'Question' }
          }
        }
      }"),
      cell = function(value, index) {
        A <- qsn2$A[index]
        A  <- if (!is.na(A )) A  else "Unknown"
        B <- qsn2$B[index]
        B  <- if (!is.na(B )) B  else "Unknown"
        C <- qsn2$C[index]
        C  <- if (!is.na(C )) C  else "Unknown"
        D <- qsn2$D[index]
        D  <- if (!is.na(D )) D  else "Unknown"
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 14, fontWeight = 400), A, " ", B, " ", C, " ", D),
        )
      },
      align = "center", minWidth = 400
      ),
      A = colDef(show = FALSE),
      B = colDef(show = FALSE),
      C = colDef(show = FALSE),
      D = colDef(show = FALSE)
  ),
    outlined = TRUE, defaultPageSize = 3, compact = FALSE, highlight = TRUE, fullWidth = TRUE,
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px"),
    theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 110),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      # "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      # "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      # borderColor = "#555", 
      height = 30, fontSize = "11px"
    )
  )
)
```

<!-- ------------------------------------------------------------------------ -->

### N1

```{r, echo=FALSE, message=FALSE}

# set.seed(3841)
qsn1 <- qsn1[sample(1:nrow(qsn1)),]

reactable(
  qsn1,
  columns = list(
       Question = colDef(
         #style = list(fontSize = "50px", fontWeight = 700), align = "center"
         
        style = JS("function(rowInfo, colInfo, state) {
        var firstSorted = state.sorted[0]
        if (!firstSorted || firstSorted.id === 'Question') {
          var prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.row['Question'] === prevRow['Question']) {
            return { visibility: 'Question' }
          }
        }
      }"),
      cell = function(value, index) {
        A <- qsn1$A[index]
        A  <- if (!is.na(A )) A  else "Unknown"
        B <- qsn1$B[index]
        B  <- if (!is.na(B )) B  else "Unknown"
        C <- qsn1$C[index]
        C  <- if (!is.na(C )) C  else "Unknown"
        D <- qsn1$D[index]
        D  <- if (!is.na(D )) D  else "Unknown"
        tagList(
          div(style = list(fontSize = 19, fontWeight = 500), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 14, fontWeight = 400), A, " ", B, " ", C, " ", D),
        )
      },
      align = "center", minWidth = 400
      ),
      A = colDef(show = FALSE),
      B = colDef(show = FALSE),
      C = colDef(show = FALSE),
      D = colDef(show = FALSE)
  ),
    outlined = TRUE, defaultPageSize = 3, compact = FALSE, highlight = TRUE, fullWidth = TRUE,
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px"),
    theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 110),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      # "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      # "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      # borderColor = "#555", 
      height = 30, fontSize = "11px"
    )
  )
)
```

<!-- ------------------------------------------------------------------------ -->

