---
title: "<b> 没入液浸漬け </b>"
output:
  html_document:
    theme: sandstone
    css: "mystyle.css"
    toc: false
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{=html}
<style type="text/css">

body{
      font-size: 13px;
      font-family: "Anonymous Pro", "Roboto", "Helvetica Neue";
  }
</style>
```
<link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Hina+Mincho&family=Klee+One:wght@400;600&family=New+Tegomin&family=Sawarabi+Gothic&family=Shippori+Mincho+B1:wght@400;500&family=Yomogi&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Noto+Sans+JP:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=M+PLUS+Rounded+1c:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;1,700&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;0,700;1,700&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Maru+Gothic:wght@300;400;500;600&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Kiwi+Maru:wght@300;400;500&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Kaku+Gothic+Antique:wght@300;400;500;700&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Kaku+Gothic+New:wght@300;400;500;700&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Maru+Gothic:wght@300;400;500;700&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=IBM+Plex+Sans+JP:wght@100;200;300;500;600&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Maru+Gothic:wght@300;400;500;600&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Open+Sans:ital,wght@0,300;0,400;0,500;0,600;1,300;1,400;1,500;1,600&display=swap" rel="stylesheet">

<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Maru+Gothic:wght@300;400;500;600&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Open+Sans:ital,wght@0,300;0,400;0,500;0,600;1,300;1,400;1,500;1,600&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Shippori+Mincho+B1:wght@400;500;600;700&display=swap" rel="stylesheet">

```{css, echo=FALSE}
.my-tbl {
  border: 1px solid rgba(0, 0, 0, 0.1);
}

.my-header {
  border-width: 1px;
}

.my-col {
  border-right: 1px solid rgba(0, 0, 0, 0.05);
}

.my-row:hover {
  background-color: #f5f8ff;
}

.toc-content {
    padding-left: 10px;
    padding-right: 10px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo=FALSE}
@media(prefers-color-scheme: light) {
  body {
    <!-- background-color: black; -->
    filter: invert(0);
  }
}
```

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(reactable)
library(htmltools)
library(bslib)
library(dplyr)
library(purrr)
library(readr)
library(vembedr)
options(readr.show_col_types = FALSE)
```

```{r, echo=FALSE, message=FALSE, error=FALSE}
yrcmp <- read_csv("jpim/YRCMP-YRCMP.csv")
btkri <- read_csv("jpim/BTKRI-BTKRI.csv")
dlg1 <- read_csv("jpim/DLG1-SNT.csv")
dlg2 <- read_csv("jpim/DLG2-SNT.csv")
exrpt <- read_csv("jpim/EXRPT-SNT.csv")
psycps <- read_csv("jpim/PSYPSS-SCRPT.csv")
dlgcom <- read_csv("jpim/DLGCOM-DLG.csv")
shrty <- read_csv("jpim/SHRTSTRY-SNT.csv")
heroine <- read_csv("jpim/HEROINE-SCRPT.csv")
witch <- read_csv("jpim/WITCH-SCRPT.csv")
blind <- read_csv("jpim/LSBLND-SCRPT.csv")
diary <- read_csv("jpim/DRY-SCRPT.csv")
kitchen <- read_csv("jpim/KTCHN-SCRPT.csv")
thausnd <- read_csv("jpim/TRHAUSND-SCRPT.csv")
krmukro <- read_csv("jpim/KRMUKRO-SCRPT.csv")
sntmre <- read_csv("jpdb/SNTMRE-SNT.csv")
htspcy <- read_csv("jpim/HTSPCY-SCRPT.csv")
wdnsdy <- read_csv("jpim/WDNSDY-SCRPT.csv")
tedtlk <- read_csv("jpim/TEDTLK-SCRPT.csv")
wrdbsc1 <- read_csv("jpim/WRDSRBSC1-WRDS.csv")
wrdbsc2 <- read_csv("jpim/WRDSRBSC2-WRDS.csv")
wrdint1 <- read_csv("jpim/WRDSRINT1-WRDS.csv")
wrdint2 <- read_csv("jpim/WRDSRINT2-WRDS.csv")
vnstc <- read_csv("jpdb/SNTSB-SSTNC.csv")
vnstd <- read_csv("jpdb/SNTSI-SSTNC.csv")
vnste <- read_csv("jpdb/SNTSA-SSTNC.csv")
vnstg <- read_csv("jpdb/SNTSR4-SSTNC.csv")
vnstb <- read_csv("jpdb/SNTSR5-SSTNC.csv")
sntv <- read_csv("jpdb/SNTSR6-SSTNC.csv")
```

# <b> Immersion </b> {.tabset}
<p style="font-size:11px; line-height: 1; font-family: Noto Sans JP;  color: #202020;">**Immersion** is the act of fully submerging something within another.</p>

## <b> Words </b> {.tabset}

### 01

```{r, echo=FALSE, message=FALSE}

wrdbsc.a <- wrdbsc1 %>% select(R01, R02, R03, R04, R05)
# wrdbsc.a <- wrdbsc.a[sample(1:nrow(wrdbsc.a)),]

reactable(
  na.omit(wrdbsc.a),
  columns = list(
    
    R01 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R02 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R03 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R04 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R05 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = FALSE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 02

```{r, echo=FALSE, message=FALSE}

wrdbsc.a <- wrdbsc1 %>% select(R06, R07, R08, R09, R10)
# wrdbsc.a <- wrdbsc.a[sample(1:nrow(wrdbsc.a)),]

reactable(
  na.omit(wrdbsc.a),
  columns = list(
    
    R06 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R07 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R08 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R09 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R10 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```


<!-- ------------------------------------------------------------------------ -->

### 03

```{r, echo=FALSE, message=FALSE}

wrdbsc.a <- wrdbsc1 %>% select(R11, R12, R13, R14, R15)
# wrdbsc.a <- wrdbsc.a[sample(1:nrow(wrdbsc.a)),]

reactable(
  na.omit(wrdbsc.a),
  columns = list(
    
    R11 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R12 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R13 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R14 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R15 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 04

```{r, echo=FALSE, message=FALSE}

wrdbsc.a <- wrdbsc1 %>% select(R16, R17, R18, R19, R20)
# wrdbsc.a <- wrdbsc.a[sample(1:nrow(wrdbsc.a)),]

reactable(
  na.omit(wrdbsc.a),
  columns = list(
    
    R16 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R17 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R18 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R19 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R20 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 05

```{r, echo=FALSE, message=FALSE}

wrdbsc.b <- wrdbsc2 %>% select(R21, R22, R23, R24, R25)
# wrdbsc.b <- wrdbsc.b[sample(1:nrow(wrdbsc.b)),]

reactable(
  na.omit(wrdbsc.b),
  columns = list(
    
    R21 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R22 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R23 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R24 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R25 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 06

```{r, echo=FALSE, message=FALSE}

wrdbsc.b <- wrdbsc2 %>% select(R26, R27, R28, R29, R30)
# wrdbsc.b <- wrdbsc.b[sample(1:nrow(wrdbsc.b)),]

reactable(
  na.omit(wrdbsc.b),
  columns = list(
    
    R26 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R27 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R28 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R29 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R30 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 07

```{r, echo=FALSE, message=FALSE}

wrdbsc.b <- wrdbsc2 %>% select(R31, R32, R33, R34, R35)
# wrdbsc.b <- wrdbsc.b[sample(1:nrow(wrdbsc.b)),]

reactable(
  na.omit(wrdbsc.b),
  columns = list(
    
    R31 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R32 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R33 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R34 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R35 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 08

```{r, echo=FALSE, message=FALSE}

wrdbsc.b <- wrdbsc2 %>% select(R36, R37, R38, R39, R40)
# wrdbsc.b <- wrdbsc.b[sample(1:nrow(wrdbsc.b)),]

reactable(
  na.omit(wrdbsc.b),
  columns = list(
    
    R36 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R37 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R38 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R39 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R40 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 09

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint1 %>% select(R41, R42, R43, R44, R45)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R41 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R42 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R43 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R44 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R45 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 10

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint1 %>% select(R46, R47, R48, R49, R50)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R46 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R47 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R48 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R49 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R50 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 11

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint1 %>% select(R51, R52, R53, R54, R55)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R51 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R52 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R53 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R54 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R55 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```


<!-- ------------------------------------------------------------------------ -->

### 12

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint1 %>% select(R56, R57, R58, R59, R60)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R56 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R57 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R58 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R59 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R60 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 13

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint2 %>% select(R61, R62, R63, R64, R65)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R61 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R62 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R63 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R64 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R65 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 14

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint2 %>% select(R66, R67, R68, R69, R70)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R66 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R67 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R68 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R69 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R70 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 15

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint2 %>% select(R71, R72, R73, R74, R75)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R71 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R72 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R73 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R74 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R75 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 16

```{r, echo=FALSE, message=FALSE}

wrdint.a <- wrdint2 %>% select(R76, R77, R78, R79, R80)
# wrdint.a <- wrdint.a[sample(1:nrow(wrdint.a)),]

reactable(
  na.omit(wrdint.a),
  columns = list(
    
    R76 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R77 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R78 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R79 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans')),
    R80 = colDef(align = "center", style = list(fontSize = 16, fontWeight = 300, background = '#1b1e1e', color = '#f1f5f5', fontFamily = 'Open Sans'))
    
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    ),
    headerStyle = list(
      backgroundColor = "#1b1e1e",
      color = "hsl(0, 0%, 95%)",
      fontSize = 0,
      fontWeight = 100,
      fontFamily = 'Open Sans',
      fontSize = "0.1rem",
      letterSpacing = "1px",
      textTransform = "uppercase",
      padding = "0px",
      "&:hover, &:focus" = list(color = '#ffff00')
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## <b> Sentences </b> {.tabset}

```{r, echo=FALSE, message=FALSE}

sntmre.a <- sntmre %>% select(Sentences, Translation)
sntmre.a <- sntmre.a[sample(1:nrow(sntmre.a)),]
vnstc.a <- vnstc %>% select(Sentence, Translation) %>% rename(Sentences = Sentence)
vnstc.a <- vnstc.a[sample(1:nrow(vnstc.a)),]
vnstd.a <- vnstd %>% select(Sentence, Translation) %>% rename(Sentences = Sentence)
vnstd.a <- vnstd.a[sample(1:nrow(vnstd.a)),]
vnste.a <- vnste %>% select(Sentence, Translation) %>% rename(Sentences = Sentence)
vnste.a <- vnste.a[sample(1:nrow(vnste.a)),]
vnstg.a <- vnstg %>% select(Phrases, Translation) %>% rename(Sentences = Phrases)
vnstg.a <- vnstg.a[sample(1:nrow(vnstg.a)),]
vnstb.a <- vnstb %>% select(Phrase, Translation) %>% rename(Sentences = Phrase)
vnstb.a <- vnstb.a[sample(1:nrow(vnstb.a)),]
sntva.a <- sntv %>% select(Sentences, Translation)
sntva.a <- sntva.a[sample(1:nrow(sntva.a)),]
sntmre.b <- bind_rows(sntmre.a, vnstc.a)
sntmre.b <- bind_rows(sntmre.b, vnstd.a)
sntmre.b <- bind_rows(sntmre.b, vnste.a)
sntmre.b <- bind_rows(sntmre.b, vnstg.a)
sntmre.b <- bind_rows(sntmre.b, vnstb.a)
sntmre.b <- bind_rows(sntmre.b, sntva.a)
sntmre.b <- sntmre.b[sample(1:nrow(sntmre.b)),]
reactable(
  na.omit(sntmre.b),
  columns = list(
    Sentences = colDef(style= list(background = '#1b1e1e'),
      minWidth = 150,
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 15, fontWeight = 300, color = '#f1f5f5', fontFamily = 'Open Sans'), value),
        )
      },
      align = "left",
    ),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## <b> Series </b> {.tabset}

### Yuru.Camp  {.tabset}

#### S1.EP01

```{r, echo=FALSE, message=FALSE}

yrcmp1 <- yrcmp %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(yrcmp1),
  columns = list(
    Script.EP1 = colDef(style= list(background = '#1b1e1e'),
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- yrcmp1$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 400, fontFamily = 'Open Sans', color = '#f1f5f5'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left",
    ),
    Meaning.EP1 = colDef(style= list(background = '#1b1e1e'),
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#f1f5f5'), value),
        )
      },
      align = "left",
    ),
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 10,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = TRUE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP02

```{r, echo=FALSE, message=FALSE}

yrcmp2 <- yrcmp %>% select(Script.EP2, Meaning.EP2)

reactable(
  na.omit(yrcmp2),
  columns = list(
    Script.EP2 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP2 <- yrcmp2$Meaning.EP2[index]
        Meaning.EP2 <- if (!is.na(Meaning.EP2)) Meaning.EP2 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP2),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP03

```{r, echo=FALSE, message=FALSE}

yrcmp3 <- yrcmp %>% select(Script.EP3, Meaning.EP3)

reactable(
  na.omit(yrcmp3),
  columns = list(
    Script.EP3 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP3 <- yrcmp3$Meaning.EP3[index]
        Meaning.EP3 <- if (!is.na(Meaning.EP3)) Meaning.EP3 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP3),
        )
      },
      align = "left"
    ),
    Meaning.EP3 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP3 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP04

```{r, echo=FALSE, message=FALSE}

yrcmp4 <- yrcmp %>% select(Script.EP4, Meaning.EP4)

reactable(
  na.omit(yrcmp4),
  columns = list(
    Script.EP4 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP4 <- yrcmp4$Meaning.EP4[index]
        Meaning.EP4 <- if (!is.na(Meaning.EP4)) Meaning.EP4 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 7, color = '#787878'), Meaning.EP4),
        )
      },
      align = "left"
    ),
    Meaning.EP4 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP4 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP05

```{r, echo=FALSE, message=FALSE}

yrcmp5 <- yrcmp %>% select(Script.EP5, Meaning.EP5)

reactable(
  na.omit(yrcmp5),
  columns = list(
    Script.EP5 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP5 <- yrcmp5$Meaning.EP5[index]
        Meaning.EP5 <- if (!is.na(Meaning.EP5)) Meaning.EP5 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878', 6495BF), Meaning.EP5),
        )
      },
      align = "left"
    ),
    Meaning.EP5 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP5 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP06

```{r, echo=FALSE, message=FALSE}

yrcmp6 <- yrcmp %>% select(Script.EP6, Meaning.EP6)

reactable(
  na.omit(yrcmp6),
  columns = list(
    Script.EP6 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP6 <- yrcmp6$Meaning.EP6[index]
        Meaning.EP6 <- if (!is.na(Meaning.EP6)) Meaning.EP6 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP6),
        )
      },
      align = "left"
    ),
    Meaning.EP6 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP6 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP07

```{r, echo=FALSE, message=FALSE}

yrcmp7 <- yrcmp %>% select(Script.EP7, Meaning.EP7)

reactable(
  na.omit(yrcmp7),
  columns = list(
    Script.EP7 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP7 <- yrcmp7$Meaning.EP7[index]
        Meaning.EP7 <- if (!is.na(Meaning.EP7)) Meaning.EP7 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP7),
        )
      },
      align = "left"
    ),
    Meaning.EP7 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP7 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP08

```{r, echo=FALSE, message=FALSE}

yrcmp8 <- yrcmp %>% select(Script.EP8, Meaning.EP8)

reactable(
  na.omit(yrcmp8),
  columns = list(
    Script.EP8 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP8 <- yrcmp8$Meaning.EP8[index]
        Meaning.EP8 <- if (!is.na(Meaning.EP8)) Meaning.EP8 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP8),
        )
      },
      align = "left"
    ),
    Meaning.EP8 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP8 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP09

```{r, echo=FALSE, message=FALSE}

yrcmp9 <- yrcmp %>% select(Script.EP9, Meaning.EP9)

reactable(
  na.omit(yrcmp9),
  columns = list(
    Script.EP9 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP9 <- yrcmp9$Meaning.EP9[index]
        Meaning.EP9 <- if (!is.na(Meaning.EP9)) Meaning.EP9 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP9),
        )
      },
      align = "left"
    ),
    Meaning.EP9 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP9 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP10

```{r, echo=FALSE, message=FALSE}

yrcmp10 <- yrcmp %>% select(Script.EP10, Meaning.EP10)

reactable(
  na.omit(yrcmp10),
  columns = list(
    Script.EP10 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP10 <- yrcmp10$Meaning.EP10[index]
        Meaning.EP10 <- if (!is.na(Meaning.EP10)) Meaning.EP10 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP10),
        )
      },
      align = "left"
    ),
    Meaning.EP10 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP10 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP11

```{r, echo=FALSE, message=FALSE}

yrcmp11 <- yrcmp %>% select(Script.EP11, Meaning.EP11)

reactable(
  na.omit(yrcmp11),
  columns = list(
    Script.EP11 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP11 <- yrcmp11$Meaning.EP11[index]
        Meaning.EP11 <- if (!is.na(Meaning.EP11)) Meaning.EP11 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP11),
        )
      },
      align = "left"
    ),
    Meaning.EP11 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP11 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP12

```{r, echo=FALSE, message=FALSE}

yrcmp12 <- yrcmp %>% select(Script.EP12, Meaning.EP12)

reactable(
  na.omit(yrcmp12),
  columns = list(
    Script.EP12 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP12 <- yrcmp12$Meaning.EP12[index]
        Meaning.EP12 <- if (!is.na(Meaning.EP12)) Meaning.EP12 else "Unknown"
        tagList(
          # div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP12),
        )
      },
      align = "left"
    ),
    Meaning.EP12 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP12 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Bottakuri {.tabset}

#### S1.EP01

```{r, echo=FALSE, message=FALSE}

btkri1 <- btkri %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(btkri1),
  columns = list(
    Script.EP1 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- btkri1$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP02

```{r, echo=FALSE, message=FALSE}

btkri2 <- btkri %>% select(Script.EP2, Meaning.EP2)

reactable(
  na.omit(btkri2),
  columns = list(
    Script.EP2 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP2 <- btkri2$Meaning.EP2[index]
        Meaning.EP2 <- if (!is.na(Meaning.EP2)) Meaning.EP2 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP2),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP2 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Psyco.Pass {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

psycps.a <- psycps %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(psycps.a),
  columns = list(
    Script.EP1 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- psycps.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Heroine {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

heroine.a <- heroine %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(heroine.a),
  columns = list(
    Script.EP1 = colDef(
      cell = function(value, index) {
        Meaning.EP1 <- heroine.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP2

```{r, echo=FALSE, message=FALSE}

heroine.a <- heroine %>% select(Script.EP2, Meaning.EP2)

reactable(
  na.omit(heroine.a),
  columns = list(
    Script.EP2 = colDef(
      cell = function(value, index) {
        Meaning.EP2 <- heroine.a$Meaning.EP2[index]
        Meaning.EP2 <- if (!is.na(Meaning.EP2)) Meaning.EP2 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP2),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Flying.Witch {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

witch.a <- witch %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(witch.a),
  columns = list(
    Script.EP1 = colDef(
      cell = function(value, index) {
        Meaning.EP1 <- witch.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP2

```{r, echo=FALSE, message=FALSE}

witch.a <- witch %>% select(Script.EP2, Meaning.EP2)

reactable(
  na.omit(witch.a),
  columns = list(
    Script.EP2 = colDef(
      cell = function(value, index) {
        Meaning.EP2 <- witch.a$Meaning.EP2[index]
        Meaning.EP2 <- if (!is.na(Meaning.EP2)) Meaning.EP2 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP2),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Love.Blind {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

blind.a <- blind %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(blind.a),
  columns = list(
    Script.EP1 = colDef(
      cell = function(value, index) {
        Meaning.EP1 <- blind.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Future.Diary {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

diary.a <- diary %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(diary.a),
  columns = list(
    Script.EP1 = colDef(
      cell = function(value, index) {
        Meaning.EP1 <- diary.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Mocos.Kitchen {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

kitchen.a <- kitchen %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(kitchen.a),
  columns = list(
    Script.EP1 = colDef(
      cell = function(value, index) {
        Meaning.EP1 <- kitchen.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Terrace.House {.tabset}

#### S6.EP1

```{r, echo=FALSE, message=FALSE}

thausnd.a <- thausnd %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(thausnd.a),
  columns = list(
    Script.EP1 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- thausnd.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Kuromukuro {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

krmukro.a <- krmukro %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(krmukro.a),
  columns = list(
    Script.EP1 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- krmukro.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Hot.Spicy {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

htspcy.a <- htspcy %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(htspcy.a),
  columns = list(
    Script.EP1 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- htspcy.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP2

```{r, echo=FALSE, message=FALSE}

htspcy.a <- htspcy %>% select(Script.EP2, Meaning.EP2)

reactable(
  na.omit(htspcy.a),
  columns = list(
    Script.EP2 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP2 <- htspcy.a$Meaning.EP2[index]
        Meaning.EP2 <- if (!is.na(Meaning.EP2)) Meaning.EP2 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP2 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```
<!-- ------------------------------------------------------------------------ -->

#### S1.EP3

```{r, echo=FALSE, message=FALSE}

htspcy.a <- htspcy %>% select(Script.EP3, Meaning.EP3)

reactable(
  na.omit(htspcy.a),
  columns = list(
    Script.EP3 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP3 <- htspcy.a$Meaning.EP3[index]
        Meaning.EP3 <- if (!is.na(Meaning.EP3)) Meaning.EP3 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP3),
        )
      },
      align = "left"
    ),
    Meaning.EP3 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP3 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Wednesday {.tabset}

#### S1.EP1

```{r, echo=FALSE, message=FALSE}

wdnsdy.a <- wdnsdy %>% select(Script.EP1, Meaning.EP1)

reactable(
  na.omit(wdnsdy.a),
  columns = list(
    Script.EP1 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP1 <- wdnsdy.a$Meaning.EP1[index]
        Meaning.EP1 <- if (!is.na(Meaning.EP1)) Meaning.EP1 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP1),
        )
      },
      align = "left"
    ),
    Meaning.EP1 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP1 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### S1.EP2

```{r, echo=FALSE, message=FALSE}

wdnsdy.a <- wdnsdy %>% select(Script.EP2, Meaning.EP2)

reactable(
  na.omit(wdnsdy.a),
  columns = list(
    Script.EP2 = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Meaning.EP2 <- wdnsdy.a$Meaning.EP2[index]
        Meaning.EP2 <- if (!is.na(Meaning.EP2)) Meaning.EP2 else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Meaning.EP2),
        )
      },
      align = "left"
    ),
    Meaning.EP2 = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Meaning.EP2 = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## <b> Dialogues </b> {.tabset}

### Japan-Life {.tabset}

```{r, echo=FALSE, message=FALSE}

dlgcom.1 <- dlgcom %>% select(Character.1, Script.1, Translation.1) %>% rename(Character = Character.1, Script = Script.1, Translation = Translation.1)

reactable(
  na.omit(dlgcom.1),
  columns = list(
    Script = colDef(
      minWidth = 150,
      cell = function(value, index) {
        Character <- dlgcom.1$Character[index]
        Character <- if (!is.na(Character)) Character else "Unknown"
        Translation <- dlgcom.1$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Translation),
        )
      },
      align = "left"
    ),
    Translation = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Character = colDef(show = FALSE),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Restaurant {.tabset}

```{r, echo=FALSE, message=FALSE}

dlg1 <- dlg1 %>% select(Dialogue, Translation)

reactable(
  na.omit(dlg1),
  columns = list(
    Dialogue = colDef(
      cell = function(value, index) {
        Translation <- dlg1$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Translation),
        )
      },
      align = "left"
    ),
    Translation = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Icecream {.tabset}

```{r, echo=FALSE, message=FALSE}

dlg2 <- dlg2 %>% select(Dialogue, Translation)

reactable(
  na.omit(dlg2),
  columns = list(
    Dialogue = colDef(
      cell = function(value, index) {
        Translation <- dlg2$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else "Unknown"
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
          # div(style = list(fontSize = 9, color = '#787878'), Translation),
        )
      },
      align = "left"
    ),
    Translation = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left"
    ), 
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## <b> Talks </b> {.tabset}

### Archi {.tabset}

```{r, echo=FALSE, message=FALSE}

tedtlk.a <- tedtlk %>% select(Script.Archi, Meaning.Archi)

reactable(
  na.omit(tedtlk.a),
  columns = list(
    Script.Archi = colDef(
      minWidth = 150,
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
        )
      },
      align = "left",
    ),
    Meaning.Archi = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left",
    ),
    Meaning.Archi = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Sushi {.tabset}

```{r, echo=FALSE, message=FALSE}

tedtlk.a <- tedtlk %>% select(Script.Sushi, Meaning.Sushi)

reactable(
  na.omit(tedtlk.a),
  columns = list(
    Script.Sushi = colDef(
      minWidth = 150,
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
        )
      },
      align = "left",
    ),
    Meaning.Sushi = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left",
    ),
    Meaning.Sushi = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Vision {.tabset}

```{r, echo=FALSE, message=FALSE}

tedtlk.a <- tedtlk %>% select(Script.Vision, Meaning.Vision)

reactable(
  na.omit(tedtlk.a),
  columns = list(
    Script.Vision = colDef(
      minWidth = 150,
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 15, fontWeight = 500, fontFamily = 'Zen Maru Gothic'), value),
        )
      },
      align = "left",
    ),
    Meaning.Vision = colDef(
      cell = function(value, index) {
        tagList(
          div(style = list(fontSize = 10, color = '#555555'), value),
        )
      },
      align = "left",
    ),
    Meaning.Vision = colDef(show = FALSE)
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", outlined = TRUE, borderless = FALSE, wrap = TRUE, resizable = TRUE, striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## <b> Exerpts </b> {.tabset}

### E01 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt <- exrpt[sample(1:nrow(exrpt)),]
exrpt.a <- exrpt  %>% slice(1:1)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E02 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(2:2)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E03 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(3:3)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E04 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(4:4)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E05 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(5:5)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E06 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(6:6)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E07 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(7:7)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E08 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(8:8)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E09 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(9:9)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E10 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(10:10)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E11 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(11:11)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E12 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(12:12)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### E13 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(13:13)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>


<!-- ------------------------------------------------------------------------ -->

### E14 {.tabset}

```{r, echo=FALSE, message=FALSE}

exrpt.a <- exrpt  %>% slice(14:14)

reactable(
  exrpt.a,
  columns = list(
    Script = colDef(html=TRUE, minWidth = 300, align = "left", style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans')),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

```{r, echo=FALSE, message=FALSE}

reactable(
  exrpt.a,
  columns = list(
    Translation = colDef(html=TRUE, minWidth = 280, align = "left", style = list(fontSize = 12, fontWeight = 300, color = '#101010', fontFamily = 'Klee One')),
    Script = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = FALSE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

## <b> Stories </b> {.tabset}

### S01 {.tabset}

```{r, echo=FALSE, message=FALSE}

shrty <- shrty[sample(1:nrow(shrty)),]
shrty.a <- shrty  %>% slice(1:1)

reactable(
  shrty.a,
  columns = list(
    Script = colDef(
      minWidth = 280,
      cell = function(value, index) {
        Translation <- shrty.a$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 12, fontWeight = 300, color = '#202020', fontFamily = 'Klee One'), Translation),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
        )
      },
      align = "left"
    ),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### S02 {.tabset}

```{r, echo=FALSE, message=FALSE}

shrty.a <- shrty  %>% slice(2:2)

reactable(
  shrty.a,
  columns = list(
    Script = colDef(
      minWidth = 280,
      cell = function(value, index) {
        Translation <- shrty.a$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 12, fontWeight = 300, color = '#202020', fontFamily = 'Klee One'), Translation),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
        )
      },
      align = "left"
    ),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### S03 {.tabset}

```{r, echo=FALSE, message=FALSE}

shrty.a <- shrty  %>% slice(3:3)

reactable(
  shrty.a,
  columns = list(
    Script = colDef(
      minWidth = 280,
      cell = function(value, index) {
        Translation <- shrty.a$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 12, fontWeight = 300, color = '#202020', fontFamily = 'Klee One'), Translation),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
        )
      },
      align = "left"
    ),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### S04 {.tabset}

```{r, echo=FALSE, message=FALSE}

shrty.a <- shrty  %>% slice(4:4)

reactable(
  shrty.a,
  columns = list(
    Script = colDef(
      minWidth = 280,
      cell = function(value, index) {
        Translation <- shrty.a$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 17, fontWeight = 300, color = '#101010', fontFamily = 'Open Sans'), value),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 12, fontWeight = 300, color = '#202020', fontFamily = 'Klee One'), Translation),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 2), "."),
        )
      },
      align = "left"
    ),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

## <b> Audio </b> {.tabset}

### Graded {.tabset}

1. 段階的L1　![](audio/levelone/01 onna no ko.m4a)    
2. 段階的L1　![](audio/levelone/02 hachi no hanashi.m4a)    
3. 段階的L1　![](audio/levelone/03 jonsan nihon e.m4a)    
4. 段階的L1　![](audio/levelone/04 urashima tarou.m4a)    
5. 段階的L1　![](audio/levelone/05 warai hanashi.m4a)    
6. 段階的L2　![](audio/levelone/Houi to chana.mp3)    
7. 段階的L2　![](audio/levelone/Nihon no ofuro.mp3)    
8. 段階的L4　![](audio/levelone/Toshishun.mp3)    
9. 段階的L4　![](audio/levelone/Yuki onna.mp3)    

<h6> </h6>

<!-- ------------------------------------------------------------------------ -->

### Level {.tabset}

#### N5 {.tabset}

<!-- ------------------------------------------------------------------------ -->

#### N4 {.tabset}

<!-- ------------------------------------------------------------------------ -->

#### N3 {.tabset}

##### Mimikara-Bunpou {.tabset}

1. 文法N3　![](audio/mimikarabunpo_n3/Track No02.mp3)   
2. 文法N3　![](audio/mimikarabunpo_n3/Track No03.mp3)   
3. 文法N3　![](audio/mimikarabunpo_n3/Track No04.mp3)   
4. 文法N3　![](audio/mimikarabunpo_n3/Track No05.mp3)   
5. 文法N3　![](audio/mimikarabunpo_n3/Track No06.mp3)   
6. 文法N3　![](audio/mimikarabunpo_n3/Track No07.mp3)   
7. 文法N3　![](audio/mimikarabunpo_n3/Track No08.mp3)   
8. 文法N3　![](audio/mimikarabunpo_n3/Track No09.mp3)   
9. 文法N3　![](audio/mimikarabunpo_n3/Track No10.mp3)   
10. 文法N3　![](audio/mimikarabunpo_n3/Track No11.mp3)   

<!-- ------------------------------------------------------------------------ -->

##### Mimikara-Choukai {.tabset}

1. 聴解N3　![](audio/mimikarachoukai_n3a/02 Track 2.mp3)   
2. 聴解N3　![](audio/mimikarachoukai_n3a/03 Track 3.mp3)   
3. 聴解N3　![](audio/mimikarachoukai_n3a/04 Track 4.mp3)   
4. 聴解N3　![](audio/mimikarachoukai_n3a/05 Track 5.mp3)   
5. 聴解N3　![](audio/mimikarachoukai_n3a/06 Track 6.mp3)   
6. 聴解N3　![](audio/mimikarachoukai_n3a/07 Track 7.mp3)   
7. 聴解N3　![](audio/mimikarachoukai_n3a/08 Track 8.mp3)   
8. 聴解N3　![](audio/mimikarachoukai_n3a/09 Track 9.mp3)   
9. 聴解N3　![](audio/mimikarachoukai_n3a/10 Track 10.mp3)   

<!-- ------------------------------------------------------------------------ -->

#### N2 {.tabset}

<!-- ------------------------------------------------------------------------ -->

#### N1 {.tabset}

<!-- ------------------------------------------------------------------------ -->

### Kikitori {.tabset}

1. 風呂敷　![](audio/kikitori_na/02 Track 2.mp3)   
2. 出前は　![](audio/kikitori_na/07 Track 7.mp3)   
3. 小さな　![](audio/kikitori_na/09 Track 9.mp3)    
4. 犬です　![](audio/kikitori_na/11 Track 11.mp3)    
5. 世界で　![](audio/kikitori_na/13 Track 13.mp3)    
6. 子供耳　![](audio/kikitori_na/15 Track 15.mp3)    
7. 日本人　![](audio/kikitori_na/19 Track 19.mp3)    
8. 百円店　![](audio/kikitori_na/21 Track 21.mp3)    
9. 百円店　![](audio/kikitori_na/22 Track 22.mp3)    
10. もしも　![](audio/kikitori_nb/01 トラック 1.mp3)     
11. 旗のデ　![](audio/kikitori_nb/04 トラック 4.mp3)     
12. 海から　![](audio/kikitori_nb/06 トラック 6.mp3)  
13. いただ　![](audio/kikitori_nc/01 トラック 1.mp3)     
14. 川渡る　![](audio/kikitori_nc/03 トラック 3.mp3)     
15. 川渡る　![](audio/kikitori_nc/04 トラック 4.mp3)    

<!-- ------------------------------------------------------------------------ -->

## <b> Video </b> {.tabset}

<!-- ------------------------------------------------------------------------ -->

