---
title: "日本語"
output:
  html_document:
    theme: sandstone
    css: "mystyle.css"
    toc: false
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{=html}
<style type="text/css">

body{
      font-size: 13px;
      font-family: "Anonymous Pro", "Roboto", "Helvetica Neue";
  }
</style>
```
<link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Hina+Mincho&family=Klee+One:wght@400;600&family=New+Tegomin&family=Sawarabi+Gothic&family=Shippori+Mincho+B1:wght@400;500&family=Yomogi&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Noto+Sans+JP:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=M+PLUS+Rounded+1c:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;1,700&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;0,700;1,700&display=swap" rel="stylesheet">

```{css, echo=FALSE}
.my-tbl {
  border: 1px solid rgba(0, 0, 0, 0.1);
}

.my-header {
  border-width: 1px;
}

.my-col {
  border-right: 1px solid rgba(0, 0, 0, 0.05);
}

.my-row:hover {
  background-color: #f5f8ff;
}

.toc-content {
    padding-left: 10px;
    padding-right: 10px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo=FALSE}
@media(prefers-color-scheme: dark) {
  body {
    background-color: black;
    filter: invert(1);
  }
}
```

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(reactable)
library(htmltools)
library(bslib)
library(dplyr)
library(purrr)
library(readr)
library(vembedr)
options(readr.show_col_types = FALSE)
```

```{r, echo=FALSE, message=FALSE, error=FALSE}
mwrdslvl <- read_csv("jpdb/JLPTWD-JLPT.csv")
corew <- read_csv("jpdb/CRWRD-CRSWRD.csv")
cnmw <- read_csv("jpdb/CMWRD-CMNW.csv")
cmwrdsn<- read_csv("jpdb/RNWRD-CMNWP.csv")
nadj1 <- read_csv("jpdb/ADJNA-ADJNA.csv")
nadj2 <- read_csv("jpdb/ADJI-ADJI.csv")
adv1 <- read_csv("jpdb/ADV-ADV.csv")
noun <- read_csv("jpdb/NOUN-NOUN.csv")
verbsw <- read_csv("jpdb/VRBS-VERBS.csv")
connector <- read_csv("jpdb/CONNECT-CONNECTORS.csv")
ontp <- read_csv("jpdb/ONTPE-ONP.csv")
gwrds <- read_csv("jpdb/WGRMR-LST.csv")
ewrds <- read_csv("vrbjp/WEXPRS-LST.csv")
jlptw5 <- read_csv("jpdb/JLPT5-VRN5.csv")
jlptw4 <- read_csv("jpdb/JLPT4-VRN4.csv")
jlptw3 <- read_csv("jpdb/JLPT3-VRN3.csv")
jlptw2 <- read_csv("jpdb/JLPT2-VRN2.csv")
jlptw1 <- read_csv("jpdb/JLPT1-VRN1.csv")
wordsw <- read_csv("jpdb/WRDSS-WORDS.csv")
```

# Words {.tabset}

## Level {.tabset}

### L5 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl %>% slice(1:2053)
mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]

reactable(
  mwrdslvl5,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]

reactable(
  mwrdslvl5,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L4 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl4 <- mwrdslvl %>% slice(2054:2722)
mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]

reactable(
  mwrdslvl4,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]

reactable(
  mwrdslvl4,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L3 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl3 <- mwrdslvl %>% slice(2723:4861)
mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]

reactable(
  mwrdslvl3,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]

reactable(
  mwrdslvl3,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L2 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl2 <- mwrdslvl %>% slice(4862:6609)
mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]

reactable(
  mwrdslvl2,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]

reactable(
  mwrdslvl2,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L1 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl1 <- mwrdslvl %>% slice(6610:9307)
mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

reactable(
  mwrdslvl1,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

reactable(
  mwrdslvl1,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## Basic {.tabset}

### Core {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

corewx <- corew %>% slice(1:200) %>% rename(Sentences = S1)
corewx <- corewx[sample(1:nrow(corewx)),]

reactable(
  corewx,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- corewx$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        M1 <- corewx$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        M2 <- corewx$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        M3 <- corewx$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11, fontWeight = 500), Reading),
          div(style = list(fontSize = 9, color = '#008000'), M1),
          div(style = list(fontSize = 9, color = '#800000'), M2),
          div(style = list(fontSize = 9), M3)
        )
      },
      align = "center"
    ),

    T1 = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

corewz <- corew %>% slice(1:200) %>% rename(Sentences = S1)
corewz <- corewz[sample(1:nrow(corewz)),]

reactable(
  corewz,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- corewz$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- corewz$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        M1 <- corewz$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        M2 <- corewz$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        M3 <- corewz$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), Sentences),
          # div(style = list(fontSize = 10), Reading),
          # div(style = list(fontSize = 9), M1),
          # div(style = list(fontSize = 9), M2),
          # div(style = list(fontSize = 9), M3)
        )
      },
      align = "center"
    ),

    T1 = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Common {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

cnmw <- cnmw[sample(1:nrow(cnmw)),]

reactable(
  cnmw,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- cnmw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- cnmw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- cnmw$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Translation <- cnmw$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 10), Meaning),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)


```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

cnmw <- cnmw[sample(1:nrow(cnmw)),]

reactable(
  cnmw,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- cnmw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- cnmw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- cnmw$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Translation <- cnmw$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), Sentences),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 10), Meaning),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Random {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

cmwrdsn <- cmwrdsn[sample(1:nrow(cmwrdsn)),]

reactable(
  cmwrdsn,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Note <- cmwrdsn$Note[index]
        Note <- if (!is.na(Note)) Note else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 10), Note),
        )
      },
      align = "center"
    ),
    
    # Sentences = colDef(
    #   minWidth = 180,
    #   cell = function(value, index) {
    #     Remarks <- cmwrdsn$Remarks[index]
    #     Remarks <- if (!is.na(Remarks)) Remarks else ""
    #     Translation <- cmwrdsn$Translation[index]
    #     Translation <- if (!is.na(Translation)) Translation else ""
    #     tagList(
    #       div(style = list(fontSize = 16, fontWeight = 500), value),
    #       div(style = list(fontSize = 9), Translation),
    #       # div(style = list(fontSize = 9, fontWeight = 500), Remarks),
    #     )
    #   },
    #   align = "left"
    # ),
    
    Rank = colDef(show = FALSE),
    Note = colDef(show = FALSE),
    Remarks = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

cmwrdsn <- cmwrdsn[sample(1:nrow(cmwrdsn)),]

reactable(
  cmwrdsn,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Note <- cmwrdsn$Note[index]
        Note <- if (!is.na(Note)) Note else ""
        Sentences <- cmwrdsn$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), Sentences),
        )
      },
      align = "center"
    ),
    
    Rank = colDef(show = FALSE),
    Note = colDef(show = FALSE),
    Remarks = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## Daily {.tabset}

### Time {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.time <- wordsw %>% select(Time, Time.Read, Time.Trans)

reactable(
  na.omit(wordsw.time),
  columns = list(
    Time = colDef(
      # Show species under character names
      cell = function(value, index) {
        Time.Read <- wordsw.time$Time.Read[index]
        Time.Read <- if (!is.na(Time.Read)) Time.Read else ""
        Time.Trans <- wordsw.time$Time.Trans[index]
        Time.Trans <- if (!is.na(Time.Trans)) Time.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Time.Read ),
          div(style = list(fontSize = 10), Time.Trans)
        )
      },
      align = "center"
    ),

    Time.Read  = colDef(show = FALSE),
    Time.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.time <- wordsw.time %>% na.omit(wordsw.time)
wordsw.time <- wordsw.time[sample(1:nrow(wordsw.time)),]

reactable(
  wordsw.time,
  columns = list(
    Time = colDef(
      # Show species under character names
      cell = function(value, index) {
        Time.Read <- wordsw.time$Time.Read[index]
        Time.Read <- if (!is.na(Time.Read)) Time.Read else ""
        Time.Trans <- wordsw.time$Time.Trans[index]
        Time.Trans <- if (!is.na(Time.Trans)) Time.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Time.Read ),
          # div(style = list(fontSize = 10), Time.Trans)
        )
      },
      align = "center"
    ),

    Time.Read  = colDef(show = FALSE),
    Time.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### House {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.house <- wordsw %>% select(House, House.Read, House.Trans)

reactable(
  na.omit(wordsw.house),
  columns = list(
    House = colDef(
      # Show species under character names
      cell = function(value, index) {
        House.Read <- wordsw.house$House.Read[index]
        House.Read <- if (!is.na(House.Read)) House.Read else ""
        House.Trans <- wordsw.house$House.Trans[index]
        House.Trans <- if (!is.na(House.Trans)) House.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), House.Read ),
          div(style = list(fontSize = 10), House.Trans)
        )
      },
      align = "center"
    ),

    House.Read  = colDef(show = FALSE),
    House.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.house <- wordsw.house %>% na.omit(wordsw.house)
wordsw.house <- wordsw.house[sample(1:nrow(wordsw.house)),]

reactable(
  wordsw.house,
  columns = list(
    House = colDef(
      # Show species under character names
      cell = function(value, index) {
        House.Read <- wordsw.house$House.Read[index]
        House.Read <- if (!is.na(House.Read)) House.Read else ""
        House.Trans <- wordsw.house$House.Trans[index]
        House.Trans <- if (!is.na(House.Trans)) House.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), House.Read ),
          # div(style = list(fontSize = 10), House.Trans)
        )
      },
      align = "center"
    ),

    House.Read  = colDef(show = FALSE),
    House.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Person {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.person <- wordsw %>% select(Person, Person.Read, Person.Trans)

reactable(
  na.omit(wordsw.person),
  columns = list(
    Person = colDef(
      # Show species under character names
      cell = function(value, index) {
        Person.Read <- wordsw.person$Person.Read[index]
        Person.Read <- if (!is.na(Person.Read)) Person.Read else ""
        Person.Trans <- wordsw.person$Person.Trans[index]
        Person.Trans <- if (!is.na(Person.Trans)) Person.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Person.Read ),
          div(style = list(fontSize = 10), Person.Trans)
        )
      },
      align = "center"
    ),

    Person.Read  = colDef(show = FALSE),
    Person.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.person <- wordsw.person %>% na.omit(wordsw.person)
wordsw.person <- wordsw.person[sample(1:nrow(wordsw.person)),]

reactable(
  wordsw.person,
  columns = list(
    Person = colDef(
      # Show species under character names
      cell = function(value, index) {
        Person.Read <- wordsw.person$Person.Read[index]
        Person.Read <- if (!is.na(Person.Read)) Person.Read else ""
        Person.Trans <- wordsw.person$Person.Trans[index]
        Person.Trans <- if (!is.na(Person.Trans)) Person.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Person.Read ),
          # div(style = list(fontSize = 10), Person.Trans)
        )
      },
      align = "center"
    ),

    Person.Read  = colDef(show = FALSE),
    Person.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Family {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.family <- wordsw %>% select(Family, Family.Read, Family.Trans)

reactable(
  na.omit(wordsw.family),
  columns = list(
    Family = colDef(
      # Show species under character names
      cell = function(value, index) {
        Family.Read <- wordsw.family$Family.Read[index]
        Family.Read <- if (!is.na(Family.Read)) Family.Read else ""
        Family.Trans <- wordsw.family$Family.Trans[index]
        Family.Trans <- if (!is.na(Family.Trans)) Family.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Family.Read ),
          div(style = list(fontSize = 10), Family.Trans)
        )
      },
      align = "center"
    ),

    Family.Read  = colDef(show = FALSE),
    Family.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.family <- wordsw.family %>% na.omit(wordsw.family)
wordsw.family <- wordsw.family[sample(1:nrow(wordsw.family)),]

reactable(
  wordsw.family,
  columns = list(
    Family = colDef(
      # Show species under character names
      cell = function(value, index) {
        Family.Read <- wordsw.family$Family.Read[index]
        Family.Read <- if (!is.na(Family.Read)) Family.Read else ""
        Family.Trans <- wordsw.family$Family.Trans[index]
        Family.Trans <- if (!is.na(Family.Trans)) Family.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Family.Read ),
          # div(style = list(fontSize = 10), Family.Trans)
        )
      },
      align = "center"
    ),

    Family.Read  = colDef(show = FALSE),
    Family.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Body {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.body <- wordsw %>% select(Body, Body.Read, Body.Trans)

reactable(
  na.omit(wordsw.body),
  columns = list(
    Body = colDef(
      # Show species under character names
      cell = function(value, index) {
        Body.Read <- wordsw.body$Body.Read[index]
        Body.Read <- if (!is.na(Body.Read)) Body.Read else ""
        Body.Trans <- wordsw.body$Body.Trans[index]
        Body.Trans <- if (!is.na(Body.Trans)) Body.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Body.Read ),
          div(style = list(fontSize = 10), Body.Trans)
        )
      },
      align = "center"
    ),

    Body.Read  = colDef(show = FALSE),
    Body.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.body <- wordsw.body %>% na.omit(wordsw.body)
wordsw.body <- wordsw.body[sample(1:nrow(wordsw.body)),]

reactable(
  wordsw.body,
  columns = list(
    Body = colDef(
      # Show species under character names
      cell = function(value, index) {
        Body.Read <- wordsw.body$Body.Read[index]
        Body.Read <- if (!is.na(Body.Read)) Body.Read else ""
        Body.Trans <- wordsw.body$Body.Trans[index]
        Body.Trans <- if (!is.na(Body.Trans)) Body.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Body.Read ),
          # div(style = list(fontSize = 10), Body.Trans)
        )
      },
      align = "center"
    ),

    Body.Read  = colDef(show = FALSE),
    Body.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## Category {.tabset}

### Na.Adjective {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

nadja <- nadj1 %>% slice(1:210)
nadja <- nadja[sample(1:nrow(nadja)),]

reactable(
  nadja,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadja$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadja$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

nadjb <- nadj1 %>% slice(1:210)
nadjb <- nadjb[sample(1:nrow(nadjb)),]

reactable(
  nadjb,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadjb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadjb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- nadjb$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- nadjb$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
          div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### I.Adjective {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

nadja <- nadj2 %>% slice(1:108)
nadja <- nadja[sample(1:nrow(nadja)),]

reactable(
  nadja,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadja$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadja$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

nadjb <- nadj2 %>% slice(1:108)
nadjb <- nadjb[sample(1:nrow(nadjb)),]

reactable(
  nadjb,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadjb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadjb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- nadjb$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Adverb {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

adva <- adv1 %>% slice(1:369)
adva <- adva[sample(1:nrow(adva)),]

reactable(
  adva,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- adva$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- adva$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

advb <- adv1 %>% slice(1:369)
advb <- advb[sample(1:nrow(advb)),]

reactable(
  advb,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- advb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- advb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- advb$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Noun {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# noun <- noun %>% slice(1:210)
noun <- noun[sample(1:nrow(noun)),]

reactable(
  noun,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- noun$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- noun$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# noun <- noun %>% slice(1:210)
noun <- noun[sample(1:nrow(noun)),]

reactable(
  noun,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- noun$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- noun$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- noun$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- noun$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
          div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Onomatope {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# ontp <- ontp %>% slice(1:369)
ontp <- ontp[sample(1:nrow(ontp)),]

reactable(
  ontp,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- ontp$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- ontp$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# ontp <- ontp %>% slice(1:369)
ontp <- ontp[sample(1:nrow(ontp)),]

reactable(
  ontp,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- ontp$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- ontp$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- ontp$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Verb {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# verbsw <- verbsw %>% slice(1:210)
verbsw <- verbsw[sample(1:nrow(verbsw)),]

reactable(
  verbsw,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- verbsw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- verbsw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# verbsw <- verbsw %>% slice(1:210)
verbsw <- verbsw[sample(1:nrow(verbsw)),]

reactable(
  verbsw,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- verbsw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- verbsw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- verbsw$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- verbsw$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
          div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Connectives {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# connector <- connector %>% slice(1:210)
connector <- connector[sample(1:nrow(connector)),]

reactable(
  connector,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- connector$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- connector$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# connector <- connector %>% slice(1:210)
connector <- connector[sample(1:nrow(connector)),]

reactable(
  connector,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- connector$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- connector$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- connector$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- connector$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 18, fontWeight = 500), S1),
          div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Grammar {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

gwrds <- gwrds[sample(1:nrow(gwrds)),]

reactable(
  gwrds,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        # Reading <- gwrds$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- gwrds$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    # S1 = colDef(show = FALSE),
    # T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Sentence = colDef(show = FALSE)
    # Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

gwrds <- gwrds[sample(1:nrow(gwrds)),]

reactable(
  gwrds,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        # Reading <- gwrds$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- gwrds$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentence <- gwrds$Sentence[index]
        Sentence <- if (!is.na(Sentence)) Sentence else ""
        # S1 <- gwrds$S1[index]
        # S1 <- if (!is.na(S1)) S1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 19, fontWeight = 500), Sentence),
          # div(style = list(fontSize = 18, fontWeight = 500), S1),
        )
      },
      align = "center"
    ),
    
    # S1 = colDef(show = FALSE),
    # T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Sentence = colDef(show = FALSE)
    # Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Expression {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

ewrds <- ewrds[sample(1:nrow(ewrds)),]

reactable(
  ewrds,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        # Reading <- ewrds$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- ewrds$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    # S1 = colDef(show = FALSE),
    # T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Sentence = colDef(show = FALSE)
    # Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

ewrds <- ewrds[sample(1:nrow(ewrds)),]

reactable(
  ewrds,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        # Reading <- ewrds$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- ewrds$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentence <- ewrds$Sentence[index]
        Sentence <- if (!is.na(Sentence)) Sentence else ""
        # S1 <- ewrds$S1[index]
        # S1 <- if (!is.na(S1)) S1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 19, fontWeight = 500), Sentence),
          # div(style = list(fontSize = 18, fontWeight = 500), S1),
        )
      },
      align = "center"
    ),
    
    # S1 = colDef(show = FALSE),
    # T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Sentence = colDef(show = FALSE)
    # Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Jlpt {.tabset}

#### L5 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw5 <- jlptw5 %>% slice(1:200)
# jlptw5 <- jlptw5[sample(1:nrow(jlptw5)),]

reactable(
  jlptw5,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw5 <- jlptw5[sample(1:nrow(jlptw5)),]

reactable(
  jlptw5,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L4 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw4 <- jlptw4 %>% slice(1:200)
# jlptw4 <- jlptw4[sample(1:nrow(jlptw4)),]

reactable(
  jlptw4,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw4 <- jlptw4[sample(1:nrow(jlptw4)),]

reactable(
  jlptw4,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L3 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw3 <- jlptw3 %>% slice(1:200)
# jlptw3 <- jlptw3[sample(1:nrow(jlptw3)),]

reactable(
  jlptw3,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw3 <- jlptw3[sample(1:nrow(jlptw3)),]

reactable(
  jlptw3,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L2 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw2 <- jlptw2 %>% slice(1:200)
# jlptw2 <- jlptw2[sample(1:nrow(jlptw2)),]

reactable(
  jlptw2,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw2 <- jlptw2[sample(1:nrow(jlptw2)),]

reactable(
  jlptw2,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L1 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw1 <- jlptw1 %>% slice(1:200)
# jlptw1 <- jlptw1[sample(1:nrow(jlptw1)),]

reactable(
  jlptw1,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw1 <- jlptw1[sample(1:nrow(jlptw1)),]

reactable(
  jlptw1,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 30, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>
