---
title: "<b> 言葉放射発散照射発光 </b>"
output:
  html_document:
    theme: sandstone
    css: "mystyle.css"
    toc: false
    toc_float:
      collapsed: false
      smooth_scroll: true
---

```{=html}
<style type="text/css">

body{
      font-size: 13px;
      font-family: "Anonymous Pro", "Roboto", "Helvetica Neue";
  }
</style>
```
<link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Hina+Mincho&family=Klee+One:wght@400;600&family=New+Tegomin&family=Sawarabi+Gothic&family=Shippori+Mincho+B1:wght@400;500&family=Yomogi&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Noto+Sans+JP:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=M+PLUS+Rounded+1c:wght@100;300;400;500;700&display=swap" rel="stylesheet"> <link rel="preconnect" href="https://fonts.gstatic.com"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;1,700&display=swap" rel="stylesheet"> <link href="https://fonts.googleapis.com/css2?family=Anonymous+Pro:ital,wght@0,400;0,700;1,700&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Zen+Maru+Gothic:wght@300;400;500;600&display=swap" rel="stylesheet">
<link rel="preconnect" href="https://fonts.googleapis.com"> 
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> 
<link href="https://fonts.googleapis.com/css2?family=M+PLUS+Rounded+1c:wght@100;300;400;500;700&display=swap" rel="stylesheet">

```{css, echo=FALSE}
.my-tbl {
  border: 1px solid rgba(0, 0, 0, 0.1);
}

.my-header {
  border-width: 1px;
}

.my-col {
  border-right: 1px solid rgba(0, 0, 0, 0.05);
}

.my-row:hover {
  background-color: #f5f8ff;
}

.toc-content {
    padding-left: 10px;
    padding-right: 10px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css, echo=FALSE}
@media(prefers-color-scheme: dark) {
  body {
    background-color: black;
    filter: invert(1);
  }
}
```

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(reactable)
library(htmltools)
library(bslib)
library(dplyr)
library(purrr)
library(readr)
library(vembedr)
options(readr.show_col_types = FALSE)
```

```{r, echo=FALSE, message=FALSE, error=FALSE}
mwrdslvl <- read_csv("jpdb/JLPTWD-JLPT.csv")
corew <- read_csv("jpdb/CRWRD-CRSWRD.csv")
cnmw <- read_csv("jpdb/CMWRD-CMNW.csv")
cmwrdsn<- read_csv("jpdb/RNWRD-CMNWP.csv")
nadj1 <- read_csv("jpdb/ADJNA-ADJNA.csv")
nadj2 <- read_csv("jpdb/ADJI-ADJI.csv")
adv1 <- read_csv("jpdb/ADV-ADV.csv")
noun <- read_csv("jpdb/NOUN-NOUN.csv")
verbsw <- read_csv("jpdb/VRBS-VERBS.csv")
connector <- read_csv("jpdb/CONNECT-CONNECTORS.csv")
ontp <- read_csv("jpdb/ONTPE-ONP.csv")
gwrds <- read_csv("jpdb/WGRMR-LST.csv")
ewrds <- read_csv("jpdb/WRDSEXP-EXPR.csv")
jlptw5 <- read_csv("jpdb/JLPT5-VRN5.csv")
jlptw4 <- read_csv("jpdb/JLPT4-VRN4.csv")
jlptw3 <- read_csv("jpdb/JLPT3-VRN3.csv")
jlptw2 <- read_csv("jpdb/JLPT2-VRN2.csv")
jlptw1 <- read_csv("jpdb/JLPT1-VRN1.csv")
wordsw <- read_csv("jpdb/WRDSS-WORDS.csv")
tblw1 <- read_csv("jpdb/TBL1-TBWRDS.csv")
tblw2 <- read_csv("jpdb/TBL2-TBWRDS.csv")
tblw3 <- read_csv("jpdb/TBL3-TBWRDS.csv")
tblw4 <- read_csv("jpdb/TBL4-TBWRDS.csv")
tblw5 <- read_csv("jpdb/TBL5-TBWRDS.csv")
techw <- read_csv("jpdb/WRDSTCH-WRD.csv")
related <- read_csv("jpdb/RLWRDS-WRDS.csv")
```

# <b> Words </b> {.tabset}

## <b> Level </b> {.tabset}

### LS {.tabset}

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl %>% slice(1:2053)
mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]
mwrdslvl4 <- mwrdslvl %>% slice(2054:2722)
mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]
mwrdslvl3 <- mwrdslvl %>% slice(2723:4861)
mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]
mwrdslvl2 <- mwrdslvl %>% slice(4862:6609)
mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]
mwrdslvl1 <- mwrdslvl %>% slice(6610:9307)
mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

mwrdslvl.lst <- bind_rows(mwrdslvl5, mwrdslvl4)
mwrdslvl.lst <- bind_rows(mwrdslvl.lst, mwrdslvl3)
mwrdslvl.lst <- bind_rows(mwrdslvl.lst, mwrdslvl2)
mwrdslvl.lst <- bind_rows(mwrdslvl.lst, mwrdslvl1)

reactable(
  mwrdslvl.lst,
  columns = list(
    Expression = colDef(minWidth = 22,align = "left", style = list(fontSize = 13.5, fontFamily = 'Rounded Mplus 1c')),
    Reading = colDef(minWidth = 25,align = "left"),
    Meaning = colDef(minWidth = 100,align = "left") 
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### L5 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl %>% slice(1:2053)
mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]

reactable(
  mwrdslvl5,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]

reactable(
  mwrdslvl5,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L4 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl4 <- mwrdslvl %>% slice(2054:2722)
mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]

reactable(
  mwrdslvl4,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]

reactable(
  mwrdslvl4,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L3 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl3 <- mwrdslvl %>% slice(2723:4861)
mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]

reactable(
  mwrdslvl3,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]

reactable(
  mwrdslvl3,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L2 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl2 <- mwrdslvl %>% slice(4862:6609)
mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]

reactable(
  mwrdslvl2,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]

reactable(
  mwrdslvl2,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### L1 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

mwrdslvl1 <- mwrdslvl %>% slice(6610:9307)
mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

reactable(
  mwrdslvl1,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

reactable(
  mwrdslvl1,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## <b> Basic </b> {.tabset}

### List {.tabset}

```{r, echo=FALSE, message=FALSE}

core.lst <- corew %>% select(Words, Reading, M1) %>% rename(Meaning = M1)
cnmw.lst <- cnmw %>% select(Words, Reading, Meaning)
rdnm.lst <- cmwrdsn %>% select(Words, Reading, Meaning)

core.lst <- core.lst[sample(1:nrow(core.lst)),]
cnmw.lst <- cnmw.lst[sample(1:nrow(cnmw.lst)),]
rdnm.lst <- rdnm.lst[sample(1:nrow(rdnm.lst)),]

words.lst <- bind_rows(core.lst, cnmw.lst)
words.lst <- bind_rows(words.lst, rdnm.lst)
# words.lst <- words.lst %>% na.omit(words.lst)

reactable(
  words.lst,
  columns = list(
    Words = colDef(minWidth = 22,align = "left", style = list(fontSize = 13.5, fontFamily = 'Rounded Mplus 1c')),
    Reading = colDef(minWidth = 25,align = "left"),
    Meaning = colDef(minWidth = 100,align = "left") 
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Sentence {.tabset}

```{r, echo=FALSE, message=FALSE}

core.snlst <- corew %>% select(Words, S1, T1) %>% rename(Sentences = S1, Translation = T1)
cnmw.snlst <- cnmw %>% select(Words, Sentences, Translation)
rdnm.snlst <- cmwrdsn %>% select(Words, Sentences, Translation)

core.snlst <- core.snlst[sample(1:nrow(core.snlst)),]
cnmw.snlst <- cnmw.snlst[sample(1:nrow(cnmw.snlst)),]
rdnm.snlst <- rdnm.snlst[sample(1:nrow(rdnm.snlst)),]

words.snlst <- bind_rows(core.snlst, cnmw.snlst)
words.snlst <- bind_rows(words.snlst, rdnm.snlst)
# words.lst <- words.lst %>% na.omit(words.lst)

reactable(
  words.snlst,
  columns = list(
    Words = colDef(minWidth = 25,align = "left", style = list(fontSize = 13.5, fontFamily = 'Rounded Mplus 1c')),
    Sentences = colDef(minWidth = 70,align = "left", style = list(fontSize = 13.5, fontFamily = 'Rounded Mplus 1c')),
    Translation = colDef(minWidth = 70,align = "left") 
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Core {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

corewx <- corew %>% slice(1:200) %>% rename(Sentences = S1)
corewx <- corewx[sample(1:nrow(corewx)),]

reactable(
  corewx,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- corewx$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        M1 <- corewx$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        M2 <- corewx$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        M3 <- corewx$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11, fontWeight = 500), Reading),
          div(style = list(fontSize = 9, color = '#008000'), M1),
          div(style = list(fontSize = 9, color = '#800000'), M2),
          div(style = list(fontSize = 9), M3)
        )
      },
      align = "center"
    ),

    T1 = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

corewz <- corew %>% slice(1:200) %>% rename(Sentences = S1, Translation = T1)
corewz <- corewz[sample(1:nrow(corewz)),]

reactable(
  corewz,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- corewz$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- corewz$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        M1 <- corewz$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        M2 <- corewz$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        M3 <- corewz$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        Translation <- corewz$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 2), "."),
          # div(style = list(fontSize = 17, fontWeight = 400), Sentences),
          # div(style = list(fontSize = 10), Reading),
          # div(style = list(fontSize = 9), M1),
          # div(style = list(fontSize = 9), M2),
          # div(style = list(fontSize = 9), M3),
          # div(style = list(fontSize = 9, color = '#404040'), Translation)
        )
      },
      align = "center"
    ),

    Translation = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Common {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

cnmw <- cnmw[sample(1:nrow(cnmw)),]

reactable(
  cnmw,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- cnmw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- cnmw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- cnmw$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Translation <- cnmw$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 10), Meaning),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)


```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

cnmw <- cnmw[sample(1:nrow(cnmw)),]

reactable(
  cnmw,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- cnmw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- cnmw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- cnmw$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Translation <- cnmw$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 2), "."),
          # div(style = list(fontSize = 17, fontWeight = 400), Sentences),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 10), Meaning),
          # div(style = list(fontSize = 9, color = '#404040'), Translation)
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Random {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

cmwrdsn <- cmwrdsn[sample(1:nrow(cmwrdsn)),]

reactable(
  cmwrdsn,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Note <- cmwrdsn$Note[index]
        Note <- if (!is.na(Note)) Note else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 10), Note),
        )
      },
      align = "center"
    ),
    
    # Sentences = colDef(
    #   minWidth = 180,
    #   cell = function(value, index) {
    #     Remarks <- cmwrdsn$Remarks[index]
    #     Remarks <- if (!is.na(Remarks)) Remarks else ""
    #     Translation <- cmwrdsn$Translation[index]
    #     Translation <- if (!is.na(Translation)) Translation else ""
    #     tagList(
    #       div(style = list(fontSize = 16, fontWeight = 500), value),
    #       div(style = list(fontSize = 9), Translation),
    #       # div(style = list(fontSize = 9, fontWeight = 500), Remarks),
    #     )
    #   },
    #   align = "left"
    # ),
    
    Reading = colDef(show = FALSE),
    Type = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Rank = colDef(show = FALSE),
    Note = colDef(show = FALSE),
    Remarks = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

cmwrdsn <- cmwrdsn[sample(1:nrow(cmwrdsn)),]

reactable(
  cmwrdsn,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Note <- cmwrdsn$Note[index]
        Note <- if (!is.na(Note)) Note else ""
        Sentences <- cmwrdsn$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Translation <- cmwrdsn$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 2), "."),
          # div(style = list(fontSize = 17, fontWeight = 400), Sentences),
          # div(style = list(fontSize = 9, color = '#404040'), Translation),
        )
      },
      align = "center"
    ),
    
    Reading = colDef(show = FALSE),
    Type = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Rank = colDef(show = FALSE),
    Note = colDef(show = FALSE),
    Remarks = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## <b> Daily </b> {.tabset}

### List {.tabset}

```{r, echo=FALSE, message=FALSE}

wordsw.tm <- wordsw %>% select(Time, Time.Read, Time.Trans )%>% rename(Expression = Time, Reading = Time.Read, Meaning = Time.Trans)
wordsw.th <- wordsw %>% select(House, House.Read, House.Trans )%>% rename(Expression = House, Reading = House.Read, Meaning = House.Trans)
wordsw.pr <- wordsw %>% select(Person, Person.Read, Person.Trans )%>% rename(Expression = Person, Reading = Person.Read, Meaning = Person.Trans)
wordsw.fm <- wordsw %>% select(Family, Family.Read, Family.Trans )%>% rename(Expression = Family, Reading = Family.Read, Meaning = Family.Trans)
wordsw.bd <- wordsw %>% select(Body, Body.Read, Body.Trans )%>% rename(Expression = Body, Reading = Body.Read, Meaning = Body.Trans)
wordsw.ps <- wordsw %>% select(Personality, Personality.Read, Personality.Trans )%>% rename(Expression = Personality, Reading = Personality.Read, Meaning = Personality.Trans)
wordsw.fd <- wordsw %>% select(Food, Food.Read, Food.Trans )%>% rename(Expression = Food, Reading = Food.Read, Meaning = Food.Trans)

wordsw.all <- bind_rows(wordsw.tm, wordsw.th)
wordsw.all <- bind_rows(wordsw.all, wordsw.pr)
wordsw.all <- bind_rows(wordsw.all, wordsw.fm)
wordsw.all <- bind_rows(wordsw.all, wordsw.bd)
wordsw.all <- bind_rows(wordsw.all, wordsw.ps)
wordsw.all <- bind_rows(wordsw.all, wordsw.fd)
wordsw.all <- wordsw.all %>% na.omit(wordsw.all)
wordsw.all <- wordsw.all[sample(1:nrow(wordsw.all)),]

reactable(
  wordsw.all,
  columns = list(
    Expression = colDef(minWidth = 22,align = "left", style = list(fontSize = 13.5,fontFamily = 'Rounded Mplus 1c')),
    Reading = colDef(minWidth = 25,align = "left"),
    Meaning = colDef(minWidth = 100,align = "left") 
  ),
  defaultPageSize = 8,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers", striped = TRUE,

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### Time {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.time <- wordsw %>% select(Time, Time.Read, Time.Trans)

reactable(
  na.omit(wordsw.time),
  columns = list(
    Time = colDef(
      # Show species under character names
      cell = function(value, index) {
        Time.Read <- wordsw.time$Time.Read[index]
        Time.Read <- if (!is.na(Time.Read)) Time.Read else ""
        Time.Trans <- wordsw.time$Time.Trans[index]
        Time.Trans <- if (!is.na(Time.Trans)) Time.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Time.Read ),
          div(style = list(fontSize = 10), Time.Trans)
        )
      },
      align = "center"
    ),

    Time.Read  = colDef(show = FALSE),
    Time.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.time <- wordsw.time %>% na.omit(wordsw.time)
wordsw.time <- wordsw.time[sample(1:nrow(wordsw.time)),]

reactable(
  wordsw.time,
  columns = list(
    Time = colDef(
      # Show species under character names
      cell = function(value, index) {
        Time.Read <- wordsw.time$Time.Read[index]
        Time.Read <- if (!is.na(Time.Read)) Time.Read else ""
        Time.Trans <- wordsw.time$Time.Trans[index]
        Time.Trans <- if (!is.na(Time.Trans)) Time.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Time.Read ),
          # div(style = list(fontSize = 10), Time.Trans)
        )
      },
      align = "center"
    ),

    Time.Read  = colDef(show = FALSE),
    Time.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### House {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.house <- wordsw %>% select(House, House.Read, House.Trans)

reactable(
  na.omit(wordsw.house),
  columns = list(
    House = colDef(
      # Show species under character names
      cell = function(value, index) {
        House.Read <- wordsw.house$House.Read[index]
        House.Read <- if (!is.na(House.Read)) House.Read else ""
        House.Trans <- wordsw.house$House.Trans[index]
        House.Trans <- if (!is.na(House.Trans)) House.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), House.Read ),
          div(style = list(fontSize = 10), House.Trans)
        )
      },
      align = "center"
    ),

    House.Read  = colDef(show = FALSE),
    House.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.house <- wordsw.house %>% na.omit(wordsw.house)
wordsw.house <- wordsw.house[sample(1:nrow(wordsw.house)),]

reactable(
  wordsw.house,
  columns = list(
    House = colDef(
      # Show species under character names
      cell = function(value, index) {
        House.Read <- wordsw.house$House.Read[index]
        House.Read <- if (!is.na(House.Read)) House.Read else ""
        House.Trans <- wordsw.house$House.Trans[index]
        House.Trans <- if (!is.na(House.Trans)) House.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), House.Read ),
          # div(style = list(fontSize = 10), House.Trans)
        )
      },
      align = "center"
    ),

    House.Read  = colDef(show = FALSE),
    House.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Person {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.person <- wordsw %>% select(Person, Person.Read, Person.Trans)

reactable(
  na.omit(wordsw.person),
  columns = list(
    Person = colDef(
      # Show species under character names
      cell = function(value, index) {
        Person.Read <- wordsw.person$Person.Read[index]
        Person.Read <- if (!is.na(Person.Read)) Person.Read else ""
        Person.Trans <- wordsw.person$Person.Trans[index]
        Person.Trans <- if (!is.na(Person.Trans)) Person.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Person.Read ),
          div(style = list(fontSize = 10), Person.Trans)
        )
      },
      align = "center"
    ),

    Person.Read  = colDef(show = FALSE),
    Person.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.person <- wordsw.person %>% na.omit(wordsw.person)
wordsw.person <- wordsw.person[sample(1:nrow(wordsw.person)),]

reactable(
  wordsw.person,
  columns = list(
    Person = colDef(
      # Show species under character names
      cell = function(value, index) {
        Person.Read <- wordsw.person$Person.Read[index]
        Person.Read <- if (!is.na(Person.Read)) Person.Read else ""
        Person.Trans <- wordsw.person$Person.Trans[index]
        Person.Trans <- if (!is.na(Person.Trans)) Person.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Person.Read ),
          # div(style = list(fontSize = 10), Person.Trans)
        )
      },
      align = "center"
    ),

    Person.Read  = colDef(show = FALSE),
    Person.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Family {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.family <- wordsw %>% select(Family, Family.Read, Family.Trans)

reactable(
  na.omit(wordsw.family),
  columns = list(
    Family = colDef(
      # Show species under character names
      cell = function(value, index) {
        Family.Read <- wordsw.family$Family.Read[index]
        Family.Read <- if (!is.na(Family.Read)) Family.Read else ""
        Family.Trans <- wordsw.family$Family.Trans[index]
        Family.Trans <- if (!is.na(Family.Trans)) Family.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Family.Read ),
          div(style = list(fontSize = 10), Family.Trans)
        )
      },
      align = "center"
    ),

    Family.Read  = colDef(show = FALSE),
    Family.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.family <- wordsw.family %>% na.omit(wordsw.family)
wordsw.family <- wordsw.family[sample(1:nrow(wordsw.family)),]

reactable(
  wordsw.family,
  columns = list(
    Family = colDef(
      # Show species under character names
      cell = function(value, index) {
        Family.Read <- wordsw.family$Family.Read[index]
        Family.Read <- if (!is.na(Family.Read)) Family.Read else ""
        Family.Trans <- wordsw.family$Family.Trans[index]
        Family.Trans <- if (!is.na(Family.Trans)) Family.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Family.Read ),
          # div(style = list(fontSize = 10), Family.Trans)
        )
      },
      align = "center"
    ),

    Family.Read  = colDef(show = FALSE),
    Family.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Body {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.body <- wordsw %>% select(Body, Body.Read, Body.Trans)

reactable(
  na.omit(wordsw.body),
  columns = list(
    Body = colDef(
      # Show species under character names
      cell = function(value, index) {
        Body.Read <- wordsw.body$Body.Read[index]
        Body.Read <- if (!is.na(Body.Read)) Body.Read else ""
        Body.Trans <- wordsw.body$Body.Trans[index]
        Body.Trans <- if (!is.na(Body.Trans)) Body.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Body.Read ),
          div(style = list(fontSize = 10), Body.Trans)
        )
      },
      align = "center"
    ),

    Body.Read  = colDef(show = FALSE),
    Body.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.body <- wordsw.body %>% na.omit(wordsw.body)
wordsw.body <- wordsw.body[sample(1:nrow(wordsw.body)),]

reactable(
  wordsw.body,
  columns = list(
    Body = colDef(
      # Show species under character names
      cell = function(value, index) {
        Body.Read <- wordsw.body$Body.Read[index]
        Body.Read <- if (!is.na(Body.Read)) Body.Read else ""
        Body.Trans <- wordsw.body$Body.Trans[index]
        Body.Trans <- if (!is.na(Body.Trans)) Body.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Body.Read ),
          # div(style = list(fontSize = 10), Body.Trans)
        )
      },
      align = "center"
    ),

    Body.Read  = colDef(show = FALSE),
    Body.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Personality {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.personality <- wordsw %>% select(Personality, Personality.Read, Personality.Trans)

reactable(
  na.omit(wordsw.personality),
  columns = list(
    Personality = colDef(
      # Show species under character names
      cell = function(value, index) {
        Personality.Read <- wordsw.personality$Personality.Read[index]
        Personality.Read <- if (!is.na(Personality.Read)) Personality.Read else ""
        Personality.Trans <- wordsw.personality$Personality.Trans[index]
        Personality.Trans <- if (!is.na(Personality.Trans)) Personality.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Personality.Read ),
          div(style = list(fontSize = 10), Personality.Trans)
        )
      },
      align = "center"
    ),

    Personality.Read  = colDef(show = FALSE),
    Personality.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.personality <- wordsw.personality %>% na.omit(wordsw.personality)
wordsw.personality <- wordsw.personality[sample(1:nrow(wordsw.personality)),]

reactable(
  wordsw.personality,
  columns = list(
    Personality = colDef(
      # Show species under character names
      cell = function(value, index) {
        Personality.Read <- wordsw.personality$Personality.Read[index]
        Personality.Read <- if (!is.na(Personality.Read)) Personality.Read else ""
        Personality.Trans <- wordsw.personality$Personality.Trans[index]
        Personality.Trans <- if (!is.na(Personality.Trans)) Personality.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Personality.Read ),
          # div(style = list(fontSize = 10), Personality.Trans)
        )
      },
      align = "center"
    ),

    Personality.Read  = colDef(show = FALSE),
    Personality.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Food {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

wordsw.food <- wordsw %>% select(Food, Food.Read, Food.Trans)

reactable(
  na.omit(wordsw.food),
  columns = list(
    Food = colDef(
      # Show species under character names
      cell = function(value, index) {
        Food.Read <- wordsw.food$Food.Read[index]
        Food.Read <- if (!is.na(Food.Read)) Food.Read else ""
        Food.Trans <- wordsw.food$Food.Trans[index]
        Food.Trans <- if (!is.na(Food.Trans)) Food.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Food.Read ),
          div(style = list(fontSize = 10), Food.Trans)
        )
      },
      align = "center"
    ),

    Food.Read  = colDef(show = FALSE),
    Food.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

wordsw.food <- wordsw.food %>% na.omit(wordsw.food)
wordsw.food <- wordsw.food[sample(1:nrow(wordsw.food)),]

reactable(
  wordsw.food,
  columns = list(
    Food = colDef(
      # Show species under character names
      cell = function(value, index) {
        Food.Read <- wordsw.food$Food.Read[index]
        Food.Read <- if (!is.na(Food.Read)) Food.Read else ""
        Food.Trans <- wordsw.food$Food.Trans[index]
        Food.Trans <- if (!is.na(Food.Trans)) Food.Trans else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Food.Read ),
          # div(style = list(fontSize = 10), Food.Trans)
        )
      },
      align = "center"
    ),

    Food.Read  = colDef(show = FALSE),
    Food.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## <b> Category </b> {.tabset}

### Na.Adj {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

nadja <- nadj1 %>% slice(1:270)
nadja <- nadja[sample(1:nrow(nadja)),]

reactable(
  nadja,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadja$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadja$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

nadjb <- nadj1 %>% slice(1:250)
nadjb <- nadjb[sample(1:nrow(nadjb)),]

reactable(
  nadjb,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadjb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadjb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- nadjb$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- nadjb$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### I.Adj {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

nadja <- nadj2 
nadja <- nadja[sample(1:nrow(nadja)),]

reactable(
  nadja,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadja$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadja$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

nadjb <- nadj2
nadjb <- nadjb[sample(1:nrow(nadjb)),]

reactable(
  nadjb,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- nadjb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadjb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- nadjb$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- nadjb$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Adverb {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

adva <- adv1 %>% slice(1:367)
adva <- adva[sample(1:nrow(adva)),]

reactable(
  adva,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- adva$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- adva$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

advb <- adv1 %>% slice(1:369)
advb <- advb[sample(1:nrow(advb)),]

reactable(
  advb,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- advb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- advb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- advb$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- advb$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Noun {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# noun <- noun %>% slice(1:210)
noun <- noun[sample(1:nrow(noun)),]

reactable(
  noun,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- noun$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- noun$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# noun <- noun %>% slice(1:210)
noun <- noun[sample(1:nrow(noun)),]

reactable(
  noun,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- noun$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- noun$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- noun$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- noun$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Onomatope {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# ontp <- ontp %>% slice(1:369)
ontp <- ontp[sample(1:nrow(ontp)),]

reactable(
  ontp,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- ontp$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- ontp$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# ontp <- ontp %>% slice(1:369)
ontp <- ontp[sample(1:nrow(ontp)),]

reactable(
  ontp,
  columns = list(
    Word = colDef(
      cell = function(value, index) {
        Reading <- ontp$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- ontp$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- ontp$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- ontp$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)     
        )
      },
      align = "center"
    ),
    
    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Verb {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# verbsw <- verbsw %>% slice(1:210)
verbsw <- verbsw[sample(1:nrow(verbsw)),]

reactable(
  verbsw,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- verbsw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- verbsw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# verbsw <- verbsw %>% slice(1:210)
verbsw <- verbsw[sample(1:nrow(verbsw)),]

reactable(
  verbsw,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- verbsw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- verbsw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- verbsw$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- verbsw$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Connectives {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

# connector <- connector %>% slice(1:210)
connector <- connector[sample(1:nrow(connector)),]

reactable(
  connector,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- connector$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- connector$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

# connector <- connector %>% slice(1:210)
connector <- connector[sample(1:nrow(connector)),]

reactable(
  connector,
  columns = list(
    Words = colDef(
      # Show species under character names
      cell = function(value, index) {
        Reading <- connector$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- connector$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        S1 <- connector$S1[index]
        S1 <- if (!is.na(S1)) S1 else ""
        T1 <- connector$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), S1),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878'), T1)
        )
      },
      align = "center"
    ),

    S1 = colDef(show = FALSE),
    T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Grammar {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

gwrds.na <- gwrds[sample(1:nrow(gwrds)),]

reactable(
  gwrds.na,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        # Reading <- gwrds.na$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- gwrds.na$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    # S1 = colDef(show = FALSE),
    # T1 = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Level = colDef(show = FALSE),
    Sentence = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
    # Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

gwrds.n2 <- gwrds %>% slice(339:470)
gwrds.n2 <- gwrds.n2[sample(1:nrow(gwrds.n2)),]
gwrds.n3 <- gwrds %>% slice(196:338)
gwrds.n3 <- gwrds.n3[sample(1:nrow(gwrds.n3)),]
gwrds.n4 <- gwrds %>% slice(43:195)
gwrds.n4 <- gwrds.n4[sample(1:nrow(gwrds.n4)),]
gwrds.n5 <- gwrds %>% slice(1:42)
gwrds.n5 <- gwrds.n5[sample(1:nrow(gwrds.n5)),]
gwrds.ex <- gwrds %>% slice(471:534)
gwrds.ex <- gwrds.ex[sample(1:nrow(gwrds.ex)),]

gwrds.na <- bind_rows(gwrds.n2, gwrds.n3)
gwrds.na <- bind_rows(gwrds.na, gwrds.n4)
gwrds.na <- bind_rows(gwrds.na, gwrds.n5)
gwrds.na <- bind_rows(gwrds.na, gwrds.ex)

reactable(
  gwrds.na,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        # Reading <- gwrds.na$Reading[index]
        # Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- gwrds.na$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentence <- gwrds.na$Sentence[index]
        Sentence <- if (!is.na(Sentence)) Sentence else ""
        Translation <- gwrds.na$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 500), Sentence),
          # div(style = list(fontSize = 9, fontWeight = 400), Translation),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Level = colDef(show = FALSE),
    Sentence = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Expression {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

ewrds <- ewrds[sample(1:nrow(ewrds)),]

reactable(
  ewrds,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Meaning <- ewrds$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Translation <- ewrds$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Sentence = colDef(show = FALSE),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

ewrds <- ewrds[sample(1:nrow(ewrds)),]

reactable(
  ewrds,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Meaning <- ewrds$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentence <- ewrds$Sentence[index]
        Sentence <- if (!is.na(Sentence)) Sentence else ""
        Translation <- ewrds$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), Sentence),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878' ), Translation),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Sentence = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
    
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Tech {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

techw <- techw[sample(1:nrow(techw)),]

reactable(
  techw,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- techw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- techw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 10), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentence = colDef(show = FALSE),
    Translation = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>

<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

techw <- techw[sample(1:nrow(techw)),]

reactable(
  techw,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- techw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- techw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentence <- techw$Sentence[index]
        Sentence <- if (!is.na(Sentence)) Sentence else ""
        Translation <- techw$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 17, fontWeight = 400), Sentence),
          # div(style = list(fontSize = 9, fontWeight = 400, color = '#787878' ), Translation),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentence = colDef(show = FALSE),
    Translation = colDef(show = FALSE)
    
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Jlpt {.tabset}

#### L5 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw5 <- jlptw5 %>% slice(1:500)
# jlptw5 <- jlptw5[sample(1:nrow(jlptw5)),]

reactable(
  jlptw5,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw5 <- jlptw5[sample(1:nrow(jlptw5)),]

reactable(
  jlptw5,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L4 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw4 <- jlptw4 %>% slice(1:500)
# jlptw4 <- jlptw4[sample(1:nrow(jlptw4)),]

reactable(
  jlptw4,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw4 <- jlptw4[sample(1:nrow(jlptw4)),]

reactable(
  jlptw4,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L3 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw3 <- jlptw3 %>% slice(1:500)
# jlptw3 <- jlptw3[sample(1:nrow(jlptw3)),]

reactable(
  jlptw3,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw3 <- jlptw3[sample(1:nrow(jlptw3)),]

reactable(
  jlptw3,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L2 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw2 <- jlptw2 %>% slice(1:500)
# jlptw2 <- jlptw2[sample(1:nrow(jlptw2)),]

reactable(
  jlptw2,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw2 <- jlptw2[sample(1:nrow(jlptw2)),]

reactable(
  jlptw2,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L1 {.tabset}

<div class = "row">
<div class = "col-sm-4">

```{r, echo=FALSE, message=FALSE}

jlptw1 <- jlptw1 %>% slice(1:500)
# jlptw1 <- jlptw1[sample(1:nrow(jlptw1)),]

reactable(
  jlptw1,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 9), Reading),
          div(style = list(fontSize = 9, fontWeight = 500), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-8">

```{r, echo=FALSE, message=FALSE}

jlptw1 <- jlptw1[sample(1:nrow(jlptw1)),]

reactable(
  jlptw1,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Reading <- jlptw1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- jlptw1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          # div(style = list(fontSize = 9), Reading),
          # div(style = list(fontSize = 8), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

## <b> Random </b> {.tabset}

### 1 {.tabset}

```{r, echo=FALSE, message=FALSE}

# tblw1 <- tblw1[sample(1:nrow(tblw1)),]

reactable(
  tblw1,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw1$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw1$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw1$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw1$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw1$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw1$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 2

```{r, echo=FALSE, message=FALSE}

tblw2 <- tblw2[sample(1:nrow(tblw2)),]

reactable(
  tblw2,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw2$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw2$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw2$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw2$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw2$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw2$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 3

```{r, echo=FALSE, message=FALSE}

tblw3 <- tblw3[sample(1:nrow(tblw3)),]

reactable(
  tblw3,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw3$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw3$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw3$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw3$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw3$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw3$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 500), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 4

```{r, echo=FALSE, message=FALSE}

tblw4 <- tblw4[sample(1:nrow(tblw4)),]

reactable(
  tblw4,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw4$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw4$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw4$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw4$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw4$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw4$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

### 5

```{r, echo=FALSE, message=FALSE}

tblw5 <- tblw5[sample(1:nrow(tblw5)),]

reactable(
  tblw5,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        R1 <- tblw5$R1[index]
        R1 <- if (!is.na(R1)) R1 else ""
        T1 <- tblw5$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8), R1),
          div(style = list(fontSize = 8), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw5$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        R2 <- tblw5$R2[index]
        R2 <- if (!is.na(R2)) R2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8), R2),
          div(style = list(fontSize = 8), T2),
        )
      },
      align = "center"
    ),
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw5$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        R3 <- tblw5$R3[index]
        R3 <- if (!is.na(R3)) R3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8), R3),
          div(style = list(fontSize = 8), T3),
        )
      },
      align = "center"
    ),
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw5$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        R4 <- tblw5$R4[index]
        R4 <- if (!is.na(R4)) R4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), value),
          div(style = list(fontSize = 8), R4),
          div(style = list(fontSize = 8), T4),
        )
      },
      align = "center"
    ),

    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    R1 = colDef(show = FALSE),
    R2 = colDef(show = FALSE),
    R3 = colDef(show = FALSE),
    R4 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

## <b> Related </b> {.tabset}

```{r, echo=FALSE, message=FALSE}
related.a <- related %>% rename(Related.Words = Related.Words.1A)
related.a <- related.a[sample(1:nrow(related.a)),]

reactable(
  related.a,
  columns = list(
    Words = colDef(
      cell = function(value, index) {
        Meaning <- related.a$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- related.a$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        tagList(
          div(style = list(fontSize = 24, fontWeight = 600), value),
          div(style = list(fontSize = 11), Reading),
          div(style = list(fontSize = 10), Meaning)
        )
      },
      align = "center"
    ),
    
    Related.Words = colDef(
      minWidth = 180,
      cell = function(value, index) {
        Related.Words.1B <- related.a$Related.Words.1B[index]
        Related.Words.1B <- if (!is.na(Related.Words.1B)) Related.Words.1B else ""
        Related.Words.2A <- related.a$Related.Words.2A[index]
        Related.Words.2A <- if (!is.na(Related.Words.2A)) Related.Words.2A else ""
        Related.Words.2B <- related.a$Related.Words.2B[index]
        Related.Words.2B <- if (!is.na(Related.Words.2B)) Related.Words.2B else ""
        Related.Words.3A <- related.a$Related.Words.3A[index]
        Related.Words.3A <- if (!is.na(Related.Words.3A)) Related.Words.3A else ""
        Related.Words.3B <- related.a$Related.Words.3B[index]
        Related.Words.3B <- if (!is.na(Related.Words.3B)) Related.Words.3B else ""
        Related.Words.4A <- related.a$Related.Words.4A[index]
        Related.Words.4A <- if (!is.na(Related.Words.4A)) Related.Words.4A else ""
        Related.Words.4B <- related.a$Related.Words.4B[index]
        Related.Words.4B <- if (!is.na(Related.Words.4B)) Related.Words.4B else ""
        Related.Words.5A <- related.a$Related.Words.5A[index]
        Related.Words.5A <- if (!is.na(Related.Words.5A)) Related.Words.5A else ""
        Related.Words.5B <- related.a$Related.Words.5B[index]
        Related.Words.5B <- if (!is.na(Related.Words.5B)) Related.Words.5B else ""
        tagList(
          div(style = list(fontSize = 18, fontWeight = 600, fontFamily = 'Zen Maru Gothic'), value),
          div(style = list(fontSize = 10), Related.Words.1B),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 18, fontWeight = 600, fontFamily = 'Zen Maru Gothic'), Related.Words.2A),
          div(style = list(fontSize = 10), Related.Words.2B),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 18, fontWeight = 600, fontFamily = 'Zen Maru Gothic'), Related.Words.3A),
          div(style = list(fontSize = 10), Related.Words.3B),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 18, fontWeight = 600, fontFamily = 'Zen Maru Gothic'), Related.Words.4A),
          div(style = list(fontSize = 10), Related.Words.4B),
          div(style = list(fontSize = 2), "."),
          div(style = list(fontSize = 18, fontWeight = 600, fontFamily = 'Zen Maru Gothic'), Related.Words.5A),
          div(style = list(fontSize = 10), Related.Words.5B),
          div(style = list(fontSize = 2), "."),
        )
      },
      align = "center"
    ),
    
    Related.Words.1B = colDef(show = FALSE),
    Related.Words.2A = colDef(show = FALSE),
    Related.Words.2B = colDef(show = FALSE),
    Related.Words.3A = colDef(show = FALSE),
    Related.Words.3B = colDef(show = FALSE),
    Related.Words.4A = colDef(show = FALSE),
    Related.Words.4B = colDef(show = FALSE),
    Related.Words.5A = colDef(show = FALSE),
    Related.Words.5B = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

<!-- ## <b> Review </b> {.tabset} -->

<!-- ### Basic {.tabset} -->

<!-- #### Core -->

<!-- <div class = "row"> -->
<!-- <div class = "col-sm-6"> -->

<!-- ```{r, echo=FALSE, message=FALSE} -->

<!-- corewz <- corewz[sample(1:nrow(corewz)),] -->

<!-- reactable( -->
<!--   corewz, -->
<!--   columns = list( -->
<!--     Sentences = colDef( -->
<!--       cell = function(value, index) { -->
<!--         Reading <- corewz$Reading[index] -->
<!--         Reading <- if (!is.na(Reading)) Reading else "" -->
<!--         Translation <- corewz$Translation[index] -->
<!--         Translation <- if (!is.na(Translation)) Translation else "" -->
<!--         M1 <- corewz$M1[index] -->
<!--         M1 <- if (!is.na(M1)) M1 else "" -->
<!--         M2 <- corewz$M2[index] -->
<!--         M2 <- if (!is.na(M2)) M2 else "" -->
<!--         M3 <- corewz$M3[index] -->
<!--         M3 <- if (!is.na(M3)) M3 else "" -->
<!--         Words <- corewz$Words[index] -->
<!--         Words <- if (!is.na(Words)) Words else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 12, fontWeight = 600), Translation) -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->

<!--     Words = colDef(show = FALSE), -->
<!--     M1 = colDef(show = FALSE), -->
<!--     M2 = colDef(show = FALSE), -->
<!--     M3 = colDef(show = FALSE), -->
<!--     Translation = colDef(show = FALSE), -->
<!--     Reading = colDef(show = FALSE) -->

<!--   ), -->
<!--   defaultPageSize = 1, -->
<!--   theme = reactableTheme( -->
<!--     cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"), -->
<!--     searchInputStyle = list( -->
<!--       paddingLeft = "8px", -->
<!--       paddingTop = "8px", -->
<!--       paddingBottom = "8px", -->
<!--       width = "100%" -->
<!--     ) -->
<!--   ), -->
<!--   showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple", -->

<!--   style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px") -->
<!-- ) -->

<!-- ``` -->

<!-- </div> -->
<!-- <div class = "col-sm-6"> -->

<!-- ```{r, echo=FALSE, message=FALSE} -->

<!-- corewz <- corewz[sample(1:nrow(corewz)),] -->

<!-- reactable( -->
<!--   corewz, -->
<!--   columns = list( -->
<!--     Translation = colDef( -->
<!--       cell = function(value, index) { -->
<!--         Reading <- corewz$Reading[index] -->
<!--         Reading <- if (!is.na(Reading)) Reading else "" -->
<!--         Sentences <- corewz$Sentences[index] -->
<!--         Sentences <- if (!is.na(Sentences)) Sentences else "" -->
<!--         M1 <- corewz$M1[index] -->
<!--         M1 <- if (!is.na(M1)) M1 else "" -->
<!--         M2 <- corewz$M2[index] -->
<!--         M2 <- if (!is.na(M2)) M2 else "" -->
<!--         M3 <- corewz$M3[index] -->
<!--         M3 <- if (!is.na(M3)) M3 else "" -->
<!--         Words <- corewz$Words[index] -->
<!--         Words <- if (!is.na(Words)) Words else "" -->
<!--         tagList( -->
<!--           div(style = list(fontSize = 20, fontWeight = 600), Sentences) -->
<!--         ) -->
<!--       }, -->
<!--       align = "center" -->
<!--     ), -->

<!--     Words = colDef(show = FALSE), -->
<!--     M1 = colDef(show = FALSE), -->
<!--     M2 = colDef(show = FALSE), -->
<!--     M3 = colDef(show = FALSE), -->
<!--     Sentences = colDef(show = FALSE), -->
<!--     Reading = colDef(show = FALSE) -->

<!--   ), -->
<!--   defaultPageSize = 1, -->
<!--   theme = reactableTheme( -->
<!--     # Vertically center cells -->
<!--     cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"), -->
<!--     searchInputStyle = list( -->
<!--       paddingLeft = "8px", -->
<!--       paddingTop = "8px", -->
<!--       paddingBottom = "8px", -->
<!--       width = "100%" -->
<!--     ) -->
<!--   ), -->
<!--   showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple", -->

<!--   style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px") -->
<!-- ) -->

<!-- ``` -->

<!-- </div> -->
<!-- </div> -->

<!-- ------------------------------------------------------------------------ -->

<!-- #### Common -->

<!-- ------------------------------------------------------------------------ -->

<!-- #### Random -->

<!-- ------------------------------------------------------------------------ -->

<!-- ### Daily {.tabset} -->

<!-- ------------------------------------------------------------------------ -->

## <b> Remember </b> {.tabset}

### Level {.tabset}

#### L5

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]

reactable(
  mwrdslvl5,
  columns = list(
    Meaning = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Expression <- mwrdslvl5$Expression[index]
        Expression <- if (!is.na(Expression)) Expression else ""
        tagList(
          div(style = list(fontSize = 21, fontWeight = 600), Expression),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Expression = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl5 <- mwrdslvl5[sample(1:nrow(mwrdslvl5)),]

reactable(
  mwrdslvl5,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl5$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl5$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L4

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]

reactable(
  mwrdslvl4,
  columns = list(
    Meaning = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Expression <- mwrdslvl4$Expression[index]
        Expression <- if (!is.na(Expression)) Expression else ""
        tagList(
          div(style = list(fontSize = 21, fontWeight = 600), Expression),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Expression = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl4 <- mwrdslvl4[sample(1:nrow(mwrdslvl4)),]

reactable(
  mwrdslvl4,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl4$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl4$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L3

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]

reactable(
  mwrdslvl3,
  columns = list(
    Meaning = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Expression <- mwrdslvl3$Expression[index]
        Expression <- if (!is.na(Expression)) Expression else ""
        tagList(
          div(style = list(fontSize = 21, fontWeight = 600), Expression),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Expression = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl3 <- mwrdslvl3[sample(1:nrow(mwrdslvl3)),]

reactable(
  mwrdslvl3,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl3$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl3$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L2

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]

reactable(
  mwrdslvl2,
  columns = list(
    Meaning = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Expression <- mwrdslvl2$Expression[index]
        Expression <- if (!is.na(Expression)) Expression else ""
        tagList(
          div(style = list(fontSize = 21, fontWeight = 600), Expression),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Expression = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl2 <- mwrdslvl2[sample(1:nrow(mwrdslvl2)),]

reactable(
  mwrdslvl2,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl2$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl2$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### L1

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

reactable(
  mwrdslvl1,
  columns = list(
    Meaning = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Expression <- mwrdslvl1$Expression[index]
        Expression <- if (!is.na(Expression)) Expression else ""
        tagList(
          div(style = list(fontSize = 21, fontWeight = 600), Expression),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Expression = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

mwrdslvl1 <- mwrdslvl1[sample(1:nrow(mwrdslvl1)),]

reactable(
  mwrdslvl1,
  columns = list(
    Expression = colDef(
      cell = function(value, index) {
        Reading <- mwrdslvl1$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- mwrdslvl1$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Meaning),
        )
      },
      align = "center"
    ),

    Reading = colDef(show = FALSE),
    Meaning = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Basic {.tabset}

#### Core

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

corewz <- corewz[sample(1:nrow(corewz)),]

reactable(
  corewz,
  columns = list(
    Translation = colDef(
      cell = function(value, index) {
        Reading <- corewz$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- corewz$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        M1 <- corewz$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        M2 <- corewz$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        M3 <- corewz$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        Words <- corewz$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Sentences)
        )
      },
      align = "center"
    ),

    Words = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

corewz <- corewz[sample(1:nrow(corewz)),]

reactable(
  corewz,
  columns = list(
    Sentences = colDef(
      cell = function(value, index) {
        Reading <- corewz$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Translation <- corewz$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        M1 <- corewz$M1[index]
        M1 <- if (!is.na(M1)) M1 else ""
        M2 <- corewz$M2[index]
        M2 <- if (!is.na(M2)) M2 else ""
        M3 <- corewz$M3[index]
        M3 <- if (!is.na(M3)) M3 else ""
        Words <- corewz$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Translation)
        )
      },
      align = "center"
    ),

    Words = colDef(show = FALSE),
    M1 = colDef(show = FALSE),
    M2 = colDef(show = FALSE),
    M3 = colDef(show = FALSE),
    Translation = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### Common

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

cnmw <- cnmw[sample(1:nrow(cnmw)),]

reactable(
  cnmw,
  columns = list(
    Translation = colDef(
      cell = function(value, index) {
        Meaning <- cnmw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- cnmw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Sentences <- cnmw$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Words <- cnmw$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Sentences),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Words = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

cnmw <- cnmw[sample(1:nrow(cnmw)),]

reactable(
  cnmw,
  columns = list(
    Sentences = colDef(
      cell = function(value, index) {
        Meaning <- cnmw$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Reading <- cnmw$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Translation <- cnmw$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        Words <- cnmw$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Translation),
        )
      },
      align = "center"
    ),
    
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE),
    Translation = colDef(show = FALSE),
    Words = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)


```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### Random

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

cmwrdsn <- cmwrdsn[sample(1:nrow(cmwrdsn)),]

reactable(
  cmwrdsn,
  columns = list(
    Translation = colDef(
      cell = function(value, index) {
        Note <- cmwrdsn$Note[index]
        Note <- if (!is.na(Note)) Note else ""
        Sentences <- cmwrdsn$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Words <- cmwrdsn$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Sentences),
        )
      },
      align = "center"
    ),
    
    Rank = colDef(show = FALSE),
    Note = colDef(show = FALSE),
    Remarks = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Words = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

cmwrdsn <- cmwrdsn[sample(1:nrow(cmwrdsn)),]

reactable(
  cmwrdsn,
  columns = list(
    Sentences = colDef(
      cell = function(value, index) {
        Note <- cmwrdsn$Note[index]
        Note <- if (!is.na(Note)) Note else ""
        Translation <- cmwrdsn$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        Words <- cmwrdsn$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Translation),
        )
      },
      align = "center"
    ),
    
    Rank = colDef(show = FALSE),
    Note = colDef(show = FALSE),
    Remarks = colDef(show = FALSE),
    Translation = colDef(show = FALSE),
    Words = colDef(show = FALSE)
  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 250),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "simple",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Daily {.tabset}

#### Time

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

wordsw.time <- wordsw.time[sample(1:nrow(wordsw.time)),]

reactable(
  wordsw.time,
  columns = list(
    Time.Trans = colDef(
      cell = function(value, index) {
        Time.Read <- wordsw.time$Time.Read[index]
        Time.Read <- if (!is.na(Time.Read)) Time.Read else ""
        Time <- wordsw.time$Time[index]
        Time <- if (!is.na(Time)) Time else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Time),
        )
      },
      align = "center"
    ),

    Time.Read  = colDef(show = FALSE),
    Time = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

wordsw.time <- wordsw.time[sample(1:nrow(wordsw.time)),]

reactable(
  wordsw.time,
  columns = list(
    Time = colDef(
      cell = function(value, index) {
        Time.Read <- wordsw.time$Time.Read[index]
        Time.Read <- if (!is.na(Time.Read)) Time.Read else ""
        Time.Trans <- wordsw.time$Time.Trans[index]
        Time.Trans <- if (!is.na(Time.Trans)) Time.Trans else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Time.Trans),
        )
      },
      align = "center"
    ),

    Time.Read  = colDef(show = FALSE),
    Time.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### House

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

wordsw.house <- wordsw.house[sample(1:nrow(wordsw.house)),]

reactable(
  wordsw.house,
  columns = list(
    House.Trans = colDef(
      cell = function(value, index) {
        House.Read <- wordsw.house$House.Read[index]
        House.Read <- if (!is.na(House.Read)) House.Read else ""
        House <- wordsw.house$House[index]
        House <- if (!is.na(House)) House else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), House),
        )
      },
      align = "center"
    ),

    House.Read  = colDef(show = FALSE),
    House = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

wordsw.house <- wordsw.house[sample(1:nrow(wordsw.house)),]

reactable(
  wordsw.house,
  columns = list(
    House = colDef(
      cell = function(value, index) {
        House.Read <- wordsw.house$House.Read[index]
        House.Read <- if (!is.na(House.Read)) House.Read else ""
        House.Trans <- wordsw.house$House.Trans[index]
        House.Trans <- if (!is.na(House.Trans)) House.Trans else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), House.Trans),
        )
      },
      align = "center"
    ),

    House.Read  = colDef(show = FALSE),
    House.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### Person

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

wordsw.person <- wordsw.person[sample(1:nrow(wordsw.person)),]

reactable(
  wordsw.person,
  columns = list(
    Person.Trans = colDef(
      cell = function(value, index) {
        Person.Read <- wordsw.person$Person.Read[index]
        Person.Read <- if (!is.na(Person.Read)) Person.Read else ""
        Person <- wordsw.person$Person[index]
        Person <- if (!is.na(Person)) Person else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Person),
        )
      },
      align = "center"
    ),

    Person.Read  = colDef(show = FALSE),
    Person = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

wordsw.person <- wordsw.person[sample(1:nrow(wordsw.person)),]

reactable(
  wordsw.person,
  columns = list(
    Person = colDef(
      cell = function(value, index) {
        Person.Read <- wordsw.person$Person.Read[index]
        Person.Read <- if (!is.na(Person.Read)) Person.Read else ""
        Person.Trans <- wordsw.person$Person.Trans[index]
        Person.Trans <- if (!is.na(Person.Trans)) Person.Trans else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Person.Trans),
        )
      },
      align = "center"
    ),

    Person.Read  = colDef(show = FALSE),
    Person.Trans = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Category {.tabset}

#### Na.Adj

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

nadjb <- nadj1 %>% rename(Translation = T1, Sentences = S1)
nadjb <- nadjb %>% na.omit(nadjb)
nadjb <- nadjb[sample(1:nrow(nadjb)),]

reactable(
  nadjb,
  columns = list(
    Translation = colDef(
      cell = function(value, index) {
        Reading <- nadjb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadjb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentences <- nadjb$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        Words <- nadjb$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Sentences),
        )
      },
      align = "center"
    ),

    Sentences = colDef(show = FALSE),
    Words = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

nadjb <- nadjb[sample(1:nrow(nadjb)),]

reactable(
  nadjb,
  columns = list(
    Sentences = colDef(
      cell = function(value, index) {
        Reading <- nadjb$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadjb$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Translation <- nadjb$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        Words <- nadjb$Words[index]
        Words <- if (!is.na(Words)) Words else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Translation),
        )
      },
      align = "center"
    ),

    Translation = colDef(show = FALSE),
    Words = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    # Vertically center cells
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### I.Adj

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

nadja <- nadj2 %>% rename(Translation = T1, Sentences = S1)
nadja <- nadja %>% na.omit(nadja)
nadja <- nadja[sample(1:nrow(nadja)),]

reactable(
  nadja,
  columns = list(
    Translation = colDef(
      cell = function(value, index) {
        Reading <- nadja$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadja$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentences <- nadja$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Sentences),
        )
      },
      align = "center"
    ),
    
    Words = colDef(show = FALSE),
    Sentences = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

nadja <- nadja[sample(1:nrow(nadja)),]

reactable(
  nadja,
  columns = list(
    Sentences = colDef(
      cell = function(value, index) {
        Reading <- nadja$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- nadja$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Translation <- nadja$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Translation),
        )
      },
      align = "center"
    ),
    
    Words = colDef(show = FALSE),
    Translation = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

#### Adverb

<div class = "row">
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

adva <- adv1 %>% rename(Translation = T1, Sentences = S1)
adva <- adva %>% na.omit(adva)
adva <- adva[sample(1:nrow(adva)),]

reactable(
  adva,
  columns = list(
    Translation = colDef(
      cell = function(value, index) {
        Reading <- adva$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- adva$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Sentences <- adva$Sentences[index]
        Sentences <- if (!is.na(Sentences)) Sentences else ""
        tagList(
          div(style = list(fontSize = 20, fontWeight = 600), Sentences),
        )
      },
      align = "center"
    ),
    
    Sentences = colDef(show = FALSE),
    Word = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
<div class = "col-sm-6">

```{r, echo=FALSE, message=FALSE}

adva <- adva[sample(1:nrow(adva)),]

reactable(
  adva,
  columns = list(
    Sentences = colDef(
      cell = function(value, index) {
        Reading <- adva$Reading[index]
        Reading <- if (!is.na(Reading)) Reading else ""
        Meaning <- adva$Meaning[index]
        Meaning <- if (!is.na(Meaning)) Meaning else ""
        Translation <- adva$Translation[index]
        Translation <- if (!is.na(Translation)) Translation else ""
        tagList(
          div(style = list(fontSize = 12, fontWeight = 600), Translation),
        )
      },
      align = "center"
    ),
    
    Translation = colDef(show = FALSE),
    Word = colDef(show = FALSE),
    Meaning = colDef(show = FALSE),
    Reading = colDef(show = FALSE)

  ),
  defaultPageSize = 1,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", height = 250, fontSize = "11px"),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, paginationType = "simple",
  
  style = list(fontFamily = "Noto Sans JP, Hiragino Maru Gothic ProN, Anonymous Pro , Helvetica Neue", fontSize = "11px")
)

```

</div>
</div>

<!-- ------------------------------------------------------------------------ -->

### Random {.tabset}

#### Recognize {.tabset}

##### 1 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw1 <- tblw1[sample(1:nrow(tblw1)),]

reactable(
  tblw1,
  columns = list(
    T1 = colDef(
      cell = function(value, index) {
        W1 <- tblw1$W1[index]
        W1 <- if (!is.na(W1)) W1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W1),
          # div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    T2 = colDef(
      cell = function(value, index) {
        W2 <- tblw1$W2[index]
        W2 <- if (!is.na(W2)) W2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W2),
          # div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    T3 = colDef(
      cell = function(value, index) {
        W3 <- tblw1$W3[index]
        W3 <- if (!is.na(W3)) W3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W3),
          # div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    T4 = colDef(
      cell = function(value, index) {
        W4 <- tblw1$W4[index]
        W4 <- if (!is.na(W4)) W4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W4),
          # div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    T5 = colDef(
      cell = function(value, index) {
        W5 <- tblw1$W5[index]
        W5 <- if (!is.na(W5)) W5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W5),
          # div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    T6 = colDef(
      cell = function(value, index) {
        W6 <- tblw1$W6[index]
        W6 <- if (!is.na(W6)) W6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W6),
          # div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),      
    
    W1 = colDef(show = FALSE),
    W2 = colDef(show = FALSE),
    W3 = colDef(show = FALSE),
    W4 = colDef(show = FALSE),
    W5 = colDef(show = FALSE),
    W6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 2 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw2 <- tblw2[sample(1:nrow(tblw2)),]

reactable(
  tblw2,
  columns = list(
    T1 = colDef(
      cell = function(value, index) {
        W1 <- tblw2$W1[index]
        W1 <- if (!is.na(W1)) W1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W1),
          # div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    T2 = colDef(
      cell = function(value, index) {
        W2 <- tblw2$W2[index]
        W2 <- if (!is.na(W2)) W2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W2),
          # div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    T3 = colDef(
      cell = function(value, index) {
        W3 <- tblw2$W3[index]
        W3 <- if (!is.na(W3)) W3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W3),
          # div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    T4 = colDef(
      cell = function(value, index) {
        W4 <- tblw2$W4[index]
        W4 <- if (!is.na(W4)) W4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W4),
          # div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    T5 = colDef(
      cell = function(value, index) {
        W5 <- tblw2$W5[index]
        W5 <- if (!is.na(W5)) W5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W5),
          # div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    T6 = colDef(
      cell = function(value, index) {
        W6 <- tblw2$W6[index]
        W6 <- if (!is.na(W6)) W6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W6),
          # div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),      
    
    W1 = colDef(show = FALSE),
    W2 = colDef(show = FALSE),
    W3 = colDef(show = FALSE),
    W4 = colDef(show = FALSE),
    W5 = colDef(show = FALSE),
    W6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 3 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw3 <- tblw3[sample(1:nrow(tblw3)),]

reactable(
  tblw3,
  columns = list(
    T1 = colDef(
      cell = function(value, index) {
        W1 <- tblw3$W1[index]
        W1 <- if (!is.na(W1)) W1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W1),
          # div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    T2 = colDef(
      cell = function(value, index) {
        W2 <- tblw3$W2[index]
        W2 <- if (!is.na(W2)) W2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W2),
          # div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    T3 = colDef(
      cell = function(value, index) {
        W3 <- tblw3$W3[index]
        W3 <- if (!is.na(W3)) W3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W3),
          # div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    T4 = colDef(
      cell = function(value, index) {
        W4 <- tblw3$W4[index]
        W4 <- if (!is.na(W4)) W4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W4),
          # div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    T5 = colDef(
      cell = function(value, index) {
        W5 <- tblw3$W5[index]
        W5 <- if (!is.na(W5)) W5 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W5),
          # div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    T6 = colDef(
      cell = function(value, index) {
        W6 <- tblw3$W6[index]
        W6 <- if (!is.na(W6)) W6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W6),
          # div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),      
    
    W1 = colDef(show = FALSE),
    W2 = colDef(show = FALSE),
    W3 = colDef(show = FALSE),
    W4 = colDef(show = FALSE),
    W5 = colDef(show = FALSE),
    W6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 4 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw4 <- tblw4[sample(1:nrow(tblw4)),]

reactable(
  tblw4,
  columns = list(
    T1 = colDef(
      cell = function(value, index) {
        W1 <- tblw4$W1[index]
        W1 <- if (!is.na(W1)) W1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W1),
          # div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    T2 = colDef(
      cell = function(value, index) {
        W2 <- tblw4$W2[index]
        W2 <- if (!is.na(W2)) W2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W2),
          # div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    T3 = colDef(
      cell = function(value, index) {
        W3 <- tblw4$W3[index]
        W3 <- if (!is.na(W3)) W3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W3),
          # div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    T4 = colDef(
      cell = function(value, index) {
        W4 <- tblw4$W4[index]
        W4 <- if (!is.na(W4)) W4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W4),
          # div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    T5 = colDef(
      cell = function(value, index) {
        W5 <- tblw4$W5[index]
        W5 <- if (!is.na(W5)) W5 else ""
        tagList(
          div(style = list(fontSize = 18, fontWeight = 500), W5),
          # div(style = list(fontSize = 8, fontWeight = 400), T5),
        )
      },
      align = "center"
    ),    
    T6 = colDef(
      cell = function(value, index) {
        W6 <- tblw4$W6[index]
        W6 <- if (!is.na(W6)) W6 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W6),
          # div(style = list(fontSize = 8, fontWeight = 400), T6),
        )
      },
      align = "center"
    ),      
    
    W1 = colDef(show = FALSE),
    W2 = colDef(show = FALSE),
    W3 = colDef(show = FALSE),
    W4 = colDef(show = FALSE),
    W5 = colDef(show = FALSE),
    W6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 5 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw5 <- tblw5[sample(1:nrow(tblw5)),]

reactable(
  tblw5,
  columns = list(
    T1 = colDef(
      cell = function(value, index) {
        W1 <- tblw5$W1[index]
        W1 <- if (!is.na(W1)) W1 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W1),
          # div(style = list(fontSize = 8, fontWeight = 400), T1),
        )
      },
      align = "center"
    ),
    T2 = colDef(
      cell = function(value, index) {
        W2 <- tblw5$W2[index]
        W2 <- if (!is.na(W2)) W2 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W2),
          # div(style = list(fontSize = 8, fontWeight = 400), T2),
        )
      },
      align = "center"
    ),    
    T3 = colDef(
      cell = function(value, index) {
        W3 <- tblw5$W3[index]
        W3 <- if (!is.na(W3)) W3 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W3),
          # div(style = list(fontSize = 8, fontWeight = 400), T3),
        )
      },
      align = "center"
    ),       
    T4 = colDef(
      cell = function(value, index) {
        W4 <- tblw5$W4[index]
        W4 <- if (!is.na(W4)) W4 else ""
        tagList(
          div(style = list(fontSize = 16, fontWeight = 500), W4),
          # div(style = list(fontSize = 8, fontWeight = 400), T4),
        )
      },
      align = "center"
    ),
    
    W1 = colDef(show = FALSE),
    W2 = colDef(show = FALSE),
    W3 = colDef(show = FALSE),
    W4 = colDef(show = FALSE),
    R1 = colDef(show = FALSE),
    R2 = colDef(show = FALSE),
    R3 = colDef(show = FALSE),
    R4 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

#### Recall {.tabset}

##### 1 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw1 <- tblw1[sample(1:nrow(tblw1)),]

reactable(
  tblw1,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw1$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W1),
          div(style = list(fontSize = 12, fontWeight = 600), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw1$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W2),
          div(style = list(fontSize = 12, fontWeight = 600), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw1$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W3),
          div(style = list(fontSize = 12, fontWeight = 600), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw1$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W4),
          div(style = list(fontSize = 12, fontWeight = 600), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw1$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W5),
          div(style = list(fontSize = 12, fontWeight = 600), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw1$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W6),
          div(style = list(fontSize = 12, fontWeight = 600), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 2 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw2 <- tblw2[sample(1:nrow(tblw2)),]

reactable(
  tblw2,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw2$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W1),
          div(style = list(fontSize = 12, fontWeight = 600), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw2$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W2),
          div(style = list(fontSize = 12, fontWeight = 600), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw2$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W3),
          div(style = list(fontSize = 12, fontWeight = 600), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw2$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W4),
          div(style = list(fontSize = 12, fontWeight = 600), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw2$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W5),
          div(style = list(fontSize = 12, fontWeight = 600), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw2$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W6),
          div(style = list(fontSize = 12, fontWeight = 600), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 3 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw3 <- tblw3[sample(1:nrow(tblw3)),]

reactable(
  tblw3,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw3$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W1),
          div(style = list(fontSize = 12, fontWeight = 600), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw3$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W2),
          div(style = list(fontSize = 12, fontWeight = 600), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw3$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W3),
          div(style = list(fontSize = 12, fontWeight = 600), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw3$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W4),
          div(style = list(fontSize = 12, fontWeight = 600), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw3$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W5),
          div(style = list(fontSize = 12, fontWeight = 600), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw3$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W6),
          div(style = list(fontSize = 12, fontWeight = 600), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 4 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw4 <- tblw4[sample(1:nrow(tblw4)),]

reactable(
  tblw4,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw4$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W1),
          div(style = list(fontSize = 12, fontWeight = 600), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw4$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W2),
          div(style = list(fontSize = 12, fontWeight = 600), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw4$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W3),
          div(style = list(fontSize = 12, fontWeight = 600), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw4$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W4),
          div(style = list(fontSize = 12, fontWeight = 600), T4),
        )
      },
      align = "center"
    ),
    W5 = colDef(
      cell = function(value, index) {
        T5 <- tblw4$T5[index]
        T5 <- if (!is.na(T5)) T5 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W5),
          div(style = list(fontSize = 12, fontWeight = 600), T5),
        )
      },
      align = "center"
    ),    
    W6 = colDef(
      cell = function(value, index) {
        T6 <- tblw4$T6[index]
        T6 <- if (!is.na(T6)) T6 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W6),
          div(style = list(fontSize = 12, fontWeight = 600), T6),
        )
      },
      align = "center"
    ),      
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    T5 = colDef(show = FALSE),
    T6 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

<!-- ------------------------------------------------------------------------ -->

##### 5 {.tabset}

```{r, echo=FALSE, message=FALSE}

tblw5 <- tblw5[sample(1:nrow(tblw5)),]

reactable(
  tblw5,
  columns = list(
    W1 = colDef(
      cell = function(value, index) {
        T1 <- tblw5$T1[index]
        T1 <- if (!is.na(T1)) T1 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W1),
          div(style = list(fontSize = 12, fontWeight = 600), T1),
        )
      },
      align = "center"
    ),
    W2 = colDef(
      cell = function(value, index) {
        T2 <- tblw5$T2[index]
        T2 <- if (!is.na(T2)) T2 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W2),
          div(style = list(fontSize = 12, fontWeight = 600), T2),
        )
      },
      align = "center"
    ),    
    W3 = colDef(
      cell = function(value, index) {
        T3 <- tblw5$T3[index]
        T3 <- if (!is.na(T3)) T3 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W3),
          div(style = list(fontSize = 12, fontWeight = 600), T3),
        )
      },
      align = "center"
    ),       
    W4 = colDef(
      cell = function(value, index) {
        T4 <- tblw5$T4[index]
        T4 <- if (!is.na(T4)) T4 else ""
        tagList(
          # div(style = list(fontSize = 18, fontWeight = 500), W4),
          div(style = list(fontSize = 12, fontWeight = 600), T4),
        )
      },
      align = "center"
    ),
    
    T1 = colDef(show = FALSE),
    T2 = colDef(show = FALSE),
    T3 = colDef(show = FALSE),
    T4 = colDef(show = FALSE),
    R1 = colDef(show = FALSE),
    R2 = colDef(show = FALSE),
    R3 = colDef(show = FALSE),
    R4 = colDef(show = FALSE)
  ),
  defaultPageSize = 5,
  theme = reactableTheme(
    cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center", fontSize = "11px", height = 90),
    searchInputStyle = list(
      paddingLeft = "8px",
      paddingTop = "8px",
      paddingBottom = "8px",
      width = "100%",
      fontSize = "11px"
    )
  ),
  showPageInfo = FALSE, bordered = TRUE, searchable = TRUE, sortable = FALSE, paginationType = "numbers",

  style = list(fontFamily = "Noto Sans JP, Heiti SC, Hiragino Maru Gothic ProN, Anonymous Pro , monospace, Helvetica Neue", fontSize = "11px")
)

```

